# MSETOOL STOCK REDUCTION ANALYSIS {#app:sra}

**The following is preliminary and largely reproduced from an MSEtool vignette (written by Quang Huynh) for completeness with some modifications. Updated by QH and imported by RF Feb 14 2020**

**The text before the equations will be rewritten for the purposes of this document.**

## A BACKGROUND ON STOCK REDUCTION ANALYSIS {#sec:sra-background}

The operating model (OM) defined in Appendix \@ref(app:dlmtool-om) is conditioned  by fitting an age-structured stock-reduction analysis (SRA) [@kimura1982; @walters2006] to historical observed catches and indices of abundance (and to age- and length-composition data if available). 
This step produces estimates of parameters that produce time-series trajectories that are consistent with historical observations. 
This is especially important in data-limited or data-moderate situations, where the lack of an accepted assessment makes it difficult to parameterize historical depletion and fishing mortality $F$.

In the literature, the term "stock reduction analysis" has been used to describe a model in which the predicted total catch matches the observed catch.
@kimura1982 presented SRA as an alternative to a virtual production analysis (VPA) or surplus production model.
The SRA approach is more applicable to data-limited species than, for example, a VPA when annual catch-at-age data aren't available, while also utilizing an age-structured modeling approach that incorporates natural mortality and recruitment information for reconstructing the stock history, rather than taking a pooled biomass-dynamics approach (e.g., surplus production model). 

Another advantage of the SRA approach for BC groundfish fisheries is it accommodates model-conditioning on multiple indices of abundance (e.g., accommodating indices from multiple fishery-independent surveys and/or commercial CPUE series).

For data-limited species, where it may only be possible to provide ranges of values for key parameters, the SRA approach tries to reduce the range of plausible parameters to be consistent with historical observations. 
for example, @walters2006 used SRA as an approach to address the broader question: what combinations of historical fishing mortality and recruitment could have generated the observed data?

## STOCK REDUCTION ANALYSIS IN THE CONTEXT OF DLMTOOL {#sec:sra-dlmtool}

In MSEtool, `SRA_scope()` is the main function for scoping historical scenarios for an OM. 
`SRA_scope` takes a DLMtool OM object (Appendix \@ref(app:dlmtool-om)) and historical observed data (observed catches, indices of abundance and, if available, composition data), fits the SRA to the observed data, and then returns a list with an updated OM and calibrated outputs from the SRA. 

The approach can be stochastic (with Monte Carlo sampling) if the operating model is specified with ranges on key parameters. 
For example, the steepness parameter of the stock-recruit relationship ($h$) is usually highly uncertain. The user can specify a range of values for $h$ (e.g., 0.6 to 0.9 with a uniform distribution):

\begin{equation}
h \sim U (0.6,0.9)
\end{equation}

In this case, with $i = 1:n$ (e.g., $n=250$) simulations in the closed-loop simulation,  `SRA_scope` will sample $n$ steepness values from this distribution and then fit the SRA model $n$ times. 
Alternatively, the user can provide values in the `cpars` section of the operating model, e.g.,

\begin{equation}
h_\text{samp} \sim \text{rbeta}(n, 13.3, 4.4)
\end{equation}

then `OM@cpars$h` = $0.8 h_\text{samp}  + 0.2$

The SRA model reconstruction from `i-th` fit will be conditioned on the `i-th` sampled value of $h$. 
The sampled values of $h$ (as well as all other input parameters to the SRA) are then saved in the OM object returned by `SRA_scope`.

## THE STOCK REDUCTION ANALYSIS MODEL {#sec:sra-model}

The SRA model can be conditioned on catch, e.g., `SRA_scope(..., condition = "catch")` or fishing effort.
For BC groundfish species, we recommend conditioning the model on catch.
If the model is conditioned on catch, then the SRA will generate predicted catches that match the observed. 
If conditioned on effort, the estimated fishing mortality in the model will be proportional to the observed effort. 
A full time series of the conditioning variable (i.e., catch) is needed, and length of the historical period `OM@nyears` will be the length of the conditioned time series.

In many cases, the time series can be assumed to begin at unfished conditions ($B_{t=1} = B_0$, where $B_{t=1}$ is spawning biomass in the first historical year and $B_0$ represents equilibrium stock size in unfished conditions. 
However, for some groundfish species in BC, catch records may be less reliable prior to the introduction of comprehensive catch monitoring (e.g., in 1996 for the BC groundfish trawl fleet). In these cases, users can pass `SRA_scope` a value for asssumed equilibrium catch ($C_{eq}$) prior to the first year of the catch time series. 
The SRA will then use this value to estimate the initial depletion ($\frac{B_{t=1}}{B_0}$) in the first year of the historical period.
However, even using this approach, initial depletion is difficult to estimate with precision without other sources of information (e.g., age-composition data). 
We therefore recommend treating $C_{eq}$ as a major axis of uncertainty if this approach is taken.
An alternative approach is to use catch-reconstruction methods [e.g., @porch2004; @starr2017] to reconstruct the catch time series back to the time when the stock was considered unfished. While this approach avoids the uncertainty associated with estimating depletion based on $C_{eq}$, it may introduce other sources of uncertainty associated with the reconstruction approach, which may itself cause controversy.

In addition to the conditioning time series, additional data types can be used, which do not need to be available in every year of the historical time series:

- Time series of indices of abundance (either as surveyed biomass or fishery-dependent catch-per-unit-effort (CPUE))
- Age-composition data
- Length-composition data
- Mean length data (this option is generally for very sparse data scenarios when mean length data are available but not the composition data)

Multiple surveys and fleets can be accommodated with `SRA_scope`. One of these several data types in addition to catch or effort is generally needed to obtain depletion estimates. 
Availability of these data can be quite sparse over time, yet still informative. 
For example, an age composition sample from a single recent year that shows a very truncated age structure can be sufficient to imply a heavily depleted stock.

The required pre-specified OM parameters needed for SRA scoping are:

- Growth (length-at-age) using slots `OM@Linf, OM@K, OM@t0` (or alternatively, `OM@cpars$Len_age`)
- Variability in length-at-age `OM@LenCV` only if length data are used
- Length-weight conversion factors using slots `OM@a` and `OM@b` (or alternatively, `OM@cpars$Wt_age`)
- Natural mortality using slots `OM@M, OM@M2` or `OM@cpars$M_ageArray`
- Maturity using slots `OM@L50, OM@L50_95` or `OM@cpars$Mat_age`
- Standard deviation of recruitment deviations using slot `OM@Perr` or `OM@cpars$Perr`
- Stock-recruit relationship with `OM@SRrel`
- Selectivity parameters with `OM@L5`, `OM@LFS`, and `OM@Vmaxlen`. If there are no age or length compositions, then selectivity in the model is fixed to these values. Otherwise, these are used as starting values.
- Unfished recruitment `OM@R0` as the starting value.

If growth, natural mortality, or maturity are time-varying in the historical period, then the SRA will implement time-varying life history in the estimation model as well. 
For example, if we're setting up an operating model where the length of the historical period is 50 years, and we believe that natural mortality has doubled from 0.2 to 0.4 since Year 30 and will remain so into the future, this code can be used to set up this scenario:

```{r, eval = FALSE}
OM@nyears <- 50
OM@proyears <- 30

M_ageArray <- array(0.4, c(OM@nsim, OM@maxage, OM@nyears + OM@proyears)) # Default M = 0.4
M_ageArray[, , 1:30] <- 0.2 # M = 0.2 in the first 30 years of the simulation
OM@cpars$M_ageArray <- M_ageArray
```

The SRA will pick up this change in the model as well.

The easiest way to turn off time-varying growth and M is to set:

```{r, eval = FALSE}
OM@Linfsd <- OM@Ksd <- OM@Msd <- c(0, 0)
```

Selectivity is fixed if no age or length compositions are provided. Otherwise, the ascending limb of selectivity is estimated with age or length composition data. 
If the selectivity is assumed to be dome-shaped, then the descending limb can either be fixed values sampled from slot `OM@Vmaxlen` or estimated in the SRA. 

Information about the slots in the OM object can be viewed through `class?OM`. 
If passing custom objects to the operating model that override default inputs (e.g., for time-varying parameters), then `DLMtool::validcpars()` will be helpful for setting up and indexing the dimensions of the custom objects.

## Updated parameters and SRA model evaluation

Historical OM parameters that are updated by the SRA scoping function include:

- Unfished recruitment `OM@R0`, only if catch is provided.
- Depletion `OM@D`
- Annual fishing effort in `OM@EffYears`, `OM@EffLower`, `OM@EffUpper`, and `OM@cpars$Find`. In conjunction with depletion, effort will be equal to the apical fishing mortality.
- Recruitment autocorrelation `OM@AC` which is estimated post-hoc from the recruitment deviation estimates.
- Annual recruitment deviations `OM@cpars$Perr_y`. Historical recruitment are those estimated from the model, while future recruitment will be sampled with autocorrelation.
- Selectivity parameters `OM@L5, OM@LFS, and OM@Vmaxlen`. If multiple fleets are modeled, then the F-at-age matrix is used to derive the effective selectivity and placed in `OM@cpars$V`.

If initial depletion is estimated, then the recruitment deviations `OM@cpars$Perr_y` for the operating model are adjusted in order to produce the estimated abundance-at-age in the first year of the SRA model. 

The SRA model will estimate and return R0 when conditioned on catch. 
When conditioning on effort, the model is generally scale-independent; there can be information to inform depletion but not the stock size. 
The exception occurs when the SRA is conditioned on effort from multiple-fleets, in which case, catch data from all fleets (incomplete series are acceptable) are needed to inform the relative F's among fleets. 
In this scenario, R0 is estimated.

Additionally, if multiple fleets are used for conditioning, then the annual selectivity can change based on the relative F among fleets. 
In this case, the annual selectivity is passed from the OM output in the `OM@cpars$V` slot. 
The default assumption in the projection period of the closed-loop simulation is that the selectivity and relative F among fleets are identical to those in the last historical year. 
Fleet allocation in management procedures can be explored in `multiMSE`, see `vignette("multiMSE")`.

Life history parameters used in the SRA reconstruction will be also passed to `OM@cpars` to ensure reproducibility. 
Time-varying parameters affect calculation of reference points, mostly importantly unfished depletion. 
In `SRA_scope` (and DLMtool), depletion is the ratio of the spawning biomass in the terminal year and the unfished spawning biomass in the first year of the model. 
In this sense, depletion used to describe changes in the stock since fishing began.
If life-history parameter are time-varying, then this definition may not necessarily reflect a management target.

The relative effort provided in the output is the apical F from the SRA. 
When running the management strategy evaluation with `DLMtool::runMSE()`, the apical F may be re-scaled to ensure that specified depletion has been reached at the beginning and end of the historical period. 
For simple operating models, i.e. those with conditions identical to the SRA, the apical F's in the MSE should be nearly identical to those from the SRA. 
To confirm that this is the case, one can run the `plot` function on output returned by `SRA_scope`:

```{r, eval = FALSE}
output <- SRA_scope(...)
plot(output)
```

This function returns a markdown report with:

- Histograms of updated parameters in the OM object
- Fits of the SRA model to the provided data
- Output from the SRA model, e.g. predicted recruitment
- Fits to an additional run of the SRA model to mean life history values among simulations (only when `SRA_scope(..., mean_fit = TRUE)` is run)
- Comparisons of the historical period of the updated OM to the estimated SRA output

Currently, it is possible to create a more complex operating model than the SRA model itself. 
For example, discard mortality, movement, and spatial targetting are currently not modeled in the SRA. 
It is assumed that the catch in the SRA are all known sources of removal, i.e. landings plus discards. 
The SRA is a single area model, whereas DLMtool uses a multiple-area model. A simple operating model that best matches the SRA model may have the following configurations:

```{r, eval = FALSE}
OM@DR <- c(0, 0) # All discards are accounted for
OM@Size_area_1 <- OM@Frac_area_1 <- OM@Prob_staying <- c(0.5, 0.5) # A well-mixed stock in 2 areas of equal sizes
```

It may be desirable to compare the SRA to a simple operating model before incorporating more complex dynamics in the operating model.

## DESCRIPTION OF THE SRA MODEL

### Selectivity and mortality

Selectivity $v$ is length-based and modeled as a double-exponential function (using base 2). 
For fleet $f$ with flat-topped selectivity, two parameters are used, the length of 5% selectivity ($L^5_f$) and the length of full selectivity $L^{\textrm{FS}}_f$. 
For dome selectivity, a third parameter, the selectivity at $L_{\infty}$, $V^{L_{\infty}}_f$ is also used. 
Length-based selectivity is converted to age-based selectivity in the age-structured model as:

\begin{equation}
v_{y,a,f} = 
\begin{cases}
2^{-[(L_{y,a} - L^{\textrm{FS}}_f)/(\sigma^{\textrm{asc}}_f)]^2} & \textrm{if } L_{y,a} < L^{\textrm{FS}}_f\\ 
1 & \textrm{if logistic and } L_{y,a} \ge L^{\textrm{FS}}_f,\\
2^{-[(L_{y,a} - L^{\textrm{FS}}_f)/(\sigma^{\textrm{des}}_f)]^2} & \textrm{if dome and } L_{y,a} \ge L^{\textrm{FS}}_f
\end{cases}
(\#eq:sra-om-vyaf)
\end{equation}

where $L_{y,a}$ is the mean length-at-age in year $y$, and $\sigma^{\textrm{asc}}_f = (L^5_f - L^{\textrm{FS}}_f)/\sqrt{-\log_2(0.05)}$ and $\sigma^{\textrm{des}}_f = (L_{\infty} - L^{\textrm{FS}}_f)/\sqrt{-\log_2(V^{L_{\infty}})}$ control the shape of the ascending and descending limbs, respectively, of the selectivity function. In this parameterization, length-based selectivity is constant over time. The corresponding age-based selectivity is constant over time if growth is not time-varying.

Total mortality $Z$ in year $y$ and for age $a$ is the sum of fishing mortality $F$ from all fleets and natural mortality $M$,

\begin{equation}
Z_{y,a} = M_{y,a} + \Sigma_f v_{y,a,f} F_{y,f}
(\#eq:sra-om-zya)
\end{equation}

### Initial population distribution

The population age distribution in the first year of the model $y=1$ is in equilibrium where

\begin{equation}
N_{1,a} = 
\begin{cases}
      R^{\textrm{eq}} \exp(-\Sigma_{i=1}^{a-1}Z^{\textrm{eq}}_i) & a = 1, \ldots, A-1\\
      \dfrac{R^{\textrm{eq}} \exp(-\Sigma_{i=1}^{a-1}Z^{\textrm{eq}}_i)}{1 - \exp(-Z^{\textrm{eq}}_A)} & a = A,
\end{cases}
(\#eq:sra-om-numinit)
\end{equation}

where the $R^{\textrm{eq}}$ is the equilibrium recruitment and $Z^{\textrm{eq}}_a = M_{1,a} + \Sigma_f v_{1,a,f} F^{\textrm{eq}}_f$ is the equilibrium total mortality rate. Unfished conditions are modeled by setting $F^{\textrm{eq}}_f = 0$. To estimate $F^{\textrm{eq}}_f$, the corresponding equilibrium catch in weight $\tilde{C}^{\textrm{eq}}_f$ prior to the first year of the model should be provided. In the equilibrium yield curve,  $F^{\textrm{eq}}_f$ would be the fishing mortality corresponding to fishing at $F^{\textrm{eq}}_f$. Once $Z^{\textrm{eq}}_a$ is obtained, then the equilibrium recruitment is calculated as:

\begin{equation}
R^{\textrm{eq}} = 
\begin{cases}
      \dfrac{\alpha^{\textrm{B}}\phi^{\textrm{eq}} - 1}{\beta^{\textrm{B}}\phi^{\textrm{eq}}} & \textrm{if Beverton-Holt stock-recruit relationship}\\
      \dfrac{\log(\alpha^{\textrm{R}}\phi^{\textrm{eq}})}{\beta^{\textrm{R}}\phi^{\textrm{eq}}} & \textrm{if Ricker stock-recruit relationship}
\end{cases}
(\#eq:om-sra-recinit)
\end{equation}

where $\phi^{\textrm{eq}}$ is the spawners-per-recruit when the mortality is $Z^{\textrm{eq}}_a$. From steepness $h$, $\alpha^{\textrm{B}} = \frac{4h}{(1-h)\phi_0}$, $\beta^{\textrm{B}} = \frac{5h-1}{(1-h)B^S_0}$, $\alpha^{\textrm{R}} = \frac{(5h)^{1.25}}{\phi_0}$, $\beta^{\textrm{R}} = \frac{\log(5h)}{B^S_0}$, where $\phi_0$ and $B^S_0$ are unfished spawners-per-recruit and unfished spawning biomass, respectively.

### Dynamics equations

After setting the equilibrium population age distribution in the first year of the model, the population abundance $N_{y,a}$ in subsequent years is

\begin{equation}
N_{y,a} =
\begin{cases}
      R_y & a = 1\\
      N_{y-1,a-1} \exp(-Z_{y-1,a-1}) & a = 2, \ldots, A - 1,\\
      N_{y-1,a-1} \exp(-Z_{y-1,a-1}) + N_{y-1,a} \exp(-Z_{y-1,a}) & a = A
\end{cases}
(\#eq:om-sra-nya)
\end{equation}

where $R_y$ is the recruitment and $A$ is the maximum-age as the plus-group. Recruitment is modelled as

<!--TODO: change B^S to S-->



\begin{equation}
R_y = 
\begin{cases}
      \dfrac{\alpha^{\textrm{BH}} B^S_{y-1}}{1 + \beta^{\textrm{BH}}B^S_{y-1}} \exp(\delta_y - 0.5 \tau^2) & \textrm{if Beverton-Holt stock-recruit relationship}\\
      \alpha^{\textrm{Ricker}} B^S_{y-1} \exp(-\beta^{\textrm{Ricker}} B^S_{y-1})\exp(\delta_y - 0.5 \tau^2) & \textrm{if Ricker stock-recruit relationship}
\end{cases},
(\#eq:om-sra-rya)
\end{equation}

where $\delta_y$ are recruitment deviates and $\tau$ is the standard deviation of the deviates.

The spawning biomass is $B^S_y$ is

\begin{equation}
B^S_y = \sum_a w_{y,a} m_{y,a} N_{y,a}
(\#eq:om-sra-sy)
\end{equation}

where $m_{y,a}$ and $w_{y,a}$ are the maturity-at-age and weight-at-age, respectively.

## Catch-at-age

If the model is fit to age-composition data, the catch (in numbers) $C^N$ at age for fleet $f$ is
\begin{equation}
C^N_{y,a,f} = \dfrac{v_{y,a,f} F_{y,f}}{Z_{y,a}} N_{y,a} (1 - \exp[-Z_{y,a}])
(\#eq:om-sra-cyaf)
\end{equation}

In our framework, we recommend conditioning the model on observed catches, as these are better reported than effort, and easier to interpret for a multispecies fishery. In this case, with a model conditioned on catch, then $F_{y,f}$ can be estimated as parameters or solved iteratively to match the observed catch. 
In other applications, if the model is conditioned on effort, then

\begin{equation}
F_{y,f} = q_f E_{y,f}
(\#eq:om-sra-fyf-eff)
\end{equation}

where $E_{y,f}$ is the observed effort and $q_f$ is the scaling coefficient.

## Catch-at-length

If the model is fit to length-composition data, the catch-at-length is calculated assuming a normally distributed length-at-age $P(\ell,a)$, where


\begin{equation}
C^N_{y,\ell,f} = \sum_a C^N_{y,a,f} P(\ell \vert a)
(\#eq:om-sra-cylf)
\end{equation}

and

\begin{equation}
P(\ell \vert a) = 
\begin{cases}
      \phi(L'_{\ell+1}) & \ell = 1\\
      \phi(L'_{\ell+1}) - \phi(L'_\ell) & \ell = 2, \ldots, L - 1,\\
      1 -\phi(L'_\ell) & \ell = L
\end{cases}
(\#eq:om-sra-pla)
\end{equation}

where $L'_{\ell}$ is the length at the lower boundary of length bin $\ell$ and $\phi(L'_{\ell})$ is the cumulative distribution function of a normal variable with mean $\tilde{L}_{y,a}$ (the expected mean length at age $a$) and standard deviation $\tilde{L}_{y,a} \times CV^L$ ($CV^L$ is the coefficient of variation in mean length at age). 

The catch in weight $\tilde{C}$ is

\begin{equation}
\tilde{C}_{y,f} = \sum_a C^N_{y,a,f} w_{y,a}
(\#eq:om-sra-cyfw)
\end{equation}

The mean length of the catch $\bar{L}_{y,f}$ is

\begin{equation}
\bar{L}_{y,f} = \dfrac{\sum_{\ell} L_{\ell} C^N_{y,\ell,f}}{\sum_{\ell} C^N_{y,\ell,f}}
(\#eq:om-sra-lmean)
\end{equation}

where $L_\ell$ is the midpoint of the length bin $\ell$.

The proportion of the catch-at-age is

\begin{equation}
p_{y,a,f} = \dfrac{C^N_{y,a,f}}{\sum_a C^N_{y,a,f}}
(\#eq:om-sra-pyaf)
\end{equation}

The proportion of the catch-at-length is

\begin{equation}
p_{y,\ell,f} = \dfrac{C^N_{y,\ell,f}}{\sum_{\ell}C^N_{y,\ell,f}}
(\#eq:om-sra-pylf)
\end{equation}

## Survey 

If the $s^{\textrm{th}}$ survey is biomass-based, then the survey value $I_{y,s}$ is calculated as

\begin{equation}
I_{y,s} = q_s \sum_a v_{y,a,s} N_{y,a} w_{y,a}
(\#eq:om-sra-iysb)
\end{equation}

where $q$ is the scaling coefficient and $s$ indexes survey.

If the survey is abundance-based, then 

\begin{equation}
I_{y,s} = q_s \sum_a v_{y,a,s} N_{y,a}
(\#eq:om-sra-iysn)
\end{equation}

### Likelihoods

If the model is conditioned on catch and fishing mortality rates are estimated parameters, then the log-likelihood component $\Lambda_1$ of the catch is

\begin{equation}
\Lambda_1 = \sum_f \left[\lambda^{\tilde{C}}_f \sum_y \left(-\log(0.01) - \dfrac{[\log(\tilde{C}^{\textrm{obs}}_{y,f}) - \log(\tilde{C}^{\textrm{pred}}_{y,f})]^2}{2 \times 0.01^2}\right)\right]
(\#eq:om-sra-like-catch)
\end{equation}

where $\textrm{obs}$ and $\textrm{pred}$ indicate observed and predicted quantities, respectively, and $\lambda$ are likelihood weights. With a small standard deviation for the catch likelihood relative to the variance in other likelihood components, the predicted catch should match the observed catch.

The log-likelihood component $\Lambda_2$ of survey data is

\begin{equation}
\Lambda_2 = \sum_s \left[ \lambda^I_s \sum_y \left(-\log(\sigma_{y,s}) - \dfrac{[\log(I^{\textrm{obs}}_{y,s}) - \log(I^{\textrm{pred}}_{y,s})]^2}{2\sigma_{y,s}^2}\right) \right]
(\#eq:om-sra-like-ind)
\end{equation}

The log-likelihood component $\Lambda_3$ of catch-at-age data is

\begin{equation}
\Lambda_3 = \sum_f \lambda^A_f \left[\sum_y O^A_{y,f} \sum_a p^{\textrm{obs}}_{y,a,f} \log(p^{\textrm{pred}}_{y,a,f})\right]
(\#eq:om-sra-like-caa)
\end{equation}

where $O^A$ is the annual sample sizes for the age compositions.

The log-likelihood component $\Lambda_4$ of catch-at-length data is

\begin{equation}
\Lambda_4 = \sum_f \lambda^L_f \left[ \sum_y O^L_{y,f} \sum_{\ell} p^{\textrm{obs}}_{y,\ell,f} \log(p^{\textrm{pred}}_{y,\ell,f})\right]
(\#eq:om-sra-like-cal)
\end{equation}

where $O^L$ is the annual sample sizes for the length compositions.

The log-likelihood component $\Lambda_5$ of observed mean lengths in the catch is

\begin{equation}
\Lambda_5 = \sum_f \lambda^{\bar{L}}_f\left[ \sum_y \left(-\log(\omega_f) - \dfrac{[\bar{L}^{\textrm{obs}}_{y,f} - \bar{L}^{\textrm{pred}}_{y,f}]^2}{2 \omega^2_f}\right)\right]
(\#eq:om-sra-like-meanl)
\end{equation}

where $\omega_f$ is the standard deviation of mean lengths.

The log-likelihood component $\Lambda_6$ of annual estimated recruitment deviates $\delta_y$ in log space is

\begin{equation}
\Lambda_6 = \Sigma_y\left(-\log(\tau) - \dfrac{\delta_y^2}{2 \tau^2}\right)
(\#eq:om-sra-like-recdevs)
\end{equation}

where $\tau$ is the standard deviation of recruitment deviates.

The log-likelihood component $\Lambda_7$ of the equilibrium catch is

\begin{equation}
\Lambda_7 = \sum_f \lambda^{\tilde{C}}_f \left(-\log(0.01) - \dfrac{[\log(\tilde{C}^{\textrm{eq,obs}}_f) - \log(\tilde{C}^{\textrm{eq,pred}}_f)]^2}{2 \times 0.01^2}\right)
(\#eq:om-sra-like-eqcatch)
\end{equation}

The total log-likelihood $\textrm{LL}$ to be maximized is
\begin{equation}
\textrm{LL} = \sum_{i=1}^7\Lambda_i
(\#eq:om-sra-like-tot)
\end{equation}

