```{r message = FALSE}
library(DLMtool)
knitr_results <- TRUE
knitr_echo <- TRUE
```

\clearpage

# DEFAULT SLOTS {#app:default-slots}

The following are OM values or "slots" that we suggest by default be "turned off" or set to default values for the sake of simplicity. On a case-by-case basis, an analyst might choose to set some of these slots to other values or include other values as part of a robustness set. However, unless specified otherwise, the following slots can be assumed to be specified as follows.

## DEFAULT STOCK SLOTS {#app:desc-stock-default}

```{r warnings = FALSE}
stock_default <- methods::new('Stock')
```

<!-- slot-chunk-begin -->
### M2 {#app:desc-stock-m2-default}

*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number*

By default we will not specify natural mortality rate by age.

```{r desc-stock-m2-default, results = knitr_results, echo = knitr_echo}
stock_default@M2
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Mexp {#app:desc-stock-mexp-default}

*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*

By default we will not use this functionality.

```{r desc-stock-mexp-default, results = knitr_results, echo = knitr_echo}
stock_default@Mexp <- c(NA_real_, NA_real_)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Msd {#app:desc-stock-msd-default}

*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*

By default we will assume that natural mortality is not time-varying, although this might be an important slot to explore as part of a robustness set for some stocks.

```{r desc-stock-msd-default, results = knitr_results, echo = knitr_echo}
stock_default@Msd
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
<!-- slot-chunk-begin -->
### Period {#app:desc-stock-period-default}

*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers*

By default we will not assume a cyclical recruitment pattern.

```{r desc-stock-period-default, results = knitr_results, echo = knitr_echo}
stock_default@Period
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Amplitude {#app:desc-stock-amplitude-default}

*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1*

By default we will not assume a cyclical recruitment pattern.

```{r desc-stock-amplitude-default, results = knitr_results, echo = knitr_echo}
stock_default@Amplitude
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Ksd {#app:desc-stock-ksd-default}

*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

By default we will assume that growth is not time varying.

```{r desc-stock-ksd-default, results = knitr_results, echo = knitr_echo}
stock_default@Ksd
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Linfsd {#app:desc-stock-linfsd-default}

*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

By default we will assume that growth is not time varying.

```{r desc-stock-linfsd-default, results = knitr_results, echo = knitr_echo}
stock_default@Linfsd
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
<!-- slot-chunk-begin -->
### Size_area_1 {#app:desc-stock-size_area_1-default}

*The size of area 1 relative to the total area (area 1 + area 2). Set to 0.5 to approximate single area model. Uniform distribution lower and upper bounds. Positive real numbers.*

We will set this to 0.5 to mimic a single area model.

```{r desc-stock-size_area_1-default, results = knitr_results, echo = knitr_echo}
stock_default@Size_area_1 <- c(0.5, 0.5)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Frac_area_1 {#app:desc-stock-frac_area_1-default}

*The fraction of the unfished biomass in area 1 relative to the total area (area 1 + area 2). Uniform distribution lower and upper bounds. Positive real numbers.*

We will set this to 0.5 to mimic a single area model.

```{r desc-stock-frac_area_1-default, results = knitr_results, echo = knitr_echo}
stock_default@Frac_area_1 <- c(0.5, 0.5)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Prob_staying {#app:desc-stock-prob_staying-default}

*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*

We will set this to 0.5 to mimic a single area model.

```{r desc-stock-prob_staying-default, results = knitr_results, echo = knitr_echo}
stock_default@Prob_staying <- c(0.5, 0.5)
```
<!-- slot-chunk-end -->

## DEFAULT FLEET SLOTS {#app:desc-fleet-default}

```{r warnings = FALSE}
fleet_default <- methods::new('Fleet')
```

<!-- slot-chunk-begin -->
### EffYears {#app:desc-fleet-effyears-default}

*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers.*

By default we will populate this from the SRA model.

```{r desc-fleet-effyears-default, results = knitr_results, echo = knitr_echo}
fleet_default@EffYears
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### EffLower {#app:desc-fleet-efflower-default}

*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers.*

By default we will populate this from the SRA model.

```{r desc-fleet-efflower-default, results = knitr_results, echo = knitr_echo}
fleet_default@EffLower
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### EffUpper {#app:desc-fleet-effupper-default}

*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers.*

By default we will populate this from the SRA model.

```{r desc-fleet-effupper-default, results = knitr_results, echo = knitr_echo}
fleet_default@EffUpper
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Esd {#app:desc-fleet-esd-default}

*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers.*

We will assume that fishing mortality is not time varying by default.

```{r desc-fleet-esd-default, results = knitr_results, echo = knitr_echo}
fleet_default@Esd <- c(0, 0)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### qinc {#app:desc-fleet-qinc-default}

*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers.*

We will assume that fishing efficiency is not time varying by default.

```{r desc-fleet-qinc-default, results = knitr_results, echo = knitr_echo}
fleet_default@qinc <- c(0, 0)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### qcv {#app:desc-fleet-qcv-default}

*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers.*

We will assume that fishing efficiency is not time varying by default.

```{r desc-fleet-qcv-default, results = knitr_results, echo = knitr_echo}
fleet_default@qcv <- c(0, 0)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### SelYears {#app:desc-fleet-selyears-default}


We will not use this functionality by default.
*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers.*

```{r desc-fleet-selyears-default, results = knitr_results, echo = knitr_echo}
fleet_default@SelYears
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### AbsSelYears {#app:desc-fleet-absselyears-default}


We will not use this functionality by default.
*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers.*

```{r desc-fleet-absselyears-default, results = knitr_results, echo = knitr_echo}
fleet_default@AbsSelYears
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L5Lower {#app:desc-fleet-l5lower-default}


We will not use this functionality by default.
*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r desc-fleet-l5lower-default, results = knitr_results, echo = knitr_echo}
fleet_default@L5Lower
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L5Upper {#app:desc-fleet-l5upper-default}


We will not use this functionality by default.
*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r desc-fleet-l5upper-default, results = knitr_results, echo = knitr_echo}
fleet_default@L5Upper
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFSLower {#app:desc-fleet-lfslower-default}


We will not use this functionality by default.
*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r desc-fleet-lfslower-default, results = knitr_results, echo = knitr_echo}
fleet_default@LFSLower
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFSUpper {#app:desc-fleet-lfsupper-default}


We will not use this functionality by default.
*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r desc-fleet-lfsupper-default, results = knitr_results, echo = knitr_echo}
fleet_default@LFSUpper
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### VmaxLower {#app:desc-fleet-vmaxlower-default}


We will not use this functionality by default.
*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction.*

```{r desc-fleet-vmaxlower-default, results = knitr_results, echo = knitr_echo}
fleet_default@VmaxLower
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### VmaxUpper {#app:desc-fleet-vmaxupper-default}


We will not use this functionality by default.
*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction.*

```{r desc-fleet-vmaxupper-default, results = knitr_results, echo = knitr_echo}
fleet_default@VmaxUpper
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### MPA {#app:desc-fleet-mpa-default}

*(Optional) Matrix specifying spatial closures for historical years.*

We will not use this functionality by default.

```{r desc-fleet-mpa-default, results = knitr_results, echo = knitr_echo}
fleet_default@MPA
```
<!-- slot-chunk-end -->

## DEFAULT IMPLEMENTATION SLOTS {#app:desc-imp-default}

```{r warnings = FALSE}
imp_default <- methods::new('Imp')
```

<!-- slot-chunk-begin -->
### TAEFrac {#app:desc-imp-taefrac-default}

*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*

We will not use this functionality by default.

```{r desc-imp-taefrac-default, results = knitr_results, echo = knitr_echo}
imp_default@TAEFrac
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### TAESD {#app:desc-imp-taesd-default}

*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*

We will not use this functionality by default.

```{r desc-imp-taesd-default, results = knitr_results, echo = knitr_echo}
imp_default@TAESD
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### SizeLimFrac {#app:desc-imp-sizelimfrac-default}

*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*

We will not use this functionality by default.

```{r desc-imp-sizelimfrac-default, results = knitr_results, echo = knitr_echo}
imp_default@SizeLimFrac
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### SizeLimSD {#app:desc-imp-sizelimsd-default}

*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*

We will not use this functionality by default.

```{r desc-imp-sizelimsd-default, results = knitr_results, echo = knitr_echo}
imp_default@SizeLimSD
```
<!-- slot-chunk-end -->
