```{r message = FALSE}
library(DLMtool)
knitr_results <- TRUE
knitr_echo <- TRUE
```

## STOCK SLOT DESCRIPTIONS {#app:desc-stock}

```{r warnings = FALSE}
stock <- methods::new('Stock')
```

<!-- autogen-begin -->
### Name {#app:desc-stock-name}

*The name of the Stock object. Single value. Character string*
<!-- autogen-end -->

```{r desc-stock-name, results = knitr_results, echo = knitr_echo}
stock@Name
```

<!-- autogen-begin -->
### Common_Name {#app:desc-stock-common_name}

*Common name of the species. Character string*
<!-- autogen-end -->

```{r desc-stock-common_name, results = knitr_results, echo = knitr_echo}
stock@Common_Name
```

<!-- autogen-begin -->
### Species {#app:desc-stock-species}

*Scientific name of the species. Genus and species name. Character string*
<!-- autogen-end -->

```{r desc-stock-species, results = knitr_results, echo = knitr_echo}
stock@Species
```

<!-- autogen-begin -->
### maxage {#app:desc-stock-maxage}

*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer*
<!-- autogen-end -->

```{r desc-stock-maxage, results = knitr_results, echo = knitr_echo}
stock@maxage
```

<!-- autogen-begin -->
### R0 {#app:desc-stock-r0}

*The magnitude of unfished recruitment. Single value. Positive real number*
<!-- autogen-end -->

```{r desc-stock-r0, results = knitr_results, echo = knitr_echo}
stock@R0
```

<!-- autogen-begin -->
### M {#app:desc-stock-m}

*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number*
<!-- autogen-end -->

```{r desc-stock-m, results = knitr_results, echo = knitr_echo}
stock@M
```

<!-- autogen-begin -->
### M2 {#app:desc-stock-m2}

*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number*
<!-- autogen-end -->

```{r desc-stock-m2, results = knitr_results, echo = knitr_echo}
stock@M2
```

<!-- autogen-begin -->
### Mexp {#app:desc-stock-mexp}

*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*
<!-- autogen-end -->

```{r desc-stock-mexp, results = knitr_results, echo = knitr_echo}
stock@Mexp
```

<!-- autogen-begin -->
### Msd {#app:desc-stock-msd}

*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-stock-msd, results = knitr_results, echo = knitr_echo}
stock@Msd
```

<!-- autogen-begin -->
### h {#app:desc-stock-h}

*Steepness of the stock recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1*
<!-- autogen-end -->

```{r desc-stock-h, results = knitr_results, echo = knitr_echo}
stock@h
```

<!-- autogen-begin -->
### SRrel {#app:desc-stock-srrel}

*Type of stock-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer*
<!-- autogen-end -->

```{r desc-stock-srrel, results = knitr_results, echo = knitr_echo}
stock@SRrel
```

<!-- autogen-begin -->
### Perr {#app:desc-stock-perr}

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-stock-perr, results = knitr_results, echo = knitr_echo}
stock@Perr
```

<!-- autogen-begin -->
### AC {#app:desc-stock-ac}

*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-stock-ac, results = knitr_results, echo = knitr_echo}
stock@AC
```

<!-- autogen-begin -->
### Period {#app:desc-stock-period}

*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-stock-period, results = knitr_results, echo = knitr_echo}
stock@Period
```

<!-- autogen-begin -->
### Amplitude {#app:desc-stock-amplitude}

*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1*
<!-- autogen-end -->

```{r desc-stock-amplitude, results = knitr_results, echo = knitr_echo}
stock@Amplitude
```

<!-- autogen-begin -->
### Linf {#app:desc-stock-linf}

*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-stock-linf, results = knitr_results, echo = knitr_echo}
stock@Linf
```

<!-- autogen-begin -->
### K {#app:desc-stock-k}

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-stock-k, results = knitr_results, echo = knitr_echo}
stock@K
```

<!-- autogen-begin -->
### t0 {#app:desc-stock-t0}

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers*
<!-- autogen-end -->

```{r desc-stock-t0, results = knitr_results, echo = knitr_echo}
stock@t0
```

<!-- autogen-begin -->
### LenCV {#app:desc-stock-lencv}

*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-stock-lencv, results = knitr_results, echo = knitr_echo}
stock@LenCV
```

<!-- autogen-begin -->
### Ksd {#app:desc-stock-ksd}

*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-stock-ksd, results = knitr_results, echo = knitr_echo}
stock@Ksd
```

<!-- autogen-begin -->
### Linfsd {#app:desc-stock-linfsd}

*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-stock-linfsd, results = knitr_results, echo = knitr_echo}
stock@Linfsd
```

<!-- autogen-begin -->
### L50 {#app:desc-stock-l50}

*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-stock-l50, results = knitr_results, echo = knitr_echo}
stock@L50
```

<!-- autogen-begin -->
### L50_95 {#app:desc-stock-l50_95}

*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-stock-l50_95, results = knitr_results, echo = knitr_echo}
stock@L50_95
```

<!-- autogen-begin -->
### D {#app:desc-stock-d}

*Current level of stock depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

```{r desc-stock-d, results = knitr_results, echo = knitr_echo}
stock@D
```

<!-- autogen-begin -->
### a {#app:desc-stock-a}

*Length-weight parameter alpha. Single value. Positive real number*
<!-- autogen-end -->

```{r desc-stock-a, results = knitr_results, echo = knitr_echo}
stock@a
```

<!-- autogen-begin -->
### b {#app:desc-stock-b}

*Length-weight parameter beta. Single value. Positive real number*
<!-- autogen-end -->

```{r desc-stock-b, results = knitr_results, echo = knitr_echo}
stock@b
```

<!-- autogen-begin -->
### Size_area_1 {#app:desc-stock-size_area_1}

*The size of area 1 relative to area 2. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-stock-size_area_1, results = knitr_results, echo = knitr_echo}
stock@Size_area_1
```

<!-- autogen-begin -->
### Frac_area_1 {#app:desc-stock-frac_area_1}

*The fraction of the unfished biomass in stock 1. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-stock-frac_area_1, results = knitr_results, echo = knitr_echo}
stock@Frac_area_1
```

<!-- autogen-begin -->
### Prob_staying {#app:desc-stock-prob_staying}

*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*
<!-- autogen-end -->

```{r desc-stock-prob_staying, results = knitr_results, echo = knitr_echo}
stock@Prob_staying
```

<!-- autogen-begin -->
### Fdisc {#app:desc-stock-fdisc}

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-stock-fdisc, results = knitr_results, echo = knitr_echo}
stock@Fdisc
```

<!-- autogen-begin -->
### Source {#app:desc-stock-source}

*A reference to a website or article from which parameters were taken to define the stock object. Single value. Character string.*
<!-- autogen-end -->

```{r desc-stock-source, results = knitr_results, echo = knitr_echo}
stock@Source
```

## FLEET SLOT DESCRIPTIONS {#app:desc-fleet}

```{r warnings = FALSE}
fleet <- methods::new('Fleet')
```

<!-- autogen-begin -->
### Name {#app:desc-fleet-name}

*Name of the Fleet object. Single value. Character string.*
<!-- autogen-end -->

```{r desc-fleet-name, results = knitr_results, echo = knitr_echo}
fleet@Name
```

<!-- autogen-begin -->
### nyears {#app:desc-fleet-nyears}

*The number of years for the historical spool-up simulation. Single value. Positive integer*
<!-- autogen-end -->

```{r desc-fleet-nyears, results = knitr_results, echo = knitr_echo}
fleet@nyears
```

<!-- autogen-begin -->
### Spat_targ {#app:desc-fleet-spat_targ}

*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers*
<!-- autogen-end -->

```{r desc-fleet-spat_targ, results = knitr_results, echo = knitr_echo}
fleet@Spat_targ
```

<!-- autogen-begin -->
### EffYears {#app:desc-fleet-effyears}

*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-effyears, results = knitr_results, echo = knitr_echo}
fleet@EffYears
```

<!-- autogen-begin -->
### EffLower {#app:desc-fleet-efflower}

*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-efflower, results = knitr_results, echo = knitr_echo}
fleet@EffLower
```

<!-- autogen-begin -->
### EffUpper {#app:desc-fleet-effupper}

*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-effupper, results = knitr_results, echo = knitr_echo}
fleet@EffUpper
```

<!-- autogen-begin -->
### Esd {#app:desc-fleet-esd}

*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-esd, results = knitr_results, echo = knitr_echo}
fleet@Esd
```

<!-- autogen-begin -->
### qinc {#app:desc-fleet-qinc}

*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-qinc, results = knitr_results, echo = knitr_echo}
fleet@qinc
```

<!-- autogen-begin -->
### qcv {#app:desc-fleet-qcv}

*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-qcv, results = knitr_results, echo = knitr_echo}
fleet@qcv
```

<!-- autogen-begin -->
### L5 {#app:desc-fleet-l5}

*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-fleet-l5, results = knitr_results, echo = knitr_echo}
fleet@L5
```

<!-- autogen-begin -->
### LFS {#app:desc-fleet-lfs}

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-fleet-lfs, results = knitr_results, echo = knitr_echo}
fleet@LFS
```

<!-- autogen-begin -->
### Vmaxlen {#app:desc-fleet-vmaxlen}

*The vulnerability of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

```{r desc-fleet-vmaxlen, results = knitr_results, echo = knitr_echo}
fleet@Vmaxlen
```

<!-- autogen-begin -->
### isRel {#app:desc-fleet-isrel}

*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*
<!-- autogen-end -->

```{r desc-fleet-isrel, results = knitr_results, echo = knitr_echo}
fleet@isRel
```

<!-- autogen-begin -->
### LR5 {#app:desc-fleet-lr5}

*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-lr5, results = knitr_results, echo = knitr_echo}
fleet@LR5
```

<!-- autogen-begin -->
### LFR {#app:desc-fleet-lfr}

*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-lfr, results = knitr_results, echo = knitr_echo}
fleet@LFR
```

<!-- autogen-begin -->
### Rmaxlen {#app:desc-fleet-rmaxlen}

*The retention of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-rmaxlen, results = knitr_results, echo = knitr_echo}
fleet@Rmaxlen
```

<!-- autogen-begin -->
### DR {#app:desc-fleet-dr}

*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

```{r desc-fleet-dr, results = knitr_results, echo = knitr_echo}
fleet@DR
```

<!-- autogen-begin -->
### SelYears {#app:desc-fleet-selyears}

*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers*
<!-- autogen-end -->

```{r desc-fleet-selyears, results = knitr_results, echo = knitr_echo}
fleet@SelYears
```

<!-- autogen-begin -->
### AbsSelYears {#app:desc-fleet-absselyears}

*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers*
<!-- autogen-end -->

```{r desc-fleet-absselyears, results = knitr_results, echo = knitr_echo}
fleet@AbsSelYears
```

<!-- autogen-begin -->
### L5Lower {#app:desc-fleet-l5lower}

*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-l5lower, results = knitr_results, echo = knitr_echo}
fleet@L5Lower
```

<!-- autogen-begin -->
### L5Upper {#app:desc-fleet-l5upper}

*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-l5upper, results = knitr_results, echo = knitr_echo}
fleet@L5Upper
```

<!-- autogen-begin -->
### LFSLower {#app:desc-fleet-lfslower}

*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-lfslower, results = knitr_results, echo = knitr_echo}
fleet@LFSLower
```

<!-- autogen-begin -->
### LFSUpper {#app:desc-fleet-lfsupper}

*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-lfsupper, results = knitr_results, echo = knitr_echo}
fleet@LFSUpper
```

<!-- autogen-begin -->
### VmaxLower {#app:desc-fleet-vmaxlower}

*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*
<!-- autogen-end -->

```{r desc-fleet-vmaxlower, results = knitr_results, echo = knitr_echo}
fleet@VmaxLower
```

<!-- autogen-begin -->
### VmaxUpper {#app:desc-fleet-vmaxupper}

*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*
<!-- autogen-end -->

```{r desc-fleet-vmaxupper, results = knitr_results, echo = knitr_echo}
fleet@VmaxUpper
```

<!-- autogen-begin -->
### CurrentYr {#app:desc-fleet-currentyr}

*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*
<!-- autogen-end -->

```{r desc-fleet-currentyr, results = knitr_results, echo = knitr_echo}
fleet@CurrentYr
```

<!-- autogen-begin -->
### MPA {#app:desc-fleet-mpa}

*(Optional) Matrix specifying spatial closures for historical years.*
<!-- autogen-end -->

```{r desc-fleet-mpa, results = knitr_results, echo = knitr_echo}
fleet@MPA
```

## OBS SLOT DESCRIPTIONS {#app:desc-obs}

```{r warnings = FALSE}
obs <- methods::new('Obs')
```

<!-- autogen-begin -->
### Name {#app:desc-obs-name}

*The name of the observation model object. Single value. Character string.*
<!-- autogen-end -->

```{r desc-obs-name, results = knitr_results, echo = knitr_echo}
obs@Name
```

<!-- autogen-begin -->
### Cobs {#app:desc-obs-cobs}

*Log-normal catch observation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-obs-cobs, results = knitr_results, echo = knitr_echo}
obs@Cobs
```

<!-- autogen-begin -->
### Cbiascv {#app:desc-obs-cbiascv}

*Log-normal coefficient of variation controlling the sampling of bias in catch observations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-obs-cbiascv, results = knitr_results, echo = knitr_echo}
obs@Cbiascv
```

<!-- autogen-begin -->
### CAA_nsamp {#app:desc-obs-caa_nsamp}

*Number of catch-at-age observation per time step. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-caa_nsamp, results = knitr_results, echo = knitr_echo}
obs@CAA_nsamp
```

<!-- autogen-begin -->
### CAA_ESS {#app:desc-obs-caa_ess}

*Effective sample size (independent age draws) of the multinomial catch-at-age observation error model. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-obs-caa_ess, results = knitr_results, echo = knitr_echo}
obs@CAA_ESS
```

<!-- autogen-begin -->
### CAL_nsamp {#app:desc-obs-cal_nsamp}

*Number of catch-at-length observation per time step. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-obs-cal_nsamp, results = knitr_results, echo = knitr_echo}
obs@CAL_nsamp
```

<!-- autogen-begin -->
### CAL_ESS {#app:desc-obs-cal_ess}

*Effective sample size (independent length draws) of the multinomial catch-at-length observation error model. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-obs-cal_ess, results = knitr_results, echo = knitr_echo}
obs@CAL_ESS
```

<!-- autogen-begin -->
### Iobs {#app:desc-obs-iobs}

*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-iobs, results = knitr_results, echo = knitr_echo}
obs@Iobs
```

<!-- autogen-begin -->
### Ibiascv {#app:desc-obs-ibiascv}

*Log-normal coefficient of variation controlling error in observations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-ibiascv, results = knitr_results, echo = knitr_echo}
obs@Ibiascv
```

<!-- autogen-begin -->
### Btobs {#app:desc-obs-btobs}

*Log-normal coefficient of variation controlling error in observations of current stock biomass among years. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-btobs, results = knitr_results, echo = knitr_echo}
obs@Btobs
```

<!-- autogen-begin -->
### Btbiascv {#app:desc-obs-btbiascv}

*Uniform-log bounds for sampling persistent bias in current stock biomass. Uniform-log distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-btbiascv, results = knitr_results, echo = knitr_echo}
obs@Btbiascv
```

<!-- autogen-begin -->
### beta {#app:desc-obs-beta}

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-beta, results = knitr_results, echo = knitr_echo}
obs@beta
```

<!-- autogen-begin -->
### LenMbiascv {#app:desc-obs-lenmbiascv}

*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-lenmbiascv, results = knitr_results, echo = knitr_echo}
obs@LenMbiascv
```

<!-- autogen-begin -->
### Mbiascv {#app:desc-obs-mbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-mbiascv, results = knitr_results, echo = knitr_echo}
obs@Mbiascv
```

<!-- autogen-begin -->
### Kbiascv {#app:desc-obs-kbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-kbiascv, results = knitr_results, echo = knitr_echo}
obs@Kbiascv
```

<!-- autogen-begin -->
### t0biascv {#app:desc-obs-t0biascv}

*Log-normal coefficient of variation for sampling persistent bias in observed t0. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-t0biascv, results = knitr_results, echo = knitr_echo}
obs@t0biascv
```

<!-- autogen-begin -->
### Linfbiascv {#app:desc-obs-linfbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed maximum length. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-linfbiascv, results = knitr_results, echo = knitr_echo}
obs@Linfbiascv
```

<!-- autogen-begin -->
### LFCbiascv {#app:desc-obs-lfcbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed length at first capture. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-lfcbiascv, results = knitr_results, echo = knitr_echo}
obs@LFCbiascv
```

<!-- autogen-begin -->
### LFSbiascv {#app:desc-obs-lfsbiascv}

*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-lfsbiascv, results = knitr_results, echo = knitr_echo}
obs@LFSbiascv
```

<!-- autogen-begin -->
### FMSYbiascv {#app:desc-obs-fmsybiascv}

*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-fmsybiascv, results = knitr_results, echo = knitr_echo}
obs@FMSYbiascv
```

<!-- autogen-begin -->
### FMSY_Mbiascv {#app:desc-obs-fmsy_mbiascv}

*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-fmsy_mbiascv, results = knitr_results, echo = knitr_echo}
obs@FMSY_Mbiascv
```

<!-- autogen-begin -->
### BMSY_B0biascv {#app:desc-obs-bmsy_b0biascv}

*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-bmsy_b0biascv, results = knitr_results, echo = knitr_echo}
obs@BMSY_B0biascv
```

<!-- autogen-begin -->
### Irefbiascv {#app:desc-obs-irefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-irefbiascv, results = knitr_results, echo = knitr_echo}
obs@Irefbiascv
```

<!-- autogen-begin -->
### Brefbiascv {#app:desc-obs-brefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-brefbiascv, results = knitr_results, echo = knitr_echo}
obs@Brefbiascv
```

<!-- autogen-begin -->
### Crefbiascv {#app:desc-obs-crefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-crefbiascv, results = knitr_results, echo = knitr_echo}
obs@Crefbiascv
```

<!-- autogen-begin -->
### Dbiascv {#app:desc-obs-dbiascv}

*Log-normal coefficient of variation for sampling persistent bias in stock depletion. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-dbiascv, results = knitr_results, echo = knitr_echo}
obs@Dbiascv
```

<!-- autogen-begin -->
### Dobs {#app:desc-obs-dobs}

*Log-normal coefficient of variation controlling error in observations of stock depletion among years. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-dobs, results = knitr_results, echo = knitr_echo}
obs@Dobs
```

<!-- autogen-begin -->
### hbiascv {#app:desc-obs-hbiascv}

*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-hbiascv, results = knitr_results, echo = knitr_echo}
obs@hbiascv
```

<!-- autogen-begin -->
### Recbiascv {#app:desc-obs-recbiascv}

*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-recbiascv, results = knitr_results, echo = knitr_echo}
obs@Recbiascv
```

## IMP SLOT DESCRIPTIONS {#app:desc-imp}

```{r warnings = FALSE}
imp <- methods::new('Imp')
```

<!-- autogen-begin -->
### Name {#app:desc-imp-name}

*The name of the Implementation error object. Single value. Character string.*
<!-- autogen-end -->

```{r desc-imp-name, results = knitr_results, echo = knitr_echo}
imp@Name
```

<!-- autogen-begin -->
### TACFrac {#app:desc-imp-tacfrac}

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-imp-tacfrac, results = knitr_results, echo = knitr_echo}
imp@TACFrac
```

<!-- autogen-begin -->
### TACSD {#app:desc-imp-tacsd}

*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-imp-tacsd, results = knitr_results, echo = knitr_echo}
imp@TACSD
```

<!-- autogen-begin -->
### TAEFrac {#app:desc-imp-taefrac}

*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-imp-taefrac, results = knitr_results, echo = knitr_echo}
imp@TAEFrac
```

<!-- autogen-begin -->
### TAESD {#app:desc-imp-taesd}

*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-imp-taesd, results = knitr_results, echo = knitr_echo}
imp@TAESD
```

<!-- autogen-begin -->
### SizeLimFrac {#app:desc-imp-sizelimfrac}

*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-imp-sizelimfrac, results = knitr_results, echo = knitr_echo}
imp@SizeLimFrac
```

<!-- autogen-begin -->
### SizeLimSD {#app:desc-imp-sizelimsd}

*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-imp-sizelimsd, results = knitr_results, echo = knitr_echo}
imp@SizeLimSD
```

## OM SLOT DESCRIPTIONS {#app:desc-om}

```{r warnings = FALSE}
om <- methods::new('OM')
```

<!-- autogen-begin -->
### Name {#app:desc-om-name}

*Name of the operating model*
<!-- autogen-end -->

```{r desc-om-name, results = knitr_results, echo = knitr_echo}
om@Name
```

<!-- autogen-begin -->
### Agency {#app:desc-om-agency}

*Name of the agency responsible for the management of the fishery. Character string*
<!-- autogen-end -->

```{r desc-om-agency, results = knitr_results, echo = knitr_echo}
om@Agency
```

<!-- autogen-begin -->
### Region {#app:desc-om-region}

*Name of the general geographic region of the fishery. Character string*
<!-- autogen-end -->

```{r desc-om-region, results = knitr_results, echo = knitr_echo}
om@Region
```

<!-- autogen-begin -->
### Sponsor {#app:desc-om-sponsor}

*Name of the organization who sponsored the OM. Character string*
<!-- autogen-end -->

```{r desc-om-sponsor, results = knitr_results, echo = knitr_echo}
om@Sponsor
```

<!-- autogen-begin -->
### Latitude {#app:desc-om-latitude}

*Latitude (decimal degrees). Negative values represent the South of the Equator. Numeric. Single value*
<!-- autogen-end -->

```{r desc-om-latitude, results = knitr_results, echo = knitr_echo}
om@Latitude
```

<!-- autogen-begin -->
### Longitude {#app:desc-om-longitude}

*Longitude (decimal degrees). Negative values represent the West of the Prime Meridian. Numeric. Single value*
<!-- autogen-end -->

```{r desc-om-longitude, results = knitr_results, echo = knitr_echo}
om@Longitude
```

<!-- autogen-begin -->
### nsim {#app:desc-om-nsim}

*The number of simulations*
<!-- autogen-end -->

```{r desc-om-nsim, results = knitr_results, echo = knitr_echo}
om@nsim
```

<!-- autogen-begin -->
### proyears {#app:desc-om-proyears}

*The number of projected years*
<!-- autogen-end -->

```{r desc-om-proyears, results = knitr_results, echo = knitr_echo}
om@proyears
```

<!-- autogen-begin -->
### interval {#app:desc-om-interval}

*The assessment interval - how often would you like to update the management system?*
<!-- autogen-end -->

```{r desc-om-interval, results = knitr_results, echo = knitr_echo}
om@interval
```

<!-- autogen-begin -->
### pstar {#app:desc-om-pstar}

*The percentile of the sample of the management recommendation for each method*
<!-- autogen-end -->

```{r desc-om-pstar, results = knitr_results, echo = knitr_echo}
om@pstar
```

<!-- autogen-begin -->
### maxF {#app:desc-om-maxf}

*Maximum instantaneous fishing mortality rate that may be simulated for any given age class*
<!-- autogen-end -->

```{r desc-om-maxf, results = knitr_results, echo = knitr_echo}
om@maxF
```

<!-- autogen-begin -->
### reps {#app:desc-om-reps}

*Number of samples of the management recommendation for each method. Note that when this is set to 1, the mean value of the data inputs is used.*
<!-- autogen-end -->

```{r desc-om-reps, results = knitr_results, echo = knitr_echo}
om@reps
```

<!-- autogen-begin -->
### cpars {#app:desc-om-cpars}

*A list of custom parameters. Time series are a matrix nsim rows by nyears columns. Single parameters are a vector nsim long*
<!-- autogen-end -->

```{r desc-om-cpars, results = knitr_results, echo = knitr_echo}
om@cpars
```

<!-- autogen-begin -->
### seed {#app:desc-om-seed}

*A random seed to ensure users can reproduce results exactly*
<!-- autogen-end -->

```{r desc-om-seed, results = knitr_results, echo = knitr_echo}
om@seed
```

<!-- autogen-begin -->
### Source {#app:desc-om-source}

*A reference to a website or article from which parameters were taken to define the operating model*
<!-- autogen-end -->

```{r desc-om-source, results = knitr_results, echo = knitr_echo}
om@Source
```

<!-- autogen-begin -->
### Common_Name {#app:desc-om-common_name}

*Common name of the species. Character string*
<!-- autogen-end -->

```{r desc-om-common_name, results = knitr_results, echo = knitr_echo}
om@Common_Name
```

<!-- autogen-begin -->
### Species {#app:desc-om-species}

*Scientific name of the species. Genus and species name. Character string*
<!-- autogen-end -->

```{r desc-om-species, results = knitr_results, echo = knitr_echo}
om@Species
```

<!-- autogen-begin -->
### maxage {#app:desc-om-maxage}

*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer*
<!-- autogen-end -->

```{r desc-om-maxage, results = knitr_results, echo = knitr_echo}
om@maxage
```

<!-- autogen-begin -->
### R0 {#app:desc-om-r0}

*The magnitude of unfished recruitment. Single value. Positive real number*
<!-- autogen-end -->

```{r desc-om-r0, results = knitr_results, echo = knitr_echo}
om@R0
```

<!-- autogen-begin -->
### M {#app:desc-om-m}

*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number*
<!-- autogen-end -->

```{r desc-om-m, results = knitr_results, echo = knitr_echo}
om@M
```

<!-- autogen-begin -->
### M2 {#app:desc-om-m2}

*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number*
<!-- autogen-end -->

```{r desc-om-m2, results = knitr_results, echo = knitr_echo}
om@M2
```

<!-- autogen-begin -->
### Mexp {#app:desc-om-mexp}

*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*
<!-- autogen-end -->

```{r desc-om-mexp, results = knitr_results, echo = knitr_echo}
om@Mexp
```

<!-- autogen-begin -->
### Msd {#app:desc-om-msd}

*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-msd, results = knitr_results, echo = knitr_echo}
om@Msd
```

<!-- autogen-begin -->
### h {#app:desc-om-h}

*Steepness of the stock recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1*
<!-- autogen-end -->

```{r desc-om-h, results = knitr_results, echo = knitr_echo}
om@h
```

<!-- autogen-begin -->
### SRrel {#app:desc-om-srrel}

*Type of stock-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer*
<!-- autogen-end -->

```{r desc-om-srrel, results = knitr_results, echo = knitr_echo}
om@SRrel
```

<!-- autogen-begin -->
### Perr {#app:desc-om-perr}

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-perr, results = knitr_results, echo = knitr_echo}
om@Perr
```

<!-- autogen-begin -->
### AC {#app:desc-om-ac}

*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-ac, results = knitr_results, echo = knitr_echo}
om@AC
```

<!-- autogen-begin -->
### Period {#app:desc-om-period}

*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-period, results = knitr_results, echo = knitr_echo}
om@Period
```

<!-- autogen-begin -->
### Amplitude {#app:desc-om-amplitude}

*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1*
<!-- autogen-end -->

```{r desc-om-amplitude, results = knitr_results, echo = knitr_echo}
om@Amplitude
```

<!-- autogen-begin -->
### Linf {#app:desc-om-linf}

*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-linf, results = knitr_results, echo = knitr_echo}
om@Linf
```

<!-- autogen-begin -->
### K {#app:desc-om-k}

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-k, results = knitr_results, echo = knitr_echo}
om@K
```

<!-- autogen-begin -->
### t0 {#app:desc-om-t0}

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers*
<!-- autogen-end -->

```{r desc-om-t0, results = knitr_results, echo = knitr_echo}
om@t0
```

<!-- autogen-begin -->
### LenCV {#app:desc-om-lencv}

*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-lencv, results = knitr_results, echo = knitr_echo}
om@LenCV
```

<!-- autogen-begin -->
### Ksd {#app:desc-om-ksd}

*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-ksd, results = knitr_results, echo = knitr_echo}
om@Ksd
```

<!-- autogen-begin -->
### Linfsd {#app:desc-om-linfsd}

*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-linfsd, results = knitr_results, echo = knitr_echo}
om@Linfsd
```

<!-- autogen-begin -->
### L50 {#app:desc-om-l50}

*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-l50, results = knitr_results, echo = knitr_echo}
om@L50
```

<!-- autogen-begin -->
### L50_95 {#app:desc-om-l50_95}

*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-l50_95, results = knitr_results, echo = knitr_echo}
om@L50_95
```

<!-- autogen-begin -->
### D {#app:desc-om-d}

*Current level of stock depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

```{r desc-om-d, results = knitr_results, echo = knitr_echo}
om@D
```

<!-- autogen-begin -->
### a {#app:desc-om-a}

*Length-weight parameter alpha. Single value. Positive real number*
<!-- autogen-end -->

```{r desc-om-a, results = knitr_results, echo = knitr_echo}
om@a
```

<!-- autogen-begin -->
### b {#app:desc-om-b}

*Length-weight parameter beta. Single value. Positive real number*
<!-- autogen-end -->

```{r desc-om-b, results = knitr_results, echo = knitr_echo}
om@b
```

<!-- autogen-begin -->
### Size_area_1 {#app:desc-om-size_area_1}

*The size of area 1 relative to area 2. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-size_area_1, results = knitr_results, echo = knitr_echo}
om@Size_area_1
```

<!-- autogen-begin -->
### Frac_area_1 {#app:desc-om-frac_area_1}

*The fraction of the unfished biomass in stock 1. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-frac_area_1, results = knitr_results, echo = knitr_echo}
om@Frac_area_1
```

<!-- autogen-begin -->
### Prob_staying {#app:desc-om-prob_staying}

*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*
<!-- autogen-end -->

```{r desc-om-prob_staying, results = knitr_results, echo = knitr_echo}
om@Prob_staying
```

<!-- autogen-begin -->
### Fdisc {#app:desc-om-fdisc}

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-fdisc, results = knitr_results, echo = knitr_echo}
om@Fdisc
```

<!-- autogen-begin -->
### nyears {#app:desc-om-nyears}

*The number of years for the historical spool-up simulation. Single value. Positive integer*
<!-- autogen-end -->

```{r desc-om-nyears, results = knitr_results, echo = knitr_echo}
om@nyears
```

<!-- autogen-begin -->
### Spat_targ {#app:desc-om-spat_targ}

*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers*
<!-- autogen-end -->

```{r desc-om-spat_targ, results = knitr_results, echo = knitr_echo}
om@Spat_targ
```

<!-- autogen-begin -->
### EffYears {#app:desc-om-effyears}

*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-effyears, results = knitr_results, echo = knitr_echo}
om@EffYears
```

<!-- autogen-begin -->
### EffLower {#app:desc-om-efflower}

*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-efflower, results = knitr_results, echo = knitr_echo}
om@EffLower
```

<!-- autogen-begin -->
### EffUpper {#app:desc-om-effupper}

*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-effupper, results = knitr_results, echo = knitr_echo}
om@EffUpper
```

<!-- autogen-begin -->
### Esd {#app:desc-om-esd}

*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-esd, results = knitr_results, echo = knitr_echo}
om@Esd
```

<!-- autogen-begin -->
### qinc {#app:desc-om-qinc}

*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-qinc, results = knitr_results, echo = knitr_echo}
om@qinc
```

<!-- autogen-begin -->
### qcv {#app:desc-om-qcv}

*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-qcv, results = knitr_results, echo = knitr_echo}
om@qcv
```

<!-- autogen-begin -->
### L5 {#app:desc-om-l5}

*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-l5, results = knitr_results, echo = knitr_echo}
om@L5
```

<!-- autogen-begin -->
### LFS {#app:desc-om-lfs}

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-lfs, results = knitr_results, echo = knitr_echo}
om@LFS
```

<!-- autogen-begin -->
### Vmaxlen {#app:desc-om-vmaxlen}

*The vulnerability of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

```{r desc-om-vmaxlen, results = knitr_results, echo = knitr_echo}
om@Vmaxlen
```

<!-- autogen-begin -->
### isRel {#app:desc-om-isrel}

*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*
<!-- autogen-end -->

```{r desc-om-isrel, results = knitr_results, echo = knitr_echo}
om@isRel
```

<!-- autogen-begin -->
### LR5 {#app:desc-om-lr5}

*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-lr5, results = knitr_results, echo = knitr_echo}
om@LR5
```

<!-- autogen-begin -->
### LFR {#app:desc-om-lfr}

*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-lfr, results = knitr_results, echo = knitr_echo}
om@LFR
```

<!-- autogen-begin -->
### Rmaxlen {#app:desc-om-rmaxlen}

*The retention of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-rmaxlen, results = knitr_results, echo = knitr_echo}
om@Rmaxlen
```

<!-- autogen-begin -->
### DR {#app:desc-om-dr}

*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

```{r desc-om-dr, results = knitr_results, echo = knitr_echo}
om@DR
```

<!-- autogen-begin -->
### SelYears {#app:desc-om-selyears}

*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-selyears, results = knitr_results, echo = knitr_echo}
om@SelYears
```

<!-- autogen-begin -->
### AbsSelYears {#app:desc-om-absselyears}

*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers*
<!-- autogen-end -->

```{r desc-om-absselyears, results = knitr_results, echo = knitr_echo}
om@AbsSelYears
```

<!-- autogen-begin -->
### L5Lower {#app:desc-om-l5lower}

*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-l5lower, results = knitr_results, echo = knitr_echo}
om@L5Lower
```

<!-- autogen-begin -->
### L5Upper {#app:desc-om-l5upper}

*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-l5upper, results = knitr_results, echo = knitr_echo}
om@L5Upper
```

<!-- autogen-begin -->
### LFSLower {#app:desc-om-lfslower}

*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-lfslower, results = knitr_results, echo = knitr_echo}
om@LFSLower
```

<!-- autogen-begin -->
### LFSUpper {#app:desc-om-lfsupper}

*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-lfsupper, results = knitr_results, echo = knitr_echo}
om@LFSUpper
```

<!-- autogen-begin -->
### VmaxLower {#app:desc-om-vmaxlower}

*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*
<!-- autogen-end -->

```{r desc-om-vmaxlower, results = knitr_results, echo = knitr_echo}
om@VmaxLower
```

<!-- autogen-begin -->
### VmaxUpper {#app:desc-om-vmaxupper}

*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*
<!-- autogen-end -->

```{r desc-om-vmaxupper, results = knitr_results, echo = knitr_echo}
om@VmaxUpper
```

<!-- autogen-begin -->
### CurrentYr {#app:desc-om-currentyr}

*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*
<!-- autogen-end -->

```{r desc-om-currentyr, results = knitr_results, echo = knitr_echo}
om@CurrentYr
```

<!-- autogen-begin -->
### MPA {#app:desc-om-mpa}

*(Optional) Matrix specifying spatial closures for historical years.*
<!-- autogen-end -->

```{r desc-om-mpa, results = knitr_results, echo = knitr_echo}
om@MPA
```

<!-- autogen-begin -->
### Cobs {#app:desc-om-cobs}

*Log-normal catch observation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-cobs, results = knitr_results, echo = knitr_echo}
om@Cobs
```

<!-- autogen-begin -->
### Cbiascv {#app:desc-om-cbiascv}

*Log-normal coefficient of variation controlling the sampling of bias in catch observations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-om-cbiascv, results = knitr_results, echo = knitr_echo}
om@Cbiascv
```

<!-- autogen-begin -->
### CAA_nsamp {#app:desc-om-caa_nsamp}

*Number of catch-at-age observation per time step. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-caa_nsamp, results = knitr_results, echo = knitr_echo}
om@CAA_nsamp
```

<!-- autogen-begin -->
### CAA_ESS {#app:desc-om-caa_ess}

*Effective sample size (independent age draws) of the multinomial catch-at-age observation error model. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-om-caa_ess, results = knitr_results, echo = knitr_echo}
om@CAA_ESS
```

<!-- autogen-begin -->
### CAL_nsamp {#app:desc-om-cal_nsamp}

*Number of catch-at-length observation per time step. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-om-cal_nsamp, results = knitr_results, echo = knitr_echo}
om@CAL_nsamp
```

<!-- autogen-begin -->
### CAL_ESS {#app:desc-om-cal_ess}

*Effective sample size (independent length draws) of the multinomial catch-at-length observation error model. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-om-cal_ess, results = knitr_results, echo = knitr_echo}
om@CAL_ESS
```

<!-- autogen-begin -->
### Iobs {#app:desc-om-iobs}

*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-iobs, results = knitr_results, echo = knitr_echo}
om@Iobs
```

<!-- autogen-begin -->
### Ibiascv {#app:desc-om-ibiascv}

*Log-normal coefficient of variation controlling error in observations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-ibiascv, results = knitr_results, echo = knitr_echo}
om@Ibiascv
```

<!-- autogen-begin -->
### Btobs {#app:desc-om-btobs}

*Log-normal coefficient of variation controlling error in observations of current stock biomass among years. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-btobs, results = knitr_results, echo = knitr_echo}
om@Btobs
```

<!-- autogen-begin -->
### Btbiascv {#app:desc-om-btbiascv}

*Uniform-log bounds for sampling persistent bias in current stock biomass. Uniform-log distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-btbiascv, results = knitr_results, echo = knitr_echo}
om@Btbiascv
```

<!-- autogen-begin -->
### beta {#app:desc-om-beta}

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-beta, results = knitr_results, echo = knitr_echo}
om@beta
```

<!-- autogen-begin -->
### LenMbiascv {#app:desc-om-lenmbiascv}

*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-lenmbiascv, results = knitr_results, echo = knitr_echo}
om@LenMbiascv
```

<!-- autogen-begin -->
### Mbiascv {#app:desc-om-mbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-mbiascv, results = knitr_results, echo = knitr_echo}
om@Mbiascv
```

<!-- autogen-begin -->
### Kbiascv {#app:desc-om-kbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-kbiascv, results = knitr_results, echo = knitr_echo}
om@Kbiascv
```

<!-- autogen-begin -->
### t0biascv {#app:desc-om-t0biascv}

*Log-normal coefficient of variation for sampling persistent bias in observed t0. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-t0biascv, results = knitr_results, echo = knitr_echo}
om@t0biascv
```

<!-- autogen-begin -->
### Linfbiascv {#app:desc-om-linfbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed maximum length. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-linfbiascv, results = knitr_results, echo = knitr_echo}
om@Linfbiascv
```

<!-- autogen-begin -->
### LFCbiascv {#app:desc-om-lfcbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed length at first capture. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-lfcbiascv, results = knitr_results, echo = knitr_echo}
om@LFCbiascv
```

<!-- autogen-begin -->
### LFSbiascv {#app:desc-om-lfsbiascv}

*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-lfsbiascv, results = knitr_results, echo = knitr_echo}
om@LFSbiascv
```

<!-- autogen-begin -->
### FMSYbiascv {#app:desc-om-fmsybiascv}

*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-fmsybiascv, results = knitr_results, echo = knitr_echo}
om@FMSYbiascv
```

<!-- autogen-begin -->
### FMSY_Mbiascv {#app:desc-om-fmsy_mbiascv}

*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-fmsy_mbiascv, results = knitr_results, echo = knitr_echo}
om@FMSY_Mbiascv
```

<!-- autogen-begin -->
### BMSY_B0biascv {#app:desc-om-bmsy_b0biascv}

*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-bmsy_b0biascv, results = knitr_results, echo = knitr_echo}
om@BMSY_B0biascv
```

<!-- autogen-begin -->
### Irefbiascv {#app:desc-om-irefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-irefbiascv, results = knitr_results, echo = knitr_echo}
om@Irefbiascv
```

<!-- autogen-begin -->
### Brefbiascv {#app:desc-om-brefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-brefbiascv, results = knitr_results, echo = knitr_echo}
om@Brefbiascv
```

<!-- autogen-begin -->
### Crefbiascv {#app:desc-om-crefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-crefbiascv, results = knitr_results, echo = knitr_echo}
om@Crefbiascv
```

<!-- autogen-begin -->
### Dbiascv {#app:desc-om-dbiascv}

*Log-normal coefficient of variation for sampling persistent bias in stock depletion. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-dbiascv, results = knitr_results, echo = knitr_echo}
om@Dbiascv
```

<!-- autogen-begin -->
### Dobs {#app:desc-om-dobs}

*Log-normal coefficient of variation controlling error in observations of stock depletion among years. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-dobs, results = knitr_results, echo = knitr_echo}
om@Dobs
```

<!-- autogen-begin -->
### hbiascv {#app:desc-om-hbiascv}

*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-hbiascv, results = knitr_results, echo = knitr_echo}
om@hbiascv
```

<!-- autogen-begin -->
### Recbiascv {#app:desc-om-recbiascv}

*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-om-recbiascv, results = knitr_results, echo = knitr_echo}
om@Recbiascv
```

<!-- autogen-begin -->
### TACFrac {#app:desc-om-tacfrac}

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-om-tacfrac, results = knitr_results, echo = knitr_echo}
om@TACFrac
```

<!-- autogen-begin -->
### TACSD {#app:desc-om-tacsd}

*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-om-tacsd, results = knitr_results, echo = knitr_echo}
om@TACSD
```

<!-- autogen-begin -->
### TAEFrac {#app:desc-om-taefrac}

*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-om-taefrac, results = knitr_results, echo = knitr_echo}
om@TAEFrac
```

<!-- autogen-begin -->
### TAESD {#app:desc-om-taesd}

*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-om-taesd, results = knitr_results, echo = knitr_echo}
om@TAESD
```

<!-- autogen-begin -->
### SizeLimFrac {#app:desc-om-sizelimfrac}

*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-om-sizelimfrac, results = knitr_results, echo = knitr_echo}
om@SizeLimFrac
```

<!-- autogen-begin -->
### SizeLimSD {#app:desc-om-sizelimsd}

*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-om-sizelimsd, results = knitr_results, echo = knitr_echo}
om@SizeLimSD
```

