`r if(knitr:::is_latex_output()) '\\Appendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

# OPERATING MODEL SPECIFICATION {#app:desc-om}

```{r message = FALSE}
library(DLMtool)
knitr_results <- TRUE
knitr_echo <- TRUE
```

```{r download-data}
science_name <- "Sebastes borealis"
species_name <- "shortraker rockfish"
species_file <- here::here("generated-data",
  paste0(gsub(" ", "-", species_name), ".rds"))
if (!file.exists(species_file)) {
  d <- list()
  d$commercial_samples <- gfplot::get_commercial_samples(species_name)
  d$survey_samples <- gfplot::get_survey_samples(species_name)
  d$catch <- gfplot::get_catch(species_name)
  d$survey_index <- gfplot::get_survey_index(species_name)
  saveRDS(d, file = species_file)
} else {
  d <- readRDS(species_file)
}
```

## STOCK SLOT DESCRIPTIONS {#app:desc-stock}

```{r warnings = FALSE}
stock <- methods::new('Stock')
```

<!-- autogen-begin -->
### Name {#app:desc-stock-name}

*The name of the Stock object. Single value. Character string*
<!-- autogen-end -->

```{r desc-stock-name, results = knitr_results, echo = knitr_echo}
stock@Name <- "Shortraker Rockfish Coastwide Stock"
```

<!-- autogen-begin -->
### Common_Name {#app:desc-stock-common_name}

*Common name of the species. Character string*
<!-- autogen-end -->

```{r desc-stock-common_name, results = knitr_results, echo = knitr_echo}
stock@Common_Name <- "Shortraker Rockfish"
```

<!-- autogen-begin -->
### Species {#app:desc-stock-species}

*Scientific name of the species. Genus and species name. Character string*
<!-- autogen-end -->

```{r desc-stock-species, results = knitr_results, echo = knitr_echo}
stock@Species <- "Sebastes borealis"
```

<!-- autogen-begin -->
### maxage {#app:desc-stock-maxage}

*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer*
<!-- autogen-end -->

```{r desc-stock-maxage, results = knitr_results, echo = knitr_echo}
stock@maxage <- max(d$survey_samples$age, d$commercial_samples$age, na.rm = TRUE)
```

<!-- autogen-begin -->
### R0 {#app:desc-stock-r0}

*The magnitude of unfished recruitment. Single value. Positive real number*
<!-- autogen-end -->

The absolute value is meaningless here. Arbitrarily pick a value.

```{r desc-stock-r0, results = knitr_results, echo = knitr_echo}
stock@R0 <- 1000
```

<!-- autogen-begin -->
### M {#app:desc-stock-m}

*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number*
<!-- autogen-end -->

@echave2015 estimate natural mortality in the Gulf of Alaska to be 0.03. We will place some relatively wide bounds around that.

```{r desc-stock-m, results = knitr_results, echo = knitr_echo}
stock@M <- c(0.02, 0.10)
```

<!-- autogen-begin -->
### M2 {#app:desc-stock-m2}

*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number*
<!-- autogen-end -->

Not used.

```{r desc-stock-m2, results = knitr_results, echo = knitr_echo}
stock@M2
```

<!-- autogen-begin -->
### Mexp {#app:desc-stock-mexp}

*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*
<!-- autogen-end -->

Not used.

```{r desc-stock-mexp, results = knitr_results, echo = knitr_echo}
stock@Mexp <- c(NA_real_, NA_real_)
```

<!-- autogen-begin -->
### Msd {#app:desc-stock-msd}

*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

Unknown. Picking an arbitrary range.

```{r desc-stock-msd, results = knitr_results, echo = knitr_echo}
stock@Msd <- c(0.00, 0.05)
```

<!-- autogen-begin -->
### h {#app:desc-stock-h}

*Steepness of the stock recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1*
<!-- autogen-end -->

FIXME: parameterize this from a meta-analysis

```{r desc-stock-h, results = knitr_results, echo = knitr_echo}
stock@h <- c(0.345, 0.720)
```

<!-- autogen-begin -->
### SRrel {#app:desc-stock-srrel}

*Type of stock-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer*
<!-- autogen-end -->

We will choose a Beverton-Holt.

```{r desc-stock-srrel, results = knitr_results, echo = knitr_echo}
stock@SRrel <- 1L
```

<!-- autogen-begin -->
### Perr {#app:desc-stock-perr}

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

@thorson2014 finds the mean SD of recruitment deviations in log space to be ballpark 0.6--0.8. Here, we will extend that range slightly.

FIXME: Need to look for data in other assessments of similar rockfish species or of shortraker in other regions.

```{r desc-stock-perr, results = knitr_results, echo = knitr_echo}
stock@Perr <- c(0.5, 0.9)
```

<!-- autogen-begin -->
### AC {#app:desc-stock-ac}

*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

FIXME: look into meta- analyses. For now we will bound this with a wide range of possibilities.

```{r desc-stock-ac, results = knitr_results, echo = knitr_echo}
stock@AC <- c(0.1, 0.9)
```

<!-- autogen-begin -->
### Period {#app:desc-stock-period}

*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

Not used.

```{r desc-stock-period, results = knitr_results, echo = knitr_echo}
stock@Period
```

<!-- autogen-begin -->
### Amplitude {#app:desc-stock-amplitude}

*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1*
<!-- autogen-end -->

Not used.

```{r desc-stock-amplitude, results = knitr_results, echo = knitr_echo}
stock@Amplitude
```

<!-- autogen-begin -->
### Linf {#app:desc-stock-linf}

*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r load-stan, message=FALSE, warning=FALSE}
suppressPackageStartupMessages(library("rstan"))
```

```{r fit-vb, echo = knitr_echo, out.width="4in", fig.width=6, warnings = FALSE}
mvb <- gfplot::fit_vb(d$survey_samples, sex = "all")

# for cpars:
# mvb_stan <- gfplot::fit_vb(d$survey_samples, sex = "all", method = "mcmc",
#   control = list(adapt_delta = 0.99), iter = 500, chains = 4)

mvb_summary <- summary(TMB::sdreport(mvb$model))
vb_cv <- mvb_summary[,"Std. Error"] / abs(mvb_summary[,"Estimate"])
gfplot::plot_vb(object_all = mvb, col = c("All" = "black"))
```

<!--   # # obj@LenCV <- sd2cv(exp(mvb$pars[["log_sigma"]])) -->
<!--   # obj@CV_vbK <- cv[["k"]] -->
<!--   # obj@CV_vbLinf <- cv[["linf"]] -->
<!--   # obj@CV_vbt0 <- cv[["t0"]] -->
<!-- ``` -->

We will grab this from our data analysis:

```{r desc-stock-linf, results = knitr_results, echo = knitr_echo}
stock@Linf <- c(-2, 2) * mvb_summary[,"Std. Error"][["linf"]] + mvb$pars[["linf"]]
```

<!-- autogen-begin -->
### K {#app:desc-stock-k}

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

We will grab this from our data analysis:

```{r desc-stock-k, results = knitr_results, echo = knitr_echo}
stock@K <-c(-2, 2) * mvb_summary[,"Std. Error"][["k"]] + mvb$pars[["k"]]
```

<!-- autogen-begin -->
### t0 {#app:desc-stock-t0}

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers*
<!-- autogen-end -->

We will grab this from our data analysis:

```{r desc-stock-t0, results = knitr_results, echo = knitr_echo}
stock@t0 <- c(-2, 2) *  mvb_summary[,"Std. Error"][["t0"]] + mvb$pars[["t0"]]
```

<!-- autogen-begin -->
### LenCV {#app:desc-stock-lencv}

*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

We will grab this from our data analysis:

```{r desc-stock-lencv, results = knitr_results, echo = knitr_echo}
sd2cv <- function(.sd) sqrt(exp(.sd^2) - 1)
stock@LenCV <- sd2cv(exp(mvb$pars[["log_sigma"]]))
round(stock@LenCV, 2)
```

<!-- autogen-begin -->
### Ksd {#app:desc-stock-ksd}

*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

FIXME: pick this.

```{r desc-stock-ksd, results = knitr_results, echo = knitr_echo}
stock@Ksd <- c(0, 0.2)
```

<!-- autogen-begin -->
### Linfsd {#app:desc-stock-linfsd}

*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

FIXME: We will grab this from our data analysis:

```{r desc-stock-linfsd, results = knitr_results, echo = knitr_echo}
stock@Linfsd <- c(0.05, 0.2)
```

<!-- autogen-begin -->
### L50 {#app:desc-stock-l50}

*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r fit-maturity, echo = knitr_echo, out.width="4in", fig.width=6}
m_mat <- gfplot::fit_mat_ogive(d$survey_samples, type = "length")
mat_perc <- pbs2dlm:::extract_maturity_perc(coef(m_mat$model))
se_l50 <- pbs2dlm:::delta_method(~ -(log((1/0.5) - 1) + x1 + x3) / (x2 + x4),
    mean = coef(m_mat$model), cov = vcov(m_mat$model))
gfplot::plot_mat_ogive(m_mat)
```

From our model, length that 50% maturity for females is calculated as `r round(mat_perc$f.p0.5, 1)` with a standard error of `r round(se_l50, 1)`. Let's pick a range that is roughly the 95% confidence interval around the estimated length that 50% maturity. Length the maturity looks similar for males and females.

```{r desc-stock-l50, results = knitr_results, echo = knitr_echo}
stock@L50 <- round(c(-2, 2) * se_l50 + mat_perc$f.p0.5, 1)
stock@L50
```

<!-- autogen-begin -->
### L50_95 {#app:desc-stock-l50_95}

*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

Similarly we will calculate the increment in length from 50% to 95% maturity.

```{r desc-stock-l50_95, results = knitr_results, echo = knitr_echo}
# TODO: Yikes! Need to check this delta method implementation.
se_l50_95m <- pbs2dlm:::delta_method(
  ~ -(log((1/0.95) - 1) + x1 + x3) / (x2 + x4) - 
    -(log((1/0.5) - 1) + x1 + x3) / (x2 + x4),
    mean = coef(m_mat$model), cov = vcov(m_mat$model))
stock@L50_95 <- round(c(-2, 2) * se_l50_95m + (mat_perc$f.p0.95 - mat_perc$f.p0.5), 1)
stock@L50_95
```

<!-- autogen-begin -->
### D {#app:desc-stock-d}

*Current level of stock depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

TODO: We are probably going to have to bound some reasonable numbers here unless we can fit a basic model such as a surplus production model or a length-based model. 

```{r desc-stock-d, results = knitr_results, echo = knitr_echo}
stock@D <- c(0.1, 0.8)
```

<!-- autogen-begin -->
### a {#app:desc-stock-a}

*Length-weight parameter alpha. Single value. Positive real number*
<!-- autogen-end -->

We can fit a length-weight growth model with gfplot:

```{r fit-lw, echo = knitr_echo, out.width="4in", fig.width=6}
mlw <- gfplot::fit_length_weight(d$survey_samples, sex = "all")

gfplot::plot_length_weight(object_all = mlw, col = c("All" = "black"))
```

We can fill this slot from our fitted model.

```{r desc-stock-a, results = knitr_results, echo = knitr_echo}
stock@a <- exp(mlw$pars[["log_a"]])
round(log(stock@a), 2)
```

<!-- autogen-begin -->
### b {#app:desc-stock-b}

*Length-weight parameter beta. Single value. Positive real number*
<!-- autogen-end -->

We can take this from our fitted model.

```{r desc-stock-b, results = knitr_results, echo = knitr_echo}
stock@b <- mlw$pars[["b"]]
round(stock@b, 2)
```

<!-- autogen-begin -->
### Size_area_1 {#app:desc-stock-size_area_1}

*The size of area 1 relative to area 2. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

Area 1 represents habitat outside of the range of fishing. TODO: we may be able to come up with some ballpark numbers from looking at the distribution of commercial effort and the predicted distribution of the species from the spatiotemporal models. For now, we will arbitrarily set this.

```{r desc-stock-size_area_1, results = knitr_results, echo = knitr_echo}
stock@Size_area_1 <- c(0, 0.5)
```

<!-- autogen-begin -->
### Frac_area_1 {#app:desc-stock-frac_area_1}

*The fraction of the unfished biomass in stock 1. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

For now, we will set this to the same fraction as the size of area 1.

```{r desc-stock-frac_area_1, results = knitr_results, echo = knitr_echo}
stock@Frac_area_1 <- c(0, 0.5)
```

<!-- autogen-begin -->
### Prob_staying {#app:desc-stock-prob_staying}

*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*
<!-- autogen-end -->

We probably don't have a lot of information on this. For now, we will set this to a wide range of possible values.

```{r desc-stock-prob_staying, results = knitr_results, echo = knitr_echo}
stock@Prob_staying <- c(0.1, 0.9)
```

<!-- autogen-begin -->
### Fdisc {#app:desc-stock-fdisc}

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

TODO: pull from some studies on this but I imagine the value is pretty close to 1.

```{r desc-stock-fdisc, results = knitr_results, echo = knitr_echo}
stock@Fdisc <- 1
```

<!-- autogen-begin -->
### Source {#app:desc-stock-source}

*A reference to a website or article from which parameters were taken to define the stock object. Single value. Character string.*
<!-- autogen-end -->

```{r desc-stock-source, results = knitr_results, echo = knitr_echo}
stock@Source <- "" 
```

## FLEET SLOT DESCRIPTIONS {#app:desc-fleet}

```{r warnings = FALSE}
fleet <- methods::new('Fleet')
fleet <- DLMtool::Generic_Fleet # TODO: temporary
```

<!-- autogen-begin -->
### Name {#app:desc-fleet-name}

*Name of the Fleet object. Single value. Character string.*
<!-- autogen-end -->

```{r desc-fleet-name, results = knitr_results, echo = knitr_echo}
fleet@Name <- "BC Fleet"
```

<!-- autogen-begin -->
### nyears {#app:desc-fleet-nyears}

*The number of years for the historical spool-up simulation. Single value. Positive integer*
<!-- autogen-end -->

We will set the historical run-up to be approximately the length of the commercial fishery:

```{r desc-fleet-nyears, results = knitr_results, echo = knitr_echo}
fleet@nyears <- 50
```

<!-- autogen-begin -->
### Spat_targ {#app:desc-fleet-spat_targ}

*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers*
<!-- autogen-end -->

```{r desc-fleet-spat_targ, results = knitr_results, echo = knitr_echo}
fleet@Spat_targ
```

<!-- autogen-begin -->
### EffYears {#app:desc-fleet-effyears}

*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers*
<!-- autogen-end -->

TODO: May need to come up with some plausible scenarios for these effort trajectories.

For now we will start with the simplest trajectory of fairly constant fishing effort at a wide and unknown range:

```{r desc-fleet-effyears, results = knitr_results, echo = knitr_echo}
fleet@EffYears <- c(0, 0.5, 1)
```

<!-- autogen-begin -->
### EffLower {#app:desc-fleet-efflower}

*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*
<!-- autogen-end -->

TODO: May need to come up with some plausible scenarios for these effort trajectories.

```{r desc-fleet-efflower, results = knitr_results, echo = knitr_echo}
fleet@EffLower <- c(0, 0.2, 0.2)
```

<!-- autogen-begin -->
### EffUpper {#app:desc-fleet-effupper}

*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*
<!-- autogen-end -->

TODO: May need to come up with some plausible scenarios for these effort trajectories.

```{r desc-fleet-effupper, results = knitr_results, echo = knitr_echo}
fleet@EffUpper <- c(0.5, 1, 1)
```

<!-- autogen-begin -->
### Esd {#app:desc-fleet-esd}

*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

TODO: We don't have a lot of data to go on for this. For now, stick with the default.

```{r desc-fleet-esd, results = knitr_results, echo = knitr_echo}
fleet@Esd
```

<!-- autogen-begin -->
### qinc {#app:desc-fleet-qinc}

*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

TODO: We don't have a lot of data to go on for this. For now, stick with the default which is a fairly wide bound.

```{r desc-fleet-qinc, results = knitr_results, echo = knitr_echo}
fleet@qinc
```

<!-- autogen-begin -->
### qcv {#app:desc-fleet-qcv}

*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

TODO: Same as above.

```{r desc-fleet-qcv, results = knitr_results, echo = knitr_echo}
fleet@qcv
```

<!-- autogen-begin -->
### L5 {#app:desc-fleet-l5}

*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-fleet-l5, results = knitr_results, echo = knitr_echo}
fleet@L5
```

<!-- autogen-begin -->
### LFS {#app:desc-fleet-lfs}

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-fleet-lfs, results = knitr_results, echo = knitr_echo}
fleet@LFS
```

<!-- autogen-begin -->
### Vmaxlen {#app:desc-fleet-vmaxlen}

*The vulnerability of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

```{r desc-fleet-vmaxlen, results = knitr_results, echo = knitr_echo}
fleet@Vmaxlen
```

<!-- autogen-begin -->
### isRel {#app:desc-fleet-isrel}

*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*
<!-- autogen-end -->

```{r desc-fleet-isrel, results = knitr_results, echo = knitr_echo}
fleet@isRel
```

<!-- autogen-begin -->
### LR5 {#app:desc-fleet-lr5}

*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-lr5, results = knitr_results, echo = knitr_echo}
fleet@LR5
```

<!-- autogen-begin -->
### LFR {#app:desc-fleet-lfr}

*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-lfr, results = knitr_results, echo = knitr_echo}
fleet@LFR
```

<!-- autogen-begin -->
### Rmaxlen {#app:desc-fleet-rmaxlen}

*The retention of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-rmaxlen, results = knitr_results, echo = knitr_echo}
fleet@Rmaxlen
```

<!-- autogen-begin -->
### DR {#app:desc-fleet-dr}

*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction*
<!-- autogen-end -->

```{r desc-fleet-dr, results = knitr_results, echo = knitr_echo}
fleet@DR
```

<!-- autogen-begin -->
### SelYears {#app:desc-fleet-selyears}

*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers*
<!-- autogen-end -->

```{r desc-fleet-selyears, results = knitr_results, echo = knitr_echo}
fleet@SelYears
```

<!-- autogen-begin -->
### AbsSelYears {#app:desc-fleet-absselyears}

*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers*
<!-- autogen-end -->

```{r desc-fleet-absselyears, results = knitr_results, echo = knitr_echo}
fleet@AbsSelYears
```

<!-- autogen-begin -->
### L5Lower {#app:desc-fleet-l5lower}

*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-l5lower, results = knitr_results, echo = knitr_echo}
fleet@L5Lower
```

<!-- autogen-begin -->
### L5Upper {#app:desc-fleet-l5upper}

*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-l5upper, results = knitr_results, echo = knitr_echo}
fleet@L5Upper
```

<!-- autogen-begin -->
### LFSLower {#app:desc-fleet-lfslower}

*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-lfslower, results = knitr_results, echo = knitr_echo}
fleet@LFSLower
```

<!-- autogen-begin -->
### LFSUpper {#app:desc-fleet-lfsupper}

*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-fleet-lfsupper, results = knitr_results, echo = knitr_echo}
fleet@LFSUpper
```

<!-- autogen-begin -->
### VmaxLower {#app:desc-fleet-vmaxlower}

*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*
<!-- autogen-end -->

```{r desc-fleet-vmaxlower, results = knitr_results, echo = knitr_echo}
fleet@VmaxLower
```

<!-- autogen-begin -->
### VmaxUpper {#app:desc-fleet-vmaxupper}

*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*
<!-- autogen-end -->

```{r desc-fleet-vmaxupper, results = knitr_results, echo = knitr_echo}
fleet@VmaxUpper
```

<!-- autogen-begin -->
### CurrentYr {#app:desc-fleet-currentyr}

*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*
<!-- autogen-end -->

```{r desc-fleet-currentyr, results = knitr_results, echo = knitr_echo}
fleet@CurrentYr
```

<!-- autogen-begin -->
### MPA {#app:desc-fleet-mpa}

*(Optional) Matrix specifying spatial closures for historical years.*
<!-- autogen-end -->

```{r desc-fleet-mpa, results = knitr_results, echo = knitr_echo}
fleet@MPA
```

## OBS SLOT DESCRIPTIONS {#app:desc-obs}

```{r warnings = FALSE}
obs <- methods::new('Obs')
obs <- DLMtool::Imprecise_Unbiased # TODO: temporary
```

<!-- autogen-begin -->
### Name {#app:desc-obs-name}

*The name of the observation model object. Single value. Character string.*
<!-- autogen-end -->

```{r desc-obs-name, results = knitr_results, echo = knitr_echo}
obs@Name
```

<!-- autogen-begin -->
### Cobs {#app:desc-obs-cobs}

*Log-normal catch observation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-obs-cobs, results = knitr_results, echo = knitr_echo}
obs@Cobs
```

<!-- autogen-begin -->
### Cbiascv {#app:desc-obs-cbiascv}

*Log-normal coefficient of variation controlling the sampling of bias in catch observations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers*
<!-- autogen-end -->

```{r desc-obs-cbiascv, results = knitr_results, echo = knitr_echo}
obs@Cbiascv
```

<!-- autogen-begin -->
### CAA_nsamp {#app:desc-obs-caa_nsamp}

*Number of catch-at-age observation per time step. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-caa_nsamp, results = knitr_results, echo = knitr_echo}
obs@CAA_nsamp
```

<!-- autogen-begin -->
### CAA_ESS {#app:desc-obs-caa_ess}

*Effective sample size (independent age draws) of the multinomial catch-at-age observation error model. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-obs-caa_ess, results = knitr_results, echo = knitr_echo}
obs@CAA_ESS
```

<!-- autogen-begin -->
### CAL_nsamp {#app:desc-obs-cal_nsamp}

*Number of catch-at-length observation per time step. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-obs-cal_nsamp, results = knitr_results, echo = knitr_echo}
obs@CAL_nsamp
```

<!-- autogen-begin -->
### CAL_ESS {#app:desc-obs-cal_ess}

*Effective sample size (independent length draws) of the multinomial catch-at-length observation error model. Uniform distribution lower and upper bounds. Positive integers*
<!-- autogen-end -->

```{r desc-obs-cal_ess, results = knitr_results, echo = knitr_echo}
obs@CAL_ESS
```

<!-- autogen-begin -->
### Iobs {#app:desc-obs-iobs}

*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-iobs, results = knitr_results, echo = knitr_echo}
obs@Iobs
```

<!-- autogen-begin -->
### Ibiascv {#app:desc-obs-ibiascv}

*Log-normal coefficient of variation controlling error in observations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-ibiascv, results = knitr_results, echo = knitr_echo}
obs@Ibiascv
```

<!-- autogen-begin -->
### Btobs {#app:desc-obs-btobs}

*Log-normal coefficient of variation controlling error in observations of current stock biomass among years. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-btobs, results = knitr_results, echo = knitr_echo}
obs@Btobs
```

<!-- autogen-begin -->
### Btbiascv {#app:desc-obs-btbiascv}

*Uniform-log bounds for sampling persistent bias in current stock biomass. Uniform-log distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-btbiascv, results = knitr_results, echo = knitr_echo}
obs@Btbiascv
```

<!-- autogen-begin -->
### beta {#app:desc-obs-beta}

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-beta, results = knitr_results, echo = knitr_echo}
obs@beta
```

<!-- autogen-begin -->
### LenMbiascv {#app:desc-obs-lenmbiascv}

*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-lenmbiascv, results = knitr_results, echo = knitr_echo}
obs@LenMbiascv
```

<!-- autogen-begin -->
### Mbiascv {#app:desc-obs-mbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-mbiascv, results = knitr_results, echo = knitr_echo}
obs@Mbiascv
```

<!-- autogen-begin -->
### Kbiascv {#app:desc-obs-kbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-kbiascv, results = knitr_results, echo = knitr_echo}
obs@Kbiascv
```

<!-- autogen-begin -->
### t0biascv {#app:desc-obs-t0biascv}

*Log-normal coefficient of variation for sampling persistent bias in observed t0. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-t0biascv, results = knitr_results, echo = knitr_echo}
obs@t0biascv
```

<!-- autogen-begin -->
### Linfbiascv {#app:desc-obs-linfbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed maximum length. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-linfbiascv, results = knitr_results, echo = knitr_echo}
obs@Linfbiascv
```

<!-- autogen-begin -->
### LFCbiascv {#app:desc-obs-lfcbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed length at first capture. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-lfcbiascv, results = knitr_results, echo = knitr_echo}
obs@LFCbiascv
```

<!-- autogen-begin -->
### LFSbiascv {#app:desc-obs-lfsbiascv}

*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-lfsbiascv, results = knitr_results, echo = knitr_echo}
obs@LFSbiascv
```

<!-- autogen-begin -->
### FMSYbiascv {#app:desc-obs-fmsybiascv}

*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-fmsybiascv, results = knitr_results, echo = knitr_echo}
obs@FMSYbiascv
```

<!-- autogen-begin -->
### FMSY_Mbiascv {#app:desc-obs-fmsy_mbiascv}

*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-fmsy_mbiascv, results = knitr_results, echo = knitr_echo}
obs@FMSY_Mbiascv
```

<!-- autogen-begin -->
### BMSY_B0biascv {#app:desc-obs-bmsy_b0biascv}

*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-bmsy_b0biascv, results = knitr_results, echo = knitr_echo}
obs@BMSY_B0biascv
```

<!-- autogen-begin -->
### Irefbiascv {#app:desc-obs-irefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-irefbiascv, results = knitr_results, echo = knitr_echo}
obs@Irefbiascv
```

<!-- autogen-begin -->
### Brefbiascv {#app:desc-obs-brefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-brefbiascv, results = knitr_results, echo = knitr_echo}
obs@Brefbiascv
```

<!-- autogen-begin -->
### Crefbiascv {#app:desc-obs-crefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-crefbiascv, results = knitr_results, echo = knitr_echo}
obs@Crefbiascv
```

<!-- autogen-begin -->
### Dbiascv {#app:desc-obs-dbiascv}

*Log-normal coefficient of variation for sampling persistent bias in stock depletion. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-dbiascv, results = knitr_results, echo = knitr_echo}
obs@Dbiascv
```

<!-- autogen-begin -->
### Dobs {#app:desc-obs-dobs}

*Log-normal coefficient of variation controlling error in observations of stock depletion among years. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-dobs, results = knitr_results, echo = knitr_echo}
obs@Dobs
```

<!-- autogen-begin -->
### hbiascv {#app:desc-obs-hbiascv}

*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-hbiascv, results = knitr_results, echo = knitr_echo}
obs@hbiascv
```

<!-- autogen-begin -->
### Recbiascv {#app:desc-obs-recbiascv}

*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers*
<!-- autogen-end -->

```{r desc-obs-recbiascv, results = knitr_results, echo = knitr_echo}
obs@Recbiascv
```

## IMP SLOT DESCRIPTIONS {#app:desc-imp}

```{r warnings = FALSE}
imp <- methods::new('Imp')
imp <- DLMtool::Perfect_Imp # TODO: temporary
```

<!-- autogen-begin -->
### Name {#app:desc-imp-name}

*The name of the Implementation error object. Single value. Character string.*
<!-- autogen-end -->

```{r desc-imp-name, results = knitr_results, echo = knitr_echo}
imp@Name
```

<!-- autogen-begin -->
### TACFrac {#app:desc-imp-tacfrac}

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-imp-tacfrac, results = knitr_results, echo = knitr_echo}
imp@TACFrac
```

<!-- autogen-begin -->
### TACSD {#app:desc-imp-tacsd}

*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-imp-tacsd, results = knitr_results, echo = knitr_echo}
imp@TACSD
```

<!-- autogen-begin -->
### TAEFrac {#app:desc-imp-taefrac}

*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-imp-taefrac, results = knitr_results, echo = knitr_echo}
imp@TAEFrac
```

<!-- autogen-begin -->
### TAESD {#app:desc-imp-taesd}

*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-imp-taesd, results = knitr_results, echo = knitr_echo}
imp@TAESD
```

<!-- autogen-begin -->
### SizeLimFrac {#app:desc-imp-sizelimfrac}

*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*
<!-- autogen-end -->

```{r desc-imp-sizelimfrac, results = knitr_results, echo = knitr_echo}
imp@SizeLimFrac
```

<!-- autogen-begin -->
### SizeLimSD {#app:desc-imp-sizelimsd}

*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*
<!-- autogen-end -->

```{r desc-imp-sizelimsd, results = knitr_results, echo = knitr_echo}
imp@SizeLimSD
```

