```{r message = FALSE}
  library(DLMtool)
```

# **Data slot descriptions**


```{r warnings = FALSE}
  data <- methods::new('Data')
```

## Name


*The name of the Data object. Single value. Character string*


```{r, data-Name, results = FALSE}
  data@Name
```
## Common_Name


*Common name of the species. Character string*


```{r, data-Common_Name, results = FALSE}
  data@Common_Name
```
## Species


*Scientific name of the species. Genus and species name. Character string*


```{r, data-Species, results = FALSE}
  data@Species
```
## Region


*Name of the general geographic region of the fishery. Character string*


```{r, data-Region, results = FALSE}
  data@Region
```
## Year


*Years that corresponding to catch and relative abundance data. Vector nyears long. Positive integer*


```{r, data-Year, results = FALSE}
  data@Year
```
## Cat


*Total annual catches. Matrix of nsim rows and nyears columns. Non-negative real numbers*


```{r, data-Cat, results = FALSE}
  data@Cat
```
## Ind


*Relative abundance index. Matrix of nsim rows and nyears columns. Non-negative real numbers*


```{r, data-Ind, results = FALSE}
  data@Ind
```
## Type


*Type of abundance index, corresponding with rows in RInd . Types are: Biomass , VBiomass , and SpBiomass for indices of total, vulnerable, and spawning biomass respectively. Character string.*


```{r, data-Type, results = FALSE}
  data@Type
```
## RInd


*One or more vectors of abundance indices. Non-negative real numbers*


```{r, data-RInd, results = FALSE}
  data@RInd
```
## Rec


*Recent recruitment strength. Matrix of nsim rows and nyears columns. Non-negative real numbers*


```{r, data-Rec, results = FALSE}
  data@Rec
```
## t


*The number of years corresponding to AvC and Dt. Single value. Positive integer*


```{r, data-t, results = FALSE}
  data@t
```
## AvC


*Average catch over time t. Vector nsim long. Positive real numbers*


```{r, data-AvC, results = FALSE}
  data@AvC
```
## Dt


*Depletion over time t SSB(now)/SSB(now-t+1). Vector nsim long. Fraction*


```{r, data-Dt, results = FALSE}
  data@Dt
```
## Mort


*Natural mortality rate. Vector nsim long. Positive real numbers*


```{r, data-Mort, results = FALSE}
  data@Mort
```
## FMSY_M


*An assumed ratio of FMSY to M. Vector nsim long. Positive real numbers*


```{r, data-FMSY_M, results = FALSE}
  data@FMSY_M
```
## BMSY_B0


*The most productive stock size relative to unfished. Vector nsim long. Fraction*


```{r, data-BMSY_B0, results = FALSE}
  data@BMSY_B0
```
## L50


*Length at 50 percent maturity. Vector nsim long. Positive real numbers*


```{r, data-L50, results = FALSE}
  data@L50
```
## L95


*Length at 95 percent maturity. Vector nsim long. Positive real numbers*


```{r, data-L95, results = FALSE}
  data@L95
```
## ML


*Mean length time series. Matrix of nsim rows and nyears columns. Non-negative real numbers*


```{r, data-ML, results = FALSE}
  data@ML
```
## Lbar


*Mean length of catches over Lc. Matrix of nsim rows and nyears columns. Positive real numbers*


```{r, data-Lbar, results = FALSE}
  data@Lbar
```
## Lc


*Modal length of catches. Matrix of nsim rows and nyears columns. Positive real numbers*


```{r, data-Lc, results = FALSE}
  data@Lc
```
## LFC


*Length at first capture. Vector nsim long. Positive real numbers*


```{r, data-LFC, results = FALSE}
  data@LFC
```
## LFS


*Shortest length at full selection. Vector nsim long. Positive real numbers*


```{r, data-LFS, results = FALSE}
  data@LFS
```
## CAA


*Catch at Age data (numbers). Array of dimensions nsim x nyears x MaxAge. Non-negative integers*


```{r, data-CAA, results = FALSE}
  data@CAA
```
## Dep


*Stock depletion SSB(current)/SSB(unfished). Vector nsim long. Fraction.*


```{r, data-Dep, results = FALSE}
  data@Dep
```
## Abun


*An estimate of absolute current vulnerable abundance. Vector nsim long. Positive real numbers*


```{r, data-Abun, results = FALSE}
  data@Abun
```
## SpAbun


*An estimate of absolute current spawning stock abundance. Vector nsim long. Positive real numbers*


```{r, data-SpAbun, results = FALSE}
  data@SpAbun
```
## vbK


*The von Bertalanffy growth coefficient K. Vector nsim long. Positive real numbers*


```{r, data-vbK, results = FALSE}
  data@vbK
```
## vbLinf


*Maximum length. Vector nsim long. Positive real numbers*


```{r, data-vbLinf, results = FALSE}
  data@vbLinf
```
## vbt0


*Theoretical age at length zero. Vector nsim long. Non-positive real numbers*


```{r, data-vbt0, results = FALSE}
  data@vbt0
```
## LenCV


*Coefficient of variation of length-at-age (assumed constant for all age classes). Vector nsim long. Positive real numbers*


```{r, data-LenCV, results = FALSE}
  data@LenCV
```
## wla


*Weight-Length parameter alpha. Vector nsim long. Positive real numbers*


```{r, data-wla, results = FALSE}
  data@wla
```
## wlb


*Weight-Length parameter beta. Vector nsim long. Positive real numbers*


```{r, data-wlb, results = FALSE}
  data@wlb
```
## steep


*Steepness of stock-recruitment relationship. Vector nsim long. Value in the range of one-fifth to 1*


```{r, data-steep, results = FALSE}
  data@steep
```
## sigmaR


*Recruitment variability. Vector nsim long. Positive real numbers*


```{r, data-sigmaR, results = FALSE}
  data@sigmaR
```
## CV_Cat


*Coefficient of variation in annual catches. Vector nsim long. Positive real numbers*


```{r, data-CV_Cat, results = FALSE}
  data@CV_Cat
```
## CV_Dt


*Coefficient of variation in depletion over time t. Vector nsim long. Positive real numbers*


```{r, data-CV_Dt, results = FALSE}
  data@CV_Dt
```
## CV_AvC


*Coefficient of variation in average catches over time t. Vector nsim long. Positive real numbers*


```{r, data-CV_AvC, results = FALSE}
  data@CV_AvC
```
## CV_Ind


*Coefficient of variation in the relative abundance index. Vector nsim long. Positive real numbers*


```{r, data-CV_Ind, results = FALSE}
  data@CV_Ind
```
## CV_Mort


*Coefficient of variation in natural mortality rate. Vector nsim long. Positive real numbers*


```{r, data-CV_Mort, results = FALSE}
  data@CV_Mort
```
## CV_FMSY_M


*Coefficient of variation in the ratio in FMSY/M. Vector nsim long. Positive real numbers*


```{r, data-CV_FMSY_M, results = FALSE}
  data@CV_FMSY_M
```
## CV_BMSY_B0


*Coefficient of variation in the position of the most productive stock size relative to unfished. Vector nsim long. Positive real numbers*


```{r, data-CV_BMSY_B0, results = FALSE}
  data@CV_BMSY_B0
```
## CV_Dep


*Coefficient of variation in current stock depletion. Vector nsim long. Positive real numbers*


```{r, data-CV_Dep, results = FALSE}
  data@CV_Dep
```
## CV_Abun


*Coefficient of variation in estimate of absolute current stock size. Vector nsim long. Positive real numbers*


```{r, data-CV_Abun, results = FALSE}
  data@CV_Abun
```
## CV_vbK


*Coefficient of variation in the von Bertalanffy K parameter. Vector nsim long. Positive real numbers*


```{r, data-CV_vbK, results = FALSE}
  data@CV_vbK
```
## CV_vbLinf


*Coefficient of variation in maximum length. Vector nsim long. Positive real numbers*


```{r, data-CV_vbLinf, results = FALSE}
  data@CV_vbLinf
```
## CV_vbt0


*Coefficient of variation in age at length zero. Vector nsim long. Positive real numbers*


```{r, data-CV_vbt0, results = FALSE}
  data@CV_vbt0
```
## CV_L50


*Coefficient of variation in length at 50 per cent maturity. Vector nsim long. Positive real numbers*


```{r, data-CV_L50, results = FALSE}
  data@CV_L50
```
## CV_LFC


*Coefficient of variation in length at first capture. Vector nsim long. Positive real numbers*


```{r, data-CV_LFC, results = FALSE}
  data@CV_LFC
```
## CV_LFS


*Coefficient of variation in length at full selection. Vector nsim long. Positive real numbers*


```{r, data-CV_LFS, results = FALSE}
  data@CV_LFS
```
## CV_wla


*Coefficient of variation in weight-length parameter a. Vector nsim long. Positive real numbers*


```{r, data-CV_wla, results = FALSE}
  data@CV_wla
```
## CV_wlb


*Coefficient of variation in weight-length parameter b. Vector nsim long. Positive real numbers*


```{r, data-CV_wlb, results = FALSE}
  data@CV_wlb
```
## CV_steep


*Coefficient of variation in steepness. Vector nsim long. Positive real numbers*


```{r, data-CV_steep, results = FALSE}
  data@CV_steep
```
## sigmaL


*Assumed observaton error of the length composition data. Vector nsim long. Positive real numbers*


```{r, data-sigmaL, results = FALSE}
  data@sigmaL
```
## MaxAge


*Maximum age. Vector nsim long. Positive integer*


```{r, data-MaxAge, results = FALSE}
  data@MaxAge
```
## CAL_bins


*The values delimiting the length bins for the catch-at-length data. Vector. Non-negative real numbers*


```{r, data-CAL_bins, results = FALSE}
  data@CAL_bins
```
## CAL


*Catch-at-length data. An array with dimensions nsim x nyears x length(CAL_bins). Non-negative integers*


```{r, data-CAL, results = FALSE}
  data@CAL
```
## TAC


*The calculated catch limits (function TAC). An array with dimensions PosMPs x replicate TAC samples x nsim. Positive real numbers*


```{r, data-TAC, results = FALSE}
  data@TAC
```
## Sense


*The results of the sensitivity analysis (function Sense). An array with dimensions PosMPs x sensitivity increments. Positive real numbers*


```{r, data-Sense, results = FALSE}
  data@Sense
```
## Units


*Units of the catch/absolute abundance estimates. Single value. Character string*


```{r, data-Units, results = FALSE}
  data@Units
```
## Ref


*A reference management level (eg a catch limit). Single value. Positive real number*


```{r, data-Ref, results = FALSE}
  data@Ref
```
## Ref_type


*Type of reference management level (eg 2009 catch limit). Single value. Character string*


```{r, data-Ref_type, results = FALSE}
  data@Ref_type
```
## Log


*A record of events. Single value. Character string*


```{r, data-Log, results = FALSE}
  data@Log
```
## params


*A place to store estimated parameters. An object. R list*


```{r, data-params, results = FALSE}
  data@params
```
## PosMPs


*The methods that can be applied to these data. Vector. Character strings*


```{r, data-PosMPs, results = FALSE}
  data@PosMPs
```
## MPs


*The methods that were applied to these data. Vector. Character strings*


```{r, data-MPs, results = FALSE}
  data@MPs
```
## OM


*A table of operating model conditions. R table object of nsim rows. Real numbers*


```{r, data-OM, results = FALSE}
  data@OM
```
## Obs


*A table of observation model conditions. R table object of nsim rows. Real numbers*


```{r, data-Obs, results = FALSE}
  data@Obs
```
## Cref


*Reference or target catch level (eg MSY). Vector of length nsim. Positive real numbers*


```{r, data-Cref, results = FALSE}
  data@Cref
```
## Iref


*Reference or target relative abundance index level (eg BMSY / B0). Vector of length nsim. Positive real numbers*


```{r, data-Iref, results = FALSE}
  data@Iref
```
## Bref


*Reference or target biomass level (eg BMSY). Vector of length nsim. Positive real numbers*


```{r, data-Bref, results = FALSE}
  data@Bref
```
## CV_Cref


*Log-normal CV for reference or target catch level. Vector of length nsim. Positive real numbers*


```{r, data-CV_Cref, results = FALSE}
  data@CV_Cref
```
## CV_Iref


*Log-normalCV for reference or target relative abundance index level. Vector of length nsim. Positive real numbers*


```{r, data-CV_Iref, results = FALSE}
  data@CV_Iref
```
## CV_Bref


*Log-normal CV for reference or target biomass level. Vector of length nsim. Positive real numbers*


```{r, data-CV_Bref, results = FALSE}
  data@CV_Bref
```
## CV_Rec


*Log-normal CV for recent recruitment strength. Vector of length nsim. Positive real numbers*


```{r, data-CV_Rec, results = FALSE}
  data@CV_Rec
```
## MPrec


*The previous recommendation of a management procedure. Vector of length nsim. Positive real numbers*


```{r, data-MPrec, results = FALSE}
  data@MPrec
```
## MPeff


*The current level of effort. Vector of length nsim. Positive real numbers*


```{r, data-MPeff, results = FALSE}
  data@MPeff
```
## LHYear


*The last historical year of the simulation (before projection). Single value. Positive integer*


```{r, data-LHYear, results = FALSE}
  data@LHYear
```
## nareas


*Number of fishing areas. Vector of length nsim. Non-negative integer*


```{r, data-nareas, results = FALSE}
  data@nareas
```
## Misc


*Other information for MPs. An object. R list*


```{r, data-Misc, results = FALSE}
  data@Misc
```
# **Stock slot descriptions**


```{r warnings = FALSE}
  stock <- methods::new('Stock')
```

## Name


*The name of the Stock object. Single value. Character string*


```{r, stock-Name, results = FALSE}
  stock@Name
```
## Common_Name


*Common name of the species. Character string*


```{r, stock-Common_Name, results = FALSE}
  stock@Common_Name
```
## Species


*Scientific name of the species. Genus and species name. Character string*


```{r, stock-Species, results = FALSE}
  stock@Species
```
## maxage


*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer*


```{r, stock-maxage, results = FALSE}
  stock@maxage
```
## R0


*The magnitude of unfished recruitment. Single value. Positive real number*


```{r, stock-R0, results = FALSE}
  stock@R0
```
## M


*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number*


```{r, stock-M, results = FALSE}
  stock@M
```
## M2


*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number*


```{r, stock-M2, results = FALSE}
  stock@M2
```
## Mexp


*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*


```{r, stock-Mexp, results = FALSE}
  stock@Mexp
```
## Msd


*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, stock-Msd, results = FALSE}
  stock@Msd
```
## Mgrad


*No longer used. Previously mean temporal trend in natural mortality rate, expressed as a percentage change in M per year.*


```{r, stock-Mgrad, results = FALSE}
  stock@Mgrad
```
## h


*Steepness of the stock recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1*


```{r, stock-h, results = FALSE}
  stock@h
```
## SRrel


*Type of stock-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer*


```{r, stock-SRrel, results = FALSE}
  stock@SRrel
```
## Perr


*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, stock-Perr, results = FALSE}
  stock@Perr
```
## AC


*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, stock-AC, results = FALSE}
  stock@AC
```
## Period


*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, stock-Period, results = FALSE}
  stock@Period
```
## Amplitude


*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1*


```{r, stock-Amplitude, results = FALSE}
  stock@Amplitude
```
## Linf


*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, stock-Linf, results = FALSE}
  stock@Linf
```
## K


*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, stock-K, results = FALSE}
  stock@K
```
## t0


*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers*


```{r, stock-t0, results = FALSE}
  stock@t0
```
## LenCV


*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers*


```{r, stock-LenCV, results = FALSE}
  stock@LenCV
```
## Ksd


*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, stock-Ksd, results = FALSE}
  stock@Ksd
```
## Kgrad


*No longer used. Previously mean temporal trend in growth parameter k, expressed as a percentage change in k per year.*


```{r, stock-Kgrad, results = FALSE}
  stock@Kgrad
```
## Linfsd


*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, stock-Linfsd, results = FALSE}
  stock@Linfsd
```
## Linfgrad


*No longer used. Previously mean temporal trend in maximum length, expressed as a percentage change in Linf per year.*


```{r, stock-Linfgrad, results = FALSE}
  stock@Linfgrad
```
## L50


*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, stock-L50, results = FALSE}
  stock@L50
```
## L50_95


*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, stock-L50_95, results = FALSE}
  stock@L50_95
```
## D


*Current level of stock depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction*


```{r, stock-D, results = FALSE}
  stock@D
```
## a


*Length-weight parameter alpha. Single value. Positive real number*


```{r, stock-a, results = FALSE}
  stock@a
```
## b


*Length-weight parameter beta. Single value. Positive real number*


```{r, stock-b, results = FALSE}
  stock@b
```
## Size_area_1


*The size of area 1 relative to area 2. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, stock-Size_area_1, results = FALSE}
  stock@Size_area_1
```
## Frac_area_1


*The fraction of the unfished biomass in stock 1. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, stock-Frac_area_1, results = FALSE}
  stock@Frac_area_1
```
## Prob_staying


*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*


```{r, stock-Prob_staying, results = FALSE}
  stock@Prob_staying
```
## Fdisc


*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, stock-Fdisc, results = FALSE}
  stock@Fdisc
```
## Source


*A reference to a website or article from which parameters were taken to define the stock object. Single value. Character string.*


```{r, stock-Source, results = FALSE}
  stock@Source
```
# **Fleet slot descriptions**


```{r warnings = FALSE}
  fleet <- methods::new('Fleet')
```

## Name


*Name of the Fleet object. Single value. Character string.*


```{r, fleet-Name, results = FALSE}
  fleet@Name
```
## nyears


*The number of years for the historical spool-up simulation. Single value. Positive integer*


```{r, fleet-nyears, results = FALSE}
  fleet@nyears
```
## Spat_targ


*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers*


```{r, fleet-Spat_targ, results = FALSE}
  fleet@Spat_targ
```
## EffYears


*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers*


```{r, fleet-EffYears, results = FALSE}
  fleet@EffYears
```
## EffLower


*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*


```{r, fleet-EffLower, results = FALSE}
  fleet@EffLower
```
## EffUpper


*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*


```{r, fleet-EffUpper, results = FALSE}
  fleet@EffUpper
```
## Esd


*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, fleet-Esd, results = FALSE}
  fleet@Esd
```
## qinc


*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, fleet-qinc, results = FALSE}
  fleet@qinc
```
## qcv


*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, fleet-qcv, results = FALSE}
  fleet@qcv
```
## L5


*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, fleet-L5, results = FALSE}
  fleet@L5
```
## LFS


*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, fleet-LFS, results = FALSE}
  fleet@LFS
```
## Vmaxlen


*The vulnerability of fish at Stock@Linf . Uniform distribution lower and upper bounds. Fraction*


```{r, fleet-Vmaxlen, results = FALSE}
  fleet@Vmaxlen
```
## isRel


*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*


```{r, fleet-isRel, results = FALSE}
  fleet@isRel
```
## LR5


*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, fleet-LR5, results = FALSE}
  fleet@LR5
```
## LFR


*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, fleet-LFR, results = FALSE}
  fleet@LFR
```
## Rmaxlen


*The retention of fish at Stock@Linf . Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, fleet-Rmaxlen, results = FALSE}
  fleet@Rmaxlen
```
## DR


*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction*


```{r, fleet-DR, results = FALSE}
  fleet@DR
```
## SelYears


*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers*


```{r, fleet-SelYears, results = FALSE}
  fleet@SelYears
```
## AbsSelYears


*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers*


```{r, fleet-AbsSelYears, results = FALSE}
  fleet@AbsSelYears
```
## L5Lower


*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r, fleet-L5Lower, results = FALSE}
  fleet@L5Lower
```
## L5Upper


*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r, fleet-L5Upper, results = FALSE}
  fleet@L5Upper
```
## LFSLower


*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r, fleet-LFSLower, results = FALSE}
  fleet@LFSLower
```
## LFSUpper


*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r, fleet-LFSUpper, results = FALSE}
  fleet@LFSUpper
```
## VmaxLower


*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*


```{r, fleet-VmaxLower, results = FALSE}
  fleet@VmaxLower
```
## VmaxUpper


*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*


```{r, fleet-VmaxUpper, results = FALSE}
  fleet@VmaxUpper
```
## CurrentYr


*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*


```{r, fleet-CurrentYr, results = FALSE}
  fleet@CurrentYr
```
## MPA


*(Optional) Matrix specifying spatial closures for historical years.*


```{r, fleet-MPA, results = FALSE}
  fleet@MPA
```
# **Obs slot descriptions**


```{r warnings = FALSE}
  obs <- methods::new('Obs')
```

## Name


*The name of the observation model object. Single value. Character string.*


```{r, obs-Name, results = FALSE}
  obs@Name
```
## Cobs


*Log-normal catch observation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, obs-Cobs, results = FALSE}
  obs@Cobs
```
## Cbiascv


*Log-normal coefficient of variation controlling the sampling of bias in catch observations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, obs-Cbiascv, results = FALSE}
  obs@Cbiascv
```
## CAA_nsamp


*Number of catch-at-age observation per time step. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-CAA_nsamp, results = FALSE}
  obs@CAA_nsamp
```
## CAA_ESS


*Effective sample size (independent age draws) of the multinomial catch-at-age observation error model. Uniform distribution lower and upper bounds. Positive integers*


```{r, obs-CAA_ESS, results = FALSE}
  obs@CAA_ESS
```
## CAL_nsamp


*Number of catch-at-length observation per time step. Uniform distribution lower and upper bounds. Positive integers*


```{r, obs-CAL_nsamp, results = FALSE}
  obs@CAL_nsamp
```
## CAL_ESS


*Effective sample size (independent length draws) of the multinomial catch-at-length observation error model. Uniform distribution lower and upper bounds. Positive integers*


```{r, obs-CAL_ESS, results = FALSE}
  obs@CAL_ESS
```
## Iobs


*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Iobs, results = FALSE}
  obs@Iobs
```
## Ibiascv


*Log-normal coefficient of variation controlling error in observations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Ibiascv, results = FALSE}
  obs@Ibiascv
```
## Btobs


*Log-normal coefficient of variation controlling error in observations of current stock biomass among years. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Btobs, results = FALSE}
  obs@Btobs
```
## Btbiascv


*Uniform-log bounds for sampling persistent bias in current stock biomass. Uniform-log distribution lower and upper bounds. Positive real numbers*


```{r, obs-Btbiascv, results = FALSE}
  obs@Btbiascv
```
## beta


*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-beta, results = FALSE}
  obs@beta
```
## LenMbiascv


*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-LenMbiascv, results = FALSE}
  obs@LenMbiascv
```
## Mbiascv


*Log-normal coefficient of variation for sampling persistent bias in observed natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Mbiascv, results = FALSE}
  obs@Mbiascv
```
## Kbiascv


*Log-normal coefficient of variation for sampling persistent bias in observed growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Kbiascv, results = FALSE}
  obs@Kbiascv
```
## t0biascv


*Log-normal coefficient of variation for sampling persistent bias in observed t0. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-t0biascv, results = FALSE}
  obs@t0biascv
```
## Linfbiascv


*Log-normal coefficient of variation for sampling persistent bias in observed maximum length. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Linfbiascv, results = FALSE}
  obs@Linfbiascv
```
## LFCbiascv


*Log-normal coefficient of variation for sampling persistent bias in observed length at first capture. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-LFCbiascv, results = FALSE}
  obs@LFCbiascv
```
## LFSbiascv


*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-LFSbiascv, results = FALSE}
  obs@LFSbiascv
```
## FMSYbiascv


*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-FMSYbiascv, results = FALSE}
  obs@FMSYbiascv
```
## FMSY_Mbiascv


*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-FMSY_Mbiascv, results = FALSE}
  obs@FMSY_Mbiascv
```
## BMSY_B0biascv


*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-BMSY_B0biascv, results = FALSE}
  obs@BMSY_B0biascv
```
## Irefbiascv


*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Irefbiascv, results = FALSE}
  obs@Irefbiascv
```
## Brefbiascv


*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Brefbiascv, results = FALSE}
  obs@Brefbiascv
```
## Crefbiascv


*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Crefbiascv, results = FALSE}
  obs@Crefbiascv
```
## Dbiascv


*Log-normal coefficient of variation for sampling persistent bias in stock depletion. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Dbiascv, results = FALSE}
  obs@Dbiascv
```
## Dobs


*Log-normal coefficient of variation controlling error in observations of stock depletion among years. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Dobs, results = FALSE}
  obs@Dobs
```
## hbiascv


*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-hbiascv, results = FALSE}
  obs@hbiascv
```
## Recbiascv


*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, obs-Recbiascv, results = FALSE}
  obs@Recbiascv
```
# **Imp slot descriptions**


```{r warnings = FALSE}
  imp <- methods::new('Imp')
```

## Name


*The name of the Implementation error object. Single value. Character string.*


```{r, imp-Name, results = FALSE}
  imp@Name
```
## TACFrac


*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*


```{r, imp-TACFrac, results = FALSE}
  imp@TACFrac
```
## TACSD


*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r, imp-TACSD, results = FALSE}
  imp@TACSD
```
## TAEFrac


*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*


```{r, imp-TAEFrac, results = FALSE}
  imp@TAEFrac
```
## TAESD


*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r, imp-TAESD, results = FALSE}
  imp@TAESD
```
## SizeLimFrac


*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*


```{r, imp-SizeLimFrac, results = FALSE}
  imp@SizeLimFrac
```
## SizeLimSD


*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r, imp-SizeLimSD, results = FALSE}
  imp@SizeLimSD
```
# **OM slot descriptions**


```{r warnings = FALSE}
  om <- methods::new('OM')
```

## Name


*Name of the operating model*


```{r, om-Name, results = FALSE}
  om@Name
```
## Agency


*Name of the agency responsible for the management of the fishery. Character string*


```{r, om-Agency, results = FALSE}
  om@Agency
```
## Region


*Name of the general geographic region of the fishery. Character string*


```{r, om-Region, results = FALSE}
  om@Region
```
## Sponsor


*Name of the organization who sponsored the OM. Character string*


```{r, om-Sponsor, results = FALSE}
  om@Sponsor
```
## Latitude


*Latitude (decimal degrees). Negative values represent the South of the Equator. Numeric. Single value*


```{r, om-Latitude, results = FALSE}
  om@Latitude
```
## Longitude


*Longitude (decimal degrees). Negative values represent the West of the Prime Meridian. Numeric. Single value*


```{r, om-Longitude, results = FALSE}
  om@Longitude
```
## nsim


*The number of simulations*


```{r, om-nsim, results = FALSE}
  om@nsim
```
## proyears


*The number of projected years*


```{r, om-proyears, results = FALSE}
  om@proyears
```
## interval


*The assessment interval - how often would you like to update the management system?*


```{r, om-interval, results = FALSE}
  om@interval
```
## pstar


*The percentile of the sample of the management recommendation for each method*


```{r, om-pstar, results = FALSE}
  om@pstar
```
## maxF


*Maximum instantaneous fishing mortality rate that may be simulated for any given age class*


```{r, om-maxF, results = FALSE}
  om@maxF
```
## reps


*Number of samples of the management recommendation for each method. Note that when this is set to 1, the mean value of the data inputs is used.*


```{r, om-reps, results = FALSE}
  om@reps
```
## cpars


*A list of custom parameters. Time series are a matrix nsim rows by nyears columns. Single parameters are a vector nsim long*


```{r, om-cpars, results = FALSE}
  om@cpars
```
## seed


*A random seed to ensure users can reproduce results exactly*


```{r, om-seed, results = FALSE}
  om@seed
```
## Source


*A reference to a website or article from which parameters were taken to define the operating model*


```{r, om-Source, results = FALSE}
  om@Source
```
## Common_Name


*Common name of the species. Character string*


```{r, om-Common_Name, results = FALSE}
  om@Common_Name
```
## Species


*Scientific name of the species. Genus and species name. Character string*


```{r, om-Species, results = FALSE}
  om@Species
```
## maxage


*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer*


```{r, om-maxage, results = FALSE}
  om@maxage
```
## R0


*The magnitude of unfished recruitment. Single value. Positive real number*


```{r, om-R0, results = FALSE}
  om@R0
```
## M


*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number*


```{r, om-M, results = FALSE}
  om@M
```
## M2


*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number*


```{r, om-M2, results = FALSE}
  om@M2
```
## Mexp


*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*


```{r, om-Mexp, results = FALSE}
  om@Mexp
```
## Msd


*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Msd, results = FALSE}
  om@Msd
```
## Mgrad


*No longer used. Previously mean temporal trend in natural mortality rate, expressed as a percentage change in M per year.*


```{r, om-Mgrad, results = FALSE}
  om@Mgrad
```
## h


*Steepness of the stock recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1*


```{r, om-h, results = FALSE}
  om@h
```
## SRrel


*Type of stock-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer*


```{r, om-SRrel, results = FALSE}
  om@SRrel
```
## Perr


*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Perr, results = FALSE}
  om@Perr
```
## AC


*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-AC, results = FALSE}
  om@AC
```
## Period


*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Period, results = FALSE}
  om@Period
```
## Amplitude


*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1*


```{r, om-Amplitude, results = FALSE}
  om@Amplitude
```
## Linf


*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Linf, results = FALSE}
  om@Linf
```
## K


*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-K, results = FALSE}
  om@K
```
## t0


*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers*


```{r, om-t0, results = FALSE}
  om@t0
```
## LenCV


*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-LenCV, results = FALSE}
  om@LenCV
```
## Ksd


*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Ksd, results = FALSE}
  om@Ksd
```
## Kgrad


*No longer used. Previously mean temporal trend in growth parameter k, expressed as a percentage change in k per year.*


```{r, om-Kgrad, results = FALSE}
  om@Kgrad
```
## Linfsd


*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Linfsd, results = FALSE}
  om@Linfsd
```
## Linfgrad


*No longer used. Previously mean temporal trend in maximum length, expressed as a percentage change in Linf per year.*


```{r, om-Linfgrad, results = FALSE}
  om@Linfgrad
```
## L50


*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-L50, results = FALSE}
  om@L50
```
## L50_95


*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-L50_95, results = FALSE}
  om@L50_95
```
## D


*Current level of stock depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction*


```{r, om-D, results = FALSE}
  om@D
```
## a


*Length-weight parameter alpha. Single value. Positive real number*


```{r, om-a, results = FALSE}
  om@a
```
## b


*Length-weight parameter beta. Single value. Positive real number*


```{r, om-b, results = FALSE}
  om@b
```
## Size_area_1


*The size of area 1 relative to area 2. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Size_area_1, results = FALSE}
  om@Size_area_1
```
## Frac_area_1


*The fraction of the unfished biomass in stock 1. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Frac_area_1, results = FALSE}
  om@Frac_area_1
```
## Prob_staying


*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*


```{r, om-Prob_staying, results = FALSE}
  om@Prob_staying
```
## Fdisc


*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Fdisc, results = FALSE}
  om@Fdisc
```
## nyears


*The number of years for the historical spool-up simulation. Single value. Positive integer*


```{r, om-nyears, results = FALSE}
  om@nyears
```
## Spat_targ


*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers*


```{r, om-Spat_targ, results = FALSE}
  om@Spat_targ
```
## EffYears


*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers*


```{r, om-EffYears, results = FALSE}
  om@EffYears
```
## EffLower


*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*


```{r, om-EffLower, results = FALSE}
  om@EffLower
```
## EffUpper


*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*


```{r, om-EffUpper, results = FALSE}
  om@EffUpper
```
## Esd


*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Esd, results = FALSE}
  om@Esd
```
## qinc


*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-qinc, results = FALSE}
  om@qinc
```
## qcv


*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-qcv, results = FALSE}
  om@qcv
```
## L5


*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-L5, results = FALSE}
  om@L5
```
## LFS


*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-LFS, results = FALSE}
  om@LFS
```
## Vmaxlen


*The vulnerability of fish at Stock@Linf . Uniform distribution lower and upper bounds. Fraction*


```{r, om-Vmaxlen, results = FALSE}
  om@Vmaxlen
```
## isRel


*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*


```{r, om-isRel, results = FALSE}
  om@isRel
```
## LR5


*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-LR5, results = FALSE}
  om@LR5
```
## LFR


*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-LFR, results = FALSE}
  om@LFR
```
## Rmaxlen


*The retention of fish at Stock@Linf . Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Rmaxlen, results = FALSE}
  om@Rmaxlen
```
## DR


*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction*


```{r, om-DR, results = FALSE}
  om@DR
```
## SelYears


*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers*


```{r, om-SelYears, results = FALSE}
  om@SelYears
```
## AbsSelYears


*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers*


```{r, om-AbsSelYears, results = FALSE}
  om@AbsSelYears
```
## L5Lower


*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r, om-L5Lower, results = FALSE}
  om@L5Lower
```
## L5Upper


*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r, om-L5Upper, results = FALSE}
  om@L5Upper
```
## LFSLower


*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r, om-LFSLower, results = FALSE}
  om@LFSLower
```
## LFSUpper


*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r, om-LFSUpper, results = FALSE}
  om@LFSUpper
```
## VmaxLower


*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*


```{r, om-VmaxLower, results = FALSE}
  om@VmaxLower
```
## VmaxUpper


*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*


```{r, om-VmaxUpper, results = FALSE}
  om@VmaxUpper
```
## CurrentYr


*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*


```{r, om-CurrentYr, results = FALSE}
  om@CurrentYr
```
## MPA


*(Optional) Matrix specifying spatial closures for historical years.*


```{r, om-MPA, results = FALSE}
  om@MPA
```
## Cobs


*Log-normal catch observation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Cobs, results = FALSE}
  om@Cobs
```
## Cbiascv


*Log-normal coefficient of variation controlling the sampling of bias in catch observations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r, om-Cbiascv, results = FALSE}
  om@Cbiascv
```
## CAA_nsamp


*Number of catch-at-age observation per time step. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-CAA_nsamp, results = FALSE}
  om@CAA_nsamp
```
## CAA_ESS


*Effective sample size (independent age draws) of the multinomial catch-at-age observation error model. Uniform distribution lower and upper bounds. Positive integers*


```{r, om-CAA_ESS, results = FALSE}
  om@CAA_ESS
```
## CAL_nsamp


*Number of catch-at-length observation per time step. Uniform distribution lower and upper bounds. Positive integers*


```{r, om-CAL_nsamp, results = FALSE}
  om@CAL_nsamp
```
## CAL_ESS


*Effective sample size (independent length draws) of the multinomial catch-at-length observation error model. Uniform distribution lower and upper bounds. Positive integers*


```{r, om-CAL_ESS, results = FALSE}
  om@CAL_ESS
```
## Iobs


*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Iobs, results = FALSE}
  om@Iobs
```
## Ibiascv


*Log-normal coefficient of variation controlling error in observations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Ibiascv, results = FALSE}
  om@Ibiascv
```
## Btobs


*Log-normal coefficient of variation controlling error in observations of current stock biomass among years. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Btobs, results = FALSE}
  om@Btobs
```
## Btbiascv


*Uniform-log bounds for sampling persistent bias in current stock biomass. Uniform-log distribution lower and upper bounds. Positive real numbers*


```{r, om-Btbiascv, results = FALSE}
  om@Btbiascv
```
## beta


*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-beta, results = FALSE}
  om@beta
```
## LenMbiascv


*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-LenMbiascv, results = FALSE}
  om@LenMbiascv
```
## Mbiascv


*Log-normal coefficient of variation for sampling persistent bias in observed natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Mbiascv, results = FALSE}
  om@Mbiascv
```
## Kbiascv


*Log-normal coefficient of variation for sampling persistent bias in observed growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Kbiascv, results = FALSE}
  om@Kbiascv
```
## t0biascv


*Log-normal coefficient of variation for sampling persistent bias in observed t0. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-t0biascv, results = FALSE}
  om@t0biascv
```
## Linfbiascv


*Log-normal coefficient of variation for sampling persistent bias in observed maximum length. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Linfbiascv, results = FALSE}
  om@Linfbiascv
```
## LFCbiascv


*Log-normal coefficient of variation for sampling persistent bias in observed length at first capture. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-LFCbiascv, results = FALSE}
  om@LFCbiascv
```
## LFSbiascv


*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-LFSbiascv, results = FALSE}
  om@LFSbiascv
```
## FMSYbiascv


*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-FMSYbiascv, results = FALSE}
  om@FMSYbiascv
```
## FMSY_Mbiascv


*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-FMSY_Mbiascv, results = FALSE}
  om@FMSY_Mbiascv
```
## BMSY_B0biascv


*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-BMSY_B0biascv, results = FALSE}
  om@BMSY_B0biascv
```
## Irefbiascv


*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Irefbiascv, results = FALSE}
  om@Irefbiascv
```
## Brefbiascv


*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Brefbiascv, results = FALSE}
  om@Brefbiascv
```
## Crefbiascv


*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Crefbiascv, results = FALSE}
  om@Crefbiascv
```
## Dbiascv


*Log-normal coefficient of variation for sampling persistent bias in stock depletion. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Dbiascv, results = FALSE}
  om@Dbiascv
```
## Dobs


*Log-normal coefficient of variation controlling error in observations of stock depletion among years. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Dobs, results = FALSE}
  om@Dobs
```
## hbiascv


*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-hbiascv, results = FALSE}
  om@hbiascv
```
## Recbiascv


*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers*


```{r, om-Recbiascv, results = FALSE}
  om@Recbiascv
```
## TACFrac


*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*


```{r, om-TACFrac, results = FALSE}
  om@TACFrac
```
## TACSD


*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r, om-TACSD, results = FALSE}
  om@TACSD
```
## TAEFrac


*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*


```{r, om-TAEFrac, results = FALSE}
  om@TAEFrac
```
## TAESD


*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r, om-TAESD, results = FALSE}
  om@TAESD
```
## SizeLimFrac


*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*


```{r, om-SizeLimFrac, results = FALSE}
  om@SizeLimFrac
```
## SizeLimSD


*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r, om-SizeLimSD, results = FALSE}
  om@SizeLimSD
```
