```{r message = FALSE}
library(DLMtool)
```

## STOCK SLOT DESCRIPTIONS

```{r warnings = FALSE}
stock <- methods::new('Stock')
```

### Name

*The name of the Stock object. Single value. Character string.*

```{r, stock-Name, results = FALSE, echo = TRUE}
stock@Name
```

### Common_Name

*Common name of the species. Character string.*

```{r, stock-Common_Name, results = FALSE, echo = TRUE}
stock@Common_Name
```

### Species

*Scientific name of the species. Genus and species name. Character string.*

```{r, stock-Species, results = FALSE, echo = TRUE}
stock@Species
```

### maxage

*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer.*

```{r, stock-maxage, results = FALSE, echo = TRUE}
stock@maxage
```

### R0

*The magnitude of unfished recruitment. Single value. Positive real number.*

```{r, stock-R0, results = FALSE, echo = TRUE}
stock@R0
```

### M

*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number.*

```{r, stock-M, results = FALSE, echo = TRUE}
stock@M
```

### M2

*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number.*

```{r, stock-M2, results = FALSE, echo = TRUE}
stock@M2
```

### Mexp

*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*

```{r, stock-Mexp, results = FALSE, echo = TRUE}
stock@Mexp
```

### Msd

*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, stock-Msd, results = FALSE, echo = TRUE}
stock@Msd
```

### h

*Steepness of the stock recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1.*

```{r, stock-h, results = FALSE, echo = TRUE}
stock@h
```

### SRrel

*Type of stock-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer.*

```{r, stock-SRrel, results = FALSE, echo = TRUE}
stock@SRrel
```

### Perr

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, stock-Perr, results = FALSE, echo = TRUE}
stock@Perr
```

### AC

*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, stock-AC, results = FALSE, echo = TRUE}
stock@AC
```

### Period

*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, stock-Period, results = FALSE, echo = TRUE}
stock@Period
```

### Amplitude

*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1.*

```{r, stock-Amplitude, results = FALSE, echo = TRUE}
stock@Amplitude
```

### Linf

*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, stock-Linf, results = FALSE, echo = TRUE}
stock@Linf
```

### K

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, stock-K, results = FALSE, echo = TRUE}
stock@K
```

### t0

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers.*

```{r, stock-t0, results = FALSE, echo = TRUE}
stock@t0
```

### LenCV

*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, stock-LenCV, results = FALSE, echo = TRUE}
stock@LenCV
```

### Ksd

*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, stock-Ksd, results = FALSE, echo = TRUE}
stock@Ksd
```

### Linfsd

*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, stock-Linfsd, results = FALSE, echo = TRUE}
stock@Linfsd
```

### L50

*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, stock-L50, results = FALSE, echo = TRUE}
stock@L50
```

### L50_95

*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, stock-L50_95, results = FALSE, echo = TRUE}
stock@L50_95
```

### D

*Current level of stock depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction.*

```{r, stock-D, results = FALSE, echo = TRUE}
stock@D
```

### a

*Length-weight parameter alpha. Single value. Positive real number.*

```{r, stock-a, results = FALSE, echo = TRUE}
stock@a
```

### b

*Length-weight parameter beta. Single value. Positive real number.*

```{r, stock-b, results = FALSE, echo = TRUE}
stock@b
```

### Size_area_1

*The size of area 1 relative to area 2. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, stock-Size_area_1, results = FALSE, echo = TRUE}
stock@Size_area_1
```

### Frac_area_1

*The fraction of the unfished biomass in stock 1. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, stock-Frac_area_1, results = FALSE, echo = TRUE}
stock@Frac_area_1
```

### Prob_staying

*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*

```{r, stock-Prob_staying, results = FALSE, echo = TRUE}
stock@Prob_staying
```

### Fdisc

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, stock-Fdisc, results = FALSE, echo = TRUE}
stock@Fdisc
```

### Source

*A reference to a website or article from which parameters were taken to define the stock object. Single value. Character string.*

```{r, stock-Source, results = FALSE, echo = TRUE}
stock@Source
```

## FLEET SLOT DESCRIPTIONS

```{r warnings = FALSE}
fleet <- methods::new('Fleet')
```

### Name

*Name of the Fleet object. Single value. Character string.*

```{r, fleet-Name, results = FALSE, echo = TRUE}
fleet@Name
```

### nyears

*The number of years for the historical spool-up simulation. Single value. Positive integer.*

```{r, fleet-nyears, results = FALSE, echo = TRUE}
fleet@nyears
```

### Spat_targ

*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers.*

```{r, fleet-Spat_targ, results = FALSE, echo = TRUE}
fleet@Spat_targ
```

### EffYears

*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers.*

```{r, fleet-EffYears, results = FALSE, echo = TRUE}
fleet@EffYears
```

### EffLower

*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers.*

```{r, fleet-EffLower, results = FALSE, echo = TRUE}
fleet@EffLower
```

### EffUpper

*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers.*

```{r, fleet-EffUpper, results = FALSE, echo = TRUE}
fleet@EffUpper
```

### Esd

*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, fleet-Esd, results = FALSE, echo = TRUE}
fleet@Esd
```

### qinc

*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, fleet-qinc, results = FALSE, echo = TRUE}
fleet@qinc
```

### qcv

*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, fleet-qcv, results = FALSE, echo = TRUE}
fleet@qcv
```

### L5

*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, fleet-L5, results = FALSE, echo = TRUE}
fleet@L5
```

### LFS

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, fleet-LFS, results = FALSE, echo = TRUE}
fleet@LFS
```

### Vmaxlen

*The vulnerability of fish at Stock@Linf . Uniform distribution lower and upper bounds. Fraction.*

```{r, fleet-Vmaxlen, results = FALSE, echo = TRUE}
fleet@Vmaxlen
```

### isRel

*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*

```{r, fleet-isRel, results = FALSE, echo = TRUE}
fleet@isRel
```

### LR5

*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, fleet-LR5, results = FALSE, echo = TRUE}
fleet@LR5
```

### LFR

*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, fleet-LFR, results = FALSE, echo = TRUE}
fleet@LFR
```

### Rmaxlen

*The retention of fish at Stock@Linf . Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, fleet-Rmaxlen, results = FALSE, echo = TRUE}
fleet@Rmaxlen
```

### DR

*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction.*

```{r, fleet-DR, results = FALSE, echo = TRUE}
fleet@DR
```

### SelYears

*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers.*

```{r, fleet-SelYears, results = FALSE, echo = TRUE}
fleet@SelYears
```

### AbsSelYears

*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers.*

```{r, fleet-AbsSelYears, results = FALSE, echo = TRUE}
fleet@AbsSelYears
```

### L5Lower

*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r, fleet-L5Lower, results = FALSE, echo = TRUE}
fleet@L5Lower
```

### L5Upper

*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r, fleet-L5Upper, results = FALSE, echo = TRUE}
fleet@L5Upper
```

### LFSLower

*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r, fleet-LFSLower, results = FALSE, echo = TRUE}
fleet@LFSLower
```

### LFSUpper

*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r, fleet-LFSUpper, results = FALSE, echo = TRUE}
fleet@LFSUpper
```

### VmaxLower

*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction.*

```{r, fleet-VmaxLower, results = FALSE, echo = TRUE}
fleet@VmaxLower
```

### VmaxUpper

*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction.*

```{r, fleet-VmaxUpper, results = FALSE, echo = TRUE}
fleet@VmaxUpper
```

### CurrentYr

*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*

```{r, fleet-CurrentYr, results = FALSE, echo = TRUE}
fleet@CurrentYr
```

### MPA

*(Optional) Matrix specifying spatial closures for historical years.*

```{r, fleet-MPA, results = FALSE, echo = TRUE}
fleet@MPA
```

## OBS SLOT DESCRIPTIONS

```{r warnings = FALSE}
obs <- methods::new('Obs')
```

### Name

*The name of the observation model object. Single value. Character string.*

```{r, obs-Name, results = FALSE, echo = TRUE}
obs@Name
```

### Cobs

*Log-normal catch observation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, obs-Cobs, results = FALSE, echo = TRUE}
obs@Cobs
```

### Cbiascv

*Log-normal coefficient of variation controlling the sampling of bias in catch observations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, obs-Cbiascv, results = FALSE, echo = TRUE}
obs@Cbiascv
```

### CAA_nsamp

*Number of catch-at-age observation per time step. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-CAA_nsamp, results = FALSE, echo = TRUE}
obs@CAA_nsamp
```

### CAA_ESS

*Effective sample size (independent age draws) of the multinomial catch-at-age observation error model. Uniform distribution lower and upper bounds. Positive integers.*

```{r, obs-CAA_ESS, results = FALSE, echo = TRUE}
obs@CAA_ESS
```

### CAL_nsamp

*Number of catch-at-length observation per time step. Uniform distribution lower and upper bounds. Positive integers.*

```{r, obs-CAL_nsamp, results = FALSE, echo = TRUE}
obs@CAL_nsamp
```

### CAL_ESS

*Effective sample size (independent length draws) of the multinomial catch-at-length observation error model. Uniform distribution lower and upper bounds. Positive integers.*

```{r, obs-CAL_ESS, results = FALSE, echo = TRUE}
obs@CAL_ESS
```

### Iobs

*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Iobs, results = FALSE, echo = TRUE}
obs@Iobs
```

### Ibiascv

*Log-normal coefficient of variation controlling error in observations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Ibiascv, results = FALSE, echo = TRUE}
obs@Ibiascv
```

### Btobs

*Log-normal coefficient of variation controlling error in observations of current stock biomass among years. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Btobs, results = FALSE, echo = TRUE}
obs@Btobs
```

### Btbiascv

*Uniform-log bounds for sampling persistent bias in current stock biomass. Uniform-log distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Btbiascv, results = FALSE, echo = TRUE}
obs@Btbiascv
```

### beta

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-beta, results = FALSE, echo = TRUE}
obs@beta
```

### LenMbiascv

*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-LenMbiascv, results = FALSE, echo = TRUE}
obs@LenMbiascv
```

### Mbiascv

*Log-normal coefficient of variation for sampling persistent bias in observed natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Mbiascv, results = FALSE, echo = TRUE}
obs@Mbiascv
```

### Kbiascv

*Log-normal coefficient of variation for sampling persistent bias in observed growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Kbiascv, results = FALSE, echo = TRUE}
obs@Kbiascv
```

### t0biascv

*Log-normal coefficient of variation for sampling persistent bias in observed t0. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-t0biascv, results = FALSE, echo = TRUE}
obs@t0biascv
```

### Linfbiascv

*Log-normal coefficient of variation for sampling persistent bias in observed maximum length. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Linfbiascv, results = FALSE, echo = TRUE}
obs@Linfbiascv
```

### LFCbiascv

*Log-normal coefficient of variation for sampling persistent bias in observed length at first capture. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-LFCbiascv, results = FALSE, echo = TRUE}
obs@LFCbiascv
```

### LFSbiascv

*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-LFSbiascv, results = FALSE, echo = TRUE}
obs@LFSbiascv
```

### FMSYbiascv

*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-FMSYbiascv, results = FALSE, echo = TRUE}
obs@FMSYbiascv
```

### FMSY_Mbiascv

*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-FMSY_Mbiascv, results = FALSE, echo = TRUE}
obs@FMSY_Mbiascv
```

### BMSY_B0biascv

*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-BMSY_B0biascv, results = FALSE, echo = TRUE}
obs@BMSY_B0biascv
```

### Irefbiascv

*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Irefbiascv, results = FALSE, echo = TRUE}
obs@Irefbiascv
```

### Brefbiascv

*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Brefbiascv, results = FALSE, echo = TRUE}
obs@Brefbiascv
```

### Crefbiascv

*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Crefbiascv, results = FALSE, echo = TRUE}
obs@Crefbiascv
```

### Dbiascv

*Log-normal coefficient of variation for sampling persistent bias in stock depletion. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Dbiascv, results = FALSE, echo = TRUE}
obs@Dbiascv
```

### Dobs

*Log-normal coefficient of variation controlling error in observations of stock depletion among years. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Dobs, results = FALSE, echo = TRUE}
obs@Dobs
```

### hbiascv

*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-hbiascv, results = FALSE, echo = TRUE}
obs@hbiascv
```

### Recbiascv

*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, obs-Recbiascv, results = FALSE, echo = TRUE}
obs@Recbiascv
```

## IMP SLOT DESCRIPTIONS

```{r warnings = FALSE}
imp <- methods::new('Imp')
```

### Name

*The name of the Implementation error object. Single value. Character string.*

```{r, imp-Name, results = FALSE, echo = TRUE}
imp@Name
```

### TACFrac

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*

```{r, imp-TACFrac, results = FALSE, echo = TRUE}
imp@TACFrac
```

### TACSD

*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, imp-TACSD, results = FALSE, echo = TRUE}
imp@TACSD
```

### TAEFrac

*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*

```{r, imp-TAEFrac, results = FALSE, echo = TRUE}
imp@TAEFrac
```

### TAESD

*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, imp-TAESD, results = FALSE, echo = TRUE}
imp@TAESD
```

### SizeLimFrac

*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*

```{r, imp-SizeLimFrac, results = FALSE, echo = TRUE}
imp@SizeLimFrac
```

### SizeLimSD

*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, imp-SizeLimSD, results = FALSE, echo = TRUE}
imp@SizeLimSD
```

## OM SLOT DESCRIPTIONS

```{r warnings = FALSE}
om <- methods::new('OM')
```

### Name

*Name of the operating model.*

```{r, om-Name, results = FALSE, echo = TRUE}
om@Name
```

### Agency

*Name of the agency responsible for the management of the fishery. Character string.*

```{r, om-Agency, results = FALSE, echo = TRUE}
om@Agency
```

### Region

*Name of the general geographic region of the fishery. Character string.*

```{r, om-Region, results = FALSE, echo = TRUE}
om@Region
```

### Sponsor

*Name of the organization who sponsored the OM. Character string.*

```{r, om-Sponsor, results = FALSE, echo = TRUE}
om@Sponsor
```

### Latitude

*Latitude (decimal degrees). Negative values represent the South of the Equator. Numeric. Single value.*

```{r, om-Latitude, results = FALSE, echo = TRUE}
om@Latitude
```

### Longitude

*Longitude (decimal degrees). Negative values represent the West of the Prime Meridian. Numeric. Single value.*

```{r, om-Longitude, results = FALSE, echo = TRUE}
om@Longitude
```

### nsim

*The number of simulations.*

```{r, om-nsim, results = FALSE, echo = TRUE}
om@nsim
```

### proyears

*The number of projected years.*

```{r, om-proyears, results = FALSE, echo = TRUE}
om@proyears
```

### interval

*The assessment interval - how often would you like to update the management system?*

```{r, om-interval, results = FALSE, echo = TRUE}
om@interval
```

### pstar

*The percentile of the sample of the management recommendation for each method.*

```{r, om-pstar, results = FALSE, echo = TRUE}
om@pstar
```

### maxF

*Maximum instantaneous fishing mortality rate that may be simulated for any given age class.*

```{r, om-maxF, results = FALSE, echo = TRUE}
om@maxF
```

### reps

*Number of samples of the management recommendation for each method. Note that when this is set to 1, the mean value of the data inputs is used.*

```{r, om-reps, results = FALSE, echo = TRUE}
om@reps
```

### cpars

*A list of custom parameters. Time series are a matrix nsim rows by nyears columns. Single parameters are a vector nsim long.*

```{r, om-cpars, results = FALSE, echo = TRUE}
om@cpars
```

### seed

*A random seed to ensure users can reproduce results exactly.*

```{r, om-seed, results = FALSE, echo = TRUE}
om@seed
```

### Source

*A reference to a website or article from which parameters were taken to define the operating model.*

```{r, om-Source, results = FALSE, echo = TRUE}
om@Source
```

### Common_Name

*Common name of the species. Character string.*

```{r, om-Common_Name, results = FALSE, echo = TRUE}
om@Common_Name
```

### Species

*Scientific name of the species. Genus and species name. Character string.*

```{r, om-Species, results = FALSE, echo = TRUE}
om@Species
```

### maxage

*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer.*

```{r, om-maxage, results = FALSE, echo = TRUE}
om@maxage
```

### R0

*The magnitude of unfished recruitment. Single value. Positive real number.*

```{r, om-R0, results = FALSE, echo = TRUE}
om@R0
```

### M

*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number.*

```{r, om-M, results = FALSE, echo = TRUE}
om@M
```

### M2

*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number.*

```{r, om-M2, results = FALSE, echo = TRUE}
om@M2
```

### Mexp

*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*

```{r, om-Mexp, results = FALSE, echo = TRUE}
om@Mexp
```

### Msd

*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Msd, results = FALSE, echo = TRUE}
om@Msd
```

### h

*Steepness of the stock recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1.*

```{r, om-h, results = FALSE, echo = TRUE}
om@h
```

### SRrel

*Type of stock-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer.*

```{r, om-SRrel, results = FALSE, echo = TRUE}
om@SRrel
```

### Perr

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Perr, results = FALSE, echo = TRUE}
om@Perr
```

### AC

*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-AC, results = FALSE, echo = TRUE}
om@AC
```

### Period

*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Period, results = FALSE, echo = TRUE}
om@Period
```

### Amplitude

*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1.*

```{r, om-Amplitude, results = FALSE, echo = TRUE}
om@Amplitude
```

### Linf

*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Linf, results = FALSE, echo = TRUE}
om@Linf
```

### K

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-K, results = FALSE, echo = TRUE}
om@K
```

### t0

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers.*

```{r, om-t0, results = FALSE, echo = TRUE}
om@t0
```

### LenCV

*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-LenCV, results = FALSE, echo = TRUE}
om@LenCV
```

### Ksd

*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Ksd, results = FALSE, echo = TRUE}
om@Ksd
```

### Linfsd

*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Linfsd, results = FALSE, echo = TRUE}
om@Linfsd
```

### L50

*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-L50, results = FALSE, echo = TRUE}
om@L50
```

### L50_95

*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-L50_95, results = FALSE, echo = TRUE}
om@L50_95
```

### D

*Current level of stock depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction.*

```{r, om-D, results = FALSE, echo = TRUE}
om@D
```

### a

*Length-weight parameter alpha. Single value. Positive real number.*

```{r, om-a, results = FALSE, echo = TRUE}
om@a
```

### b

*Length-weight parameter beta. Single value. Positive real number.*

```{r, om-b, results = FALSE, echo = TRUE}
om@b
```

### Size_area_1

*The size of area 1 relative to area 2. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Size_area_1, results = FALSE, echo = TRUE}
om@Size_area_1
```

### Frac_area_1

*The fraction of the unfished biomass in stock 1. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Frac_area_1, results = FALSE, echo = TRUE}
om@Frac_area_1
```

### Prob_staying

*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*

```{r, om-Prob_staying, results = FALSE, echo = TRUE}
om@Prob_staying
```

### Fdisc

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Fdisc, results = FALSE, echo = TRUE}
om@Fdisc
```

### nyears

*The number of years for the historical spool-up simulation. Single value. Positive integer.*

```{r, om-nyears, results = FALSE, echo = TRUE}
om@nyears
```

### Spat_targ

*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers.*

```{r, om-Spat_targ, results = FALSE, echo = TRUE}
om@Spat_targ
```

### EffYears

*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers.*

```{r, om-EffYears, results = FALSE, echo = TRUE}
om@EffYears
```

### EffLower

*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers.*

```{r, om-EffLower, results = FALSE, echo = TRUE}
om@EffLower
```

### EffUpper

*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers.*

```{r, om-EffUpper, results = FALSE, echo = TRUE}
om@EffUpper
```

### Esd

*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Esd, results = FALSE, echo = TRUE}
om@Esd
```

### qinc

*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-qinc, results = FALSE, echo = TRUE}
om@qinc
```

### qcv

*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-qcv, results = FALSE, echo = TRUE}
om@qcv
```

### L5

*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-L5, results = FALSE, echo = TRUE}
om@L5
```

### LFS

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-LFS, results = FALSE, echo = TRUE}
om@LFS
```

### Vmaxlen

*The vulnerability of fish at Stock@Linf . Uniform distribution lower and upper bounds. Fraction.*

```{r, om-Vmaxlen, results = FALSE, echo = TRUE}
om@Vmaxlen
```

### isRel

*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*

```{r, om-isRel, results = FALSE, echo = TRUE}
om@isRel
```

### LR5

*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-LR5, results = FALSE, echo = TRUE}
om@LR5
```

### LFR

*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-LFR, results = FALSE, echo = TRUE}
om@LFR
```

### Rmaxlen

*The retention of fish at Stock@Linf . Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Rmaxlen, results = FALSE, echo = TRUE}
om@Rmaxlen
```

### DR

*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction.*

```{r, om-DR, results = FALSE, echo = TRUE}
om@DR
```

### SelYears

*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers.*

```{r, om-SelYears, results = FALSE, echo = TRUE}
om@SelYears
```

### AbsSelYears

*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers.*

```{r, om-AbsSelYears, results = FALSE, echo = TRUE}
om@AbsSelYears
```

### L5Lower

*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r, om-L5Lower, results = FALSE, echo = TRUE}
om@L5Lower
```

### L5Upper

*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r, om-L5Upper, results = FALSE, echo = TRUE}
om@L5Upper
```

### LFSLower

*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r, om-LFSLower, results = FALSE, echo = TRUE}
om@LFSLower
```

### LFSUpper

*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers.*

```{r, om-LFSUpper, results = FALSE, echo = TRUE}
om@LFSUpper
```

### VmaxLower

*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction.*

```{r, om-VmaxLower, results = FALSE, echo = TRUE}
om@VmaxLower
```

### VmaxUpper

*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction.*

```{r, om-VmaxUpper, results = FALSE, echo = TRUE}
om@VmaxUpper
```

### CurrentYr

*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*

```{r, om-CurrentYr, results = FALSE, echo = TRUE}
om@CurrentYr
```

### MPA

*(Optional) Matrix specifying spatial closures for historical years.*

```{r, om-MPA, results = FALSE, echo = TRUE}
om@MPA
```

### Cobs

*Log-normal catch observation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Cobs, results = FALSE, echo = TRUE}
om@Cobs
```

### Cbiascv

*Log-normal coefficient of variation controlling the sampling of bias in catch observations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-Cbiascv, results = FALSE, echo = TRUE}
om@Cbiascv
```

### CAA_nsamp

*Number of catch-at-age observation per time step. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-CAA_nsamp, results = FALSE, echo = TRUE}
om@CAA_nsamp
```

### CAA_ESS

*Effective sample size (independent age draws) of the multinomial catch-at-age observation error model. Uniform distribution lower and upper bounds. Positive integers.*

```{r, om-CAA_ESS, results = FALSE, echo = TRUE}
om@CAA_ESS
```

### CAL_nsamp

*Number of catch-at-length observation per time step. Uniform distribution lower and upper bounds. Positive integers.*

```{r, om-CAL_nsamp, results = FALSE, echo = TRUE}
om@CAL_nsamp
```

### CAL_ESS

*Effective sample size (independent length draws) of the multinomial catch-at-length observation error model. Uniform distribution lower and upper bounds. Positive integers.*

```{r, om-CAL_ESS, results = FALSE, echo = TRUE}
om@CAL_ESS
```

### Iobs

*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Iobs, results = FALSE, echo = TRUE}
om@Iobs
```

### Ibiascv

*Log-normal coefficient of variation controlling error in observations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Ibiascv, results = FALSE, echo = TRUE}
om@Ibiascv
```

### Btobs

*Log-normal coefficient of variation controlling error in observations of current stock biomass among years. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Btobs, results = FALSE, echo = TRUE}
om@Btobs
```

### Btbiascv

*Uniform-log bounds for sampling persistent bias in current stock biomass. Uniform-log distribution lower and upper bounds. Positive real numbers.*

```{r, om-Btbiascv, results = FALSE, echo = TRUE}
om@Btbiascv
```

### beta

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-beta, results = FALSE, echo = TRUE}
om@beta
```

### LenMbiascv

*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-LenMbiascv, results = FALSE, echo = TRUE}
om@LenMbiascv
```

### Mbiascv

*Log-normal coefficient of variation for sampling persistent bias in observed natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Mbiascv, results = FALSE, echo = TRUE}
om@Mbiascv
```

### Kbiascv

*Log-normal coefficient of variation for sampling persistent bias in observed growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Kbiascv, results = FALSE, echo = TRUE}
om@Kbiascv
```

### t0biascv

*Log-normal coefficient of variation for sampling persistent bias in observed t0. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-t0biascv, results = FALSE, echo = TRUE}
om@t0biascv
```

### Linfbiascv

*Log-normal coefficient of variation for sampling persistent bias in observed maximum length. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Linfbiascv, results = FALSE, echo = TRUE}
om@Linfbiascv
```

### LFCbiascv

*Log-normal coefficient of variation for sampling persistent bias in observed length at first capture. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-LFCbiascv, results = FALSE, echo = TRUE}
om@LFCbiascv
```

### LFSbiascv

*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-LFSbiascv, results = FALSE, echo = TRUE}
om@LFSbiascv
```

### FMSYbiascv

*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-FMSYbiascv, results = FALSE, echo = TRUE}
om@FMSYbiascv
```

### FMSY_Mbiascv

*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-FMSY_Mbiascv, results = FALSE, echo = TRUE}
om@FMSY_Mbiascv
```

### BMSY_B0biascv

*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-BMSY_B0biascv, results = FALSE, echo = TRUE}
om@BMSY_B0biascv
```

### Irefbiascv

*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Irefbiascv, results = FALSE, echo = TRUE}
om@Irefbiascv
```

### Brefbiascv

*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Brefbiascv, results = FALSE, echo = TRUE}
om@Brefbiascv
```

### Crefbiascv

*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Crefbiascv, results = FALSE, echo = TRUE}
om@Crefbiascv
```

### Dbiascv

*Log-normal coefficient of variation for sampling persistent bias in stock depletion. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Dbiascv, results = FALSE, echo = TRUE}
om@Dbiascv
```

### Dobs

*Log-normal coefficient of variation controlling error in observations of stock depletion among years. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Dobs, results = FALSE, echo = TRUE}
om@Dobs
```

### hbiascv

*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-hbiascv, results = FALSE, echo = TRUE}
om@hbiascv
```

### Recbiascv

*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers.*

```{r, om-Recbiascv, results = FALSE, echo = TRUE}
om@Recbiascv
```

### TACFrac

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*

```{r, om-TACFrac, results = FALSE, echo = TRUE}
om@TACFrac
```

### TACSD

*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-TACSD, results = FALSE, echo = TRUE}
om@TACSD
```

### TAEFrac

*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*

```{r, om-TAEFrac, results = FALSE, echo = TRUE}
om@TAEFrac
```

### TAESD

*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-TAESD, results = FALSE, echo = TRUE}
om@TAESD
```

### SizeLimFrac

*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*

```{r, om-SizeLimFrac, results = FALSE, echo = TRUE}
om@SizeLimFrac
```

### SizeLimSD

*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*

```{r, om-SizeLimSD, results = FALSE, echo = TRUE}
om@SizeLimSD
```

