`r if(knitr:::is_latex_output()) '\\Appendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

# EXPLORING CATCH AND EFFORT TIMESERIES FOR PACIFIC COD

This appendix has three purposes:

1. Derive a consistent measure of (bottom trawl) commercial fishing effort that is relevant to Pacific Cod. To do this we will look at effort for depths and localities that have the highest proportion of Pacific Cod catches. 

2. Bring in code from 2018 assessment to run standardized catch per unit effort index.

The effort times will be used to parameterize the operating model. The catch time series will be used as part of checking the calibration of the operating model. The catch timeseries and CPUE timeseries may be used when applying a management procedure to the observed data.

```{r download-data-pc}
#Make sure these two area descriptions match up
pcod_areas <- c("05","06","07","08") #QCS and HS for comm samples, surv samples and catch
pcod_survey_areas <- c("Queen Charlotte Sound Synoptic Bottom Trawl" ,"Hecate Strait Synoptic Bottom Trawl") #QCS and HS for survey index
science_name <- "Gadus macrocephalus"
species_name <- "Pacific Cod"
species_file <- here::here("generated-data",
  paste0(gsub(" ", "-", species_name), ".rds"))
if (!file.exists(species_file)) {
  .dpc <- list()
  .dpc$commercial_samples <- gfplot::get_commercial_samples(species_name)
  .dpc$survey_samples <- gfplot::get_survey_samples(species_name)
  .dpc$catch <- gfplot::get_catch(species_name)
  .dpc$survey_index <- gfplot::get_survey_index(species_name)
  saveRDS(d, file = species_file)
} else {
  .dpc <- readRDS(species_file)
}

#Get only 5ABCD data
.dpc$commercial_samples <- .dpc$commercial_samples %>% 
  filter(major_stat_area_code %in% pcod_areas)

.dpc$survey_samples <- .dpc$survey_samples %>% 
  filter(major_stat_area_code %in% pcod_areas)

.dpc$catch <- .dpc$catch %>% 
  filter(major_stat_area_code %in% pcod_areas)

.dpc$survey_index <- .dpc$survey_index %>% 
  filter(survey_series_desc %in% pcod_survey_areas)

```

## EFFORT

```{r effort-get-data-pc}
.f <- here::here("report/data/cpue-historical-pcod.rds")
if (!file.exists(.f)) {
  dat_historicalpc <- gfplot::get_cpue_historical(species = NULL, end_year = 2018)
  saveRDS(dat_historicalpc, file = .f)
} else {
  dat_historicalpc <- readRDS(.f)
}
```

```{r effort-load-packages-pc, warning=FALSE, message=FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)
```

```{r effort-plot-raw-data-pc}
dat_historicalpc %>% 
  group_by(year) %>% 
  summarize(effort = sum(hours_fished )) %>% 
  ggplot(aes(year, effort)) + 
  geom_line()
```

<!-- We will process the data the way we have before. This tidies the data so that we can work with it and puts the depths into bins. -->

```{r effort-tidy-data-pc}
datpc <- gfplot::tidy_cpue_historical(dat_historicalpc,
  species_common = "pacific cod",
  use_alt_year = FALSE,
  year_range = range(dat_historicalpc$year),
  depth_band_width = 25,
  area_grep_pattern = "^5A|^5B|^5C|^5D",
  depth_bin_quantiles = c(0, 1),
  min_bin_prop = 0,
  type = "trip-level-data")
```

Let's look at the distribution of trips by depth by year in terms of which trips caught Pacific Cod:

```{r effort-depth-distribution-pc}
gpc <- datpc %>%
  mutate(time_bin = seq(1930, 2020, 5)[findInterval(year, vec = seq(1930, 2020, 5))]) %>% 
  mutate(`Trip\ncaught this species` = 
      ifelse(pos_catch == 1, "Yes", "No")) %>%
  filter(best_depth < 800) %>% 
  ggplot(aes(best_depth, fill = `Trip\ncaught this species`)) +
  geom_histogram(binwidth = 25) +
  ylim(0, NA) +
  coord_cartesian(expand = FALSE)
gpc

gpc + facet_wrap(~time_bin)
```

Pacific Cod are usually caught in fairly shallow waters---usually shallower than around 300m. 

We can look at a bubble plot of positive trips by year and locality. We will only show localities with at least 10 positive trips. The outside circle represents the number of trips. The inside coloured circle represents the number of trips that that reported catching at least Pacific Cod. 

```{r effort-locality-bubble-plot-pc}
datpc %>% group_by(locality) %>% 
  mutate(total_positive_trips = sum(pos_catch)) %>% 
  filter(total_positive_trips > 10) %>% 
  gfplot:::plot_predictor_bubbles("locality",
    group = "trip_id") %>% print()
```

Let's look at the effort for the localities and depths that make up 80% of the Pacific Cod catch. 

```{r effort-find-major-localities-and-depths-pc}
locality_keeppc <- datpc %>% group_by(locality) %>%
  summarize(locality_pcod_catch = sum(spp_catch)) %>% 
  arrange(-locality_pcod_catch) %>% 
  mutate(cumulative_catch = cumsum(locality_pcod_catch)/
      sum(locality_pcod_catch)) %>% 
  arrange(cumulative_catch) %>% 
  filter(cumulative_catch > 0) %>% 
  filter(cumulative_catch < 0.8)

depth_keeppc <- datpc %>%
  group_by(depth) %>% 
  summarize(depth_pcod_catch = sum(spp_catch)) %>% 
  mutate(depth = as.numeric(as.character(depth))) %>% 
  arrange(-depth) %>% 
  mutate(cumulative_catch = cumsum(depth_pcod_catch)/
      sum(depth_pcod_catch)) %>%
  filter(cumulative_catch > 0) %>% 
  arrange(-depth) %>% 
  filter(cumulative_catch < 0.8)
```

```{r effort-locality-and-depth-tables-pc}
csasdown::csas_table(locality_keeppc, digits = c(0, 0, 2))
csasdown::csas_table(depth_keeppc, digits = c(0, 0, 2))
```

```{r effort-pull-pc}
depth_keeppc <- depth_keeppc %>% pull(depth)
locality_keeppc <- locality_keeppc %>% pull(locality)
```

Let's define a relevant "fleet" based on trips that are recorded at our filtered "prime Pacific Cod" depths and localities and look at the distribution of trips that did and did not catch Pacific Cod in our filtered data set:

```{r effort-histogram-relevant-fleet-pc}
dat_keeppc <- filter(datpc, best_depth > min(depth_keeppc) & locality %in% locality_keeppc)
dat_keeppc %>%
  mutate(time_bin = seq(1930, 2020, 5)[findInterval(year, vec = seq(1930, 2020, 5))]) %>% 
  mutate(`Trip\ncaught this species` = 
      ifelse(pos_catch == 1, "Yes", "No")) %>%
  filter(best_depth < 800) %>% 
  ggplot(aes(best_depth, fill = `Trip\ncaught this species`)) +
  geom_histogram(binwidth = 25) +
  ylim(0, NA) +
  coord_cartesian(expand = FALSE)
```

Defined as we have here, our "fleet" represents approximately `r round(sum(dat_keeppc$spp_catch) / sum(datpc$spp_catch) * 100, 0)`% of the total Pacific Cod catch in our databases from `r min(datpc$year)` to `r max(datpc$year)`.

Finally, we can look at the effort trajectory from our filtered data set:

```{r effort-basic-ts-pc}
dat_keeppc %>% 
  group_by(year) %>% 
  summarize(hours_fished = sum(hours_fished)) %>% 
  ggplot(aes(year, hours_fished)) + 
  geom_line()
```

```{r effort-save-csv-pc}
dat_keeppc %>% 
  group_by(year) %>% 
  summarize(hours_fished = sum(hours_fished)) %>% 
  readr::write_csv(path = here::here("report/data/pcod-fleet-effort.csv"))
```


```{r effort-basic-ts-catch-pc}
dat_keeppc %>%
  # filter(best_depth <= 800, year >= 1970) %>% 
  group_by(year) %>% 
  summarize(spp_catch = sum(spp_catch)) %>% 
  ggplot(aes(year, spp_catch)) + 
  geom_line()
```

We can also try jackknifing out individual localities to look at the sensitivity to any individual locality:

```{r effort-locality-sensitivity-pc}
get_effortpc <- function(excluded_locality) {
  dat_keeppc %>%
    filter(locality != excluded_locality) %>% 
    group_by(year) %>% 
    summarize(hours_fished = sum(hours_fished), excluded_locality = excluded_locality)
}
purrr::map_df(unique(dat_keeppc$locality), ~get_effortpc(.x)) %>% 
  ggplot(aes(year, hours_fished, colour = excluded_locality)) + 
  geom_line() +
  guides(colour = FALSE)
```

The timeseries of effort does not seem too sensitive to any one locality.  *NOTE: Maybe the cyan series (recent years) and the blue series (early years)*

How sensitive is the effort timeseries to our definition of common depths for Pacific Cod assuming we work with these same localities?

```{r effort-depth-sensitivity-pc}
get_effortpc <- function(depth_threshold) {
  filter(datpc, best_depth > depth_threshold & locality %in% locality_keeppc) %>% 
    group_by(year) %>% 
    summarize(hours_fished = sum(hours_fished), depth_threshold = depth_threshold)
}
g <- purrr::map_df(seq(150, 800, 50), ~get_effortpc(.x)) %>%
  ggplot(aes(year, hours_fished, 
    group = as.factor(depth_threshold), colour = depth_threshold)) + 
  geom_line() +
  scale_color_viridis_c()
g

# g + scale_y_continuous(trans = "sqrt")
```

**This is Placeholder text for shortraker* 

The depth threshold does affect the perceived ramp-up in effort to 1996, but it does not have a big effect on the perceived effort timeseries after 1996. This can help us bound our operating models. There is certainly some omitted effort prior to 1996. FIXME: Need to discuss with industry ballpark how much may be missing and whether this is changing over time. FIXME: Also how much foreign effort might be missed here.

Perhaps we can parameterize an operating model with slowly increasing effort until around 1990, effort that increases approximately 3-fold from around 1990 to 1995 before declining to approximately the same level at 2000 and remaining relatively constant since. In the operating model, the effort prior to 1990 may need to be increased by some multiplier with a fair bit of uncertainty.

## HISTORICAL CATCH

Just use observed catch for Pacific Cod.

```{r plot-corrected-catch-pc}
corrected_catch <- .dpc$catch %>% group_by(year) %>%
  summarise(
    spp_catch_observed = sum(landed_kg)) %>% 
  transmute(
    Year = year,
      `Observed catch` = spp_catch_observed / 1e6)
readr::write_csv(corrected_catch, path = here::here("report/data/pcod-corrected-catch.csv"))

g <- corrected_catch %>% 
  reshape2::melt(id.vars = "Year", variable.name = "Type", value.name = "Catch") %>% 
  ggplot(aes(
    x = Year, 
    y = Catch, colour = Type)) + 
  # geom_vline(xintercept = 1996, lty = 2) + gfplot::theme_pbs() +
  geom_rect(xmin = 1900, xmax = 1996, ymin = 0, ymax = 1e9,
    fill = "grey90", inherit.aes = FALSE, alpha = 0.1) + 
  geom_line(lwd = 1) +
  gfplot::theme_pbs() + coord_cartesian(expand = FALSE) +
  scale_color_brewer(palette = "Set2") + ylab("Catch (1000 t)")
print(g)
```



## COMMERCIAL CATCH PER UNIT EFFORT

Previously we have always conducted catch per unit effort analyses separately for the historical and modern time periods. Since it's important to try to figure out (very approximately) what has been happening over the entire timeseries for the purposes of parameterizing our operating model, here I will try to combine the two. Because there is not sufficient data in each depth bin for each year we will work with a quadratic function for depth instead of the binned factor predictors that has been used in similar analyses at PBS in the past. The form of our model (in a quick draft R format) is:

```
cpue = Tweedie(mu, phi, power),
mu ~ exp(0 + year_factor + month + depth_scaled + I(depth_scaled^2) + 
  (1 | locality) + (1 | year_locality)).
```

```{r effort-fit-cpue-pc, warning=FALSE}
dpc <- filter(dat_keeppc, year >= 1955, best_depth <= 800)
dpc$year_locality <- paste0(dpc$year, dpc$locality)
dpc$depth <- as.factor(dpc$depth)
dpc$month <- as.factor(dpc$month)
dpc$locality <- as.factor(dpc$locality)
dpc$year_locality <- as.factor(dpc$year_locality)
dpc$year_factor <- as.factor(dpc$year_factor)
dpc$depth_scaled <- dpc$best_depth - mean(dpc$best_depth)

dpc %>% group_by(year) %>%
  summarise(
    effort = sum(hours_fished),
    catch_observed = sum(spp_catch)
    ) %>%
  select(year, catch_observed) %>% 
  reshape2::melt(id.vars = "year", variable.name = "Type") %>% 
  ggplot(aes(year, value, colour = Type)) + geom_line()

dpc %>% group_by(year) %>%
  summarise(effort = sum(hours_fished)) %>%
  ggplot(aes(year, effort)) + geom_line()


```



```{r effort-plot-cpue-uncorrected-pc}
m <- gfplot::fit_cpue_index_glmmtmb(dpc,
  cpue ~ 0 + year_factor + month + depth_scaled + I(depth_scaled^2) + 
    (1 | locality) + (1 | year_locality), verbose = FALSE)

gfplot::predict_cpue_index_tweedie(m) %>%
  ggplot(aes(year, est, ymin = lwr, ymax = upr)) + 
  geom_ribbon(alpha = .5) + 
  geom_line() +
  geom_vline(xintercept = 1996, lty = 2)
```


