```{r message = FALSE}
library(DLMtool)
knitr_results <- TRUE
knitr_echo <- TRUE
```


## STOCK SLOT DESCRIPTIONS {#app:desc-stock}

```{r warnings = FALSE}
stock <- methods::new('Stock')
```

```{r, echo=FALSE}
stock@Size_area_1 <- c(0.5, 0.5)
stock@Frac_area_1 <- c(0.5, 0.5)
stock@Prob_staying <- c(0.5, 0.5)
stock@Mexp <- c(NA_real_, NA_real_)
```

<!-- slot-chunk-begin -->
### Name {#app:desc-stock-name}

*The name of the Stock object. Single value. Character string*


```{r desc-stock-name, results = knitr_results, echo = knitr_echo}
stock@Name <- "Rex Sole"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Common_Name {#app:desc-stock-common_name}

*Common name of the species. Character string*


```{r desc-stock-common_name, results = knitr_results, echo = knitr_echo}
stock@Common_Name <- "Rex Sole"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Species {#app:desc-stock-species}

*Scientific name of the species. Genus and species name. Character string*


```{r desc-stock-species, results = knitr_results, echo = knitr_echo}
stock@Species <- "Glyptocephalus zachirus"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### maxage {#app:desc-stock-maxage}

*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer*

From @turnock2005. This is the plus group value. TODO Can't find turnock2005

From @munk2001, who document the maximum ages observed in various surveys in Alaska, note the maximum age observe for Rex Sole in the Gulf of Alaska is 27 years. We don't have ages in our database to inform the maximum age for this region.

```{r desc-stock-maxage, results = knitr_results, echo = knitr_echo}
stock@maxage <- 27
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### R0 {#app:desc-stock-r0}

*The magnitude of unfished recruitment. Single value. Positive real number*

The absolute value is meaningless here. Arbitrarily pick a value.

```{r desc-stock-r0, results = knitr_results, echo = knitr_echo}
stock@R0 <- 1000
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### M {#app:desc-stock-m}

*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number*

From @mcgilliard2017

```{r desc-stock-m, results = knitr_results, echo = knitr_echo}
stock@M <- c(0.17, 0.17) # TODO add uncertainty?
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### h {#app:desc-stock-h}

*Steepness of the stock recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1*

@maunder2012 cite @myers1999 who found a median value of steepness of 0.80 for flatfish and note that because of the bias in the value estimated for north Atlantic cod in that paper that the value might be closer to 0.94. @grandin2017arrowtooth estimated steepness for Arrowtooth Flounder, but found their posterior was highly influenced by their prior (they estimated a median of 0.88 with a 95% CI of 0.69--0.98). Here we will choose a value that encompasses this range with some extra uncertainty.

```{r desc-stock-h, results = knitr_results, echo = knitr_echo}
stock@h <- c(0.70, 0.95)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### SRrel {#app:desc-stock-srrel}

*Type of stock-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer*

We will use a Beverton-Holt stock-recruit relationship as is been used in most British Columbia groundfish assessments and is assumed in the estimates of steepness used in this operating model.

```{r desc-stock-srrel, results = knitr_results, echo = knitr_echo}
stock@SRrel <- 1L
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Perr {#app:desc-stock-perr}

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers*

FIXME: Need to look at other assessments. For now this was copied from the Shortraker OM.

@thorson2014 (Table 2) finds the mean standard deviation of log recruitment deviations for Pleuronectiformes to be about 0.64 with a standard deviation of about 0.26. We will set our uniform distribution to be approximately plus or minus one standard deviation.

```{r desc-stock-perr, results = knitr_results, echo = knitr_echo}
stock@Perr <- c(0.4, 0.9)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### AC {#app:desc-stock-ac}

*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers*

@thorson2014 (Table 2) finds the mean autocorrelation for Pleuronectiformes to be about 0.44 with a standard deviation of about 0.27. We will set our uniform distribution to be approximately plus or minus one standard deviation.

```{r desc-stock-ac, results = knitr_results, echo = knitr_echo}
stock@AC <- c(0.2, 0.7)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Linf {#app:desc-stock-linf}

*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers*

Alternatively from @turnock2005, table 4.12:
- Male = 39.5
- Female = 44.9

TODO: take the linf from the females above and add uncertainty (also for other VB parameters)

```{r desc-stock-linf, results = knitr_results, echo = knitr_echo}
# mvb <- gfplot::fit_vb(drex$survey_samples, sex = "all")
# mvb_summary <- summary(TMB::sdreport(mvb$model))
# vb_cv <- mvb_summary[,"Std. Error"] / abs(mvb_summary[,"Estimate"])
# gfplot::plot_vb(object_all = mvb, col = c("All" = "black"))
# stock@Linf <- c(-2, 2) * mvb_summary[,"Std. Error"][["linf"]] + mvb$pars[["linf"]]
stock@Linf <- c(39.5, 44.9)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### K {#app:desc-stock-k}

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers*

Alternatively from @turnock2005, table 4.12:
- Male = 0.38
- Female = 0.31

```{r desc-stock-k, results = knitr_results, echo = knitr_echo}
# stock@K <- c(-2, 2) * mvb_summary[,"Std. Error"][["k"]] + mvb$pars[["k"]]
stock@K <- c(0.31, 0.38)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### t0 {#app:desc-stock-t0}

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers*

Alternatively from @turnock2005, table 4.12:
- Male = 0.79
- Female = 0.69
Note - t0 was not reported in @mcgilliard2017, but @turnock2005 reported all values t0, K, and Linf

```{r desc-stock-t0, results = knitr_results, echo = knitr_echo}
# stock@t0 <- c(-2, 2) *  mvb_summary[,"Std. Error"][["t0"]] + mvb$pars[["t0"]]
stock@t0 <- c(0.69, 0.79)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LenCV {#app:desc-stock-lencv}

*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers*

TODO: picking a value here

```{r desc-stock-lencv, results = knitr_results, echo = knitr_echo}
# sd2cv <- function(.sd) sqrt(exp(.sd ^ 2) - 1)
# stock@LenCV <- sd2cv(exp(mvb$pars[["log_sigma"]]))
# round(stock@LenCV, 2)
stock@LenCV <- c(0.2, 0.2)
```
<!-- slot-chunk-end -->
### L50 {#app:desc-stock-l50}

*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*

Alternatively, see @abookire2006, Table 3, for value 35.17 cm.

```{r desc-stock-l50, results = knitr_results, echo = knitr_echo}
m_mat <- gfplot::fit_mat_ogive(drex$survey_samples, type = "length")
mat_perc <- pbs2dlm:::extract_maturity_perc(coef(m_mat$model))
se_l50 <- pbs2dlm:::delta_method(~ -(log((1/0.5) - 1) + x1 + x3) / (x2 + x4),
    mean = coef(m_mat$model), cov = vcov(m_mat$model))
gfplot::plot_mat_ogive(m_mat)

stock@L50 <- round(c(-2, 2) * se_l50 + mat_perc$f.p0.5, 1)
stock@L50
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L50_95 {#app:desc-stock-l50_95}

*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*

Alternatively, see @abookire2006, Table 3, for value 35.97 cm.

```{r desc-stock-l50_95, results = knitr_results, echo = knitr_echo}
se_l50_95m <- gfdlm:::delta_method(
  ~ -(log((1/0.95) - 1) + x1 + x3) / (x2 + x4) -
    -(log((1/0.5) - 1) + x1 + x3) / (x2 + x4),
    mean = coef(m_mat$model), cov = vcov(m_mat$model))
stock@L50_95 <- round(c(-2, 2) * se_l50_95m + (mat_perc$f.p0.95 - mat_perc$f.p0.5), 1)
stock@L50_95
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### D {#app:desc-stock-d}

*Current level of stock depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction*

This will be populated via the SRA model.

```{r desc-stock-d, results = knitr_results, echo = knitr_echo}
stock@D
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### a {#app:desc-stock-a}

*Length-weight parameter alpha. Single value. Positive real number*

Alternatively from @mcgilliard2017:
- Female = 1.35e-06
- Male = 2.18e-06

```{r desc-stock-a, results = knitr_results, echo = knitr_echo}
mlw <- gfplot::fit_length_weight(drex$survey_samples, sex = "all")
gfplot::plot_length_weight(object_all = mlw, col = c("All" = "black"))
stock@a <- exp(mlw$pars[["log_a"]])
round(log(stock@a), 2)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### b {#app:desc-stock-b}

*Length-weight parameter beta. Single value. Positive real number*

Alternatively from @mcgilliard2017:
- Female = 3.44963
- Male = 3.30571

```{r desc-stock-b, results = knitr_results, echo = knitr_echo}
stock@b <- mlw$pars[["b"]]
round(stock@b, 2)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Fdisc {#app:desc-stock-fdisc}

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers*

Since there is 100% observer coverage we can assume there is no unreported discards. Therefore the following slot does not get used.

```{r desc-stock-fdisc, results = knitr_results, echo = knitr_echo}
stock@Fdisc
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Source {#app:desc-stock-source}

*A reference to a website or article from which parameters were taken to define the stock object. Single value. Character string.*


```{r desc-stock-source, results = knitr_results, echo = knitr_echo}
stock@Source <- ""
```
<!-- slot-chunk-end -->

## FLEET SLOT DESCRIPTIONS {#app:desc-fleet}

```{r warnings = FALSE}
fleet <- DLMtool::Generic_Fleet # TODO: temporary
```

```{r warnings = FALSE}
fleet@Esd <- c(0, 0)
fleet@qinc <- c(0, 0)
fleet@qcv <- c(0, 0)
```

<!-- slot-chunk-begin -->
### Name {#app:desc-fleet-name}

*Name of the Fleet object. Single value. Character string.*


```{r desc-fleet-name, results = knitr_results, echo = knitr_echo}
fleet@Name <- "BC Fleet"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### nyears {#app:desc-fleet-nyears}

*The number of years for the historical spool-up simulation. Single value. Positive integer*

We will set the historical run-up to be approximately the length of the commercial fishery.

```{r desc-fleet-nyears, results = knitr_results, echo = knitr_echo}
catch_yrs <- unique(drex$catch$year)
fleet@nyears <- length(catch_yrs)
c(catch_yrs[1], catch_yrs[length(catch_yrs)])
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Spat_targ {#app:desc-fleet-spat_targ}

*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers*

We have set up a single area model.

```{r desc-fleet-spat_targ, results = knitr_results, echo = knitr_echo}
fleet@Spat_targ
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L5 {#app:desc-fleet-l5}

*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers*

```{r min-caught-rex}
min_caught <- min(drex$commercial_samples$length, na.rm = TRUE)
min_caught <- 14
```

TODO: in the data from this analysis report the minimum length caught in 3C is 14. Need to figure out why these are not in our filtered rex data.

Based on the slot `isRel` below, this lot needs to be filled in proportion of size-of-maturity. The 95% CI of size at maturity from this analysis is `r stock@L50[[1]]` to `r stock@L50[[2]]`. The shortest length fish in the commercial samples is `r min_caught`, although commercial samples are only available from 2015 in WCVI.

```{r desc-fleet-l5, results = knitr_results, echo = knitr_echo}
fleet@L5 <- c(min_caught/stock@L50[[2]], min_caught/stock@L50[[1]])
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFS {#app:desc-fleet-lfs}

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers*

Here's a comparison of the commercial and survey samples:

```{r}
hist(drex$commercial_samples$length, xlim = c(5, 60), breaks = 50);par(new = TRUE);plot(density(na.omit(drex$survey_samples$length)), xlim = c(5, 60), main = "", ylab = "", xlab = "", axes = FALSE)
# FIXME: missing a lot of samples
```

Based on the observed commercial length samples let's assume that Rex Sole is fully vulnerable to fishing by the like that 50% maturity. FIXME

```{r desc-fleet-lfs, results = knitr_results, echo = knitr_echo}
fleet@LFS <- c(0.9, 1.1)
```

<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Vmaxlen {#app:desc-fleet-vmaxlen}

*The vulnerability of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Fraction*

We will set this to 1. Setting this to a value lower than 1 would be assuming dome-shaped selectivity.

```{r desc-fleet-vmaxlen, results = knitr_results, echo = knitr_echo}
fleet@Vmaxlen <- c(1, 1)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### isRel {#app:desc-fleet-isrel}

*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*


```{r desc-fleet-isrel, results = knitr_results, echo = knitr_echo}
fleet@isRel
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LR5 {#app:desc-fleet-lr5}

*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleet-lr5, results = knitr_results, echo = knitr_echo}
fleet@LR5
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFR {#app:desc-fleet-lfr}

*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleet-lfr, results = knitr_results, echo = knitr_echo}
fleet@LFR
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Rmaxlen {#app:desc-fleet-rmaxlen}

*The retention of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleet-rmaxlen, results = knitr_results, echo = knitr_echo}
fleet@Rmaxlen
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### DR {#app:desc-fleet-dr}

*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction*


```{r desc-fleet-dr, results = knitr_results, echo = knitr_echo}
fleet@DR <- c(0, 0)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CurrentYr {#app:desc-fleet-currentyr}

*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*


```{r desc-fleet-currentyr, results = knitr_results, echo = knitr_echo}
fleet@CurrentYr <- 2018
```
<!-- slot-chunk-end -->

## OBS SLOT DESCRIPTIONS {#app:desc-obs}

```{r warnings = FALSE}
obs <- DLMtool::Precise_Unbiased
```

<!-- slot-chunk-begin -->
### Name {#app:desc-obs-name}

*The name of the observation model object. Single value. Character string.*


```{r desc-obs-name, results = knitr_results, echo = knitr_echo}
obs@Name <- "BC Obs"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Cobs {#app:desc-obs}

*Log-normal catch observation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*

At least since 1996, observation error on catch should be very small. Setting this to 0.

TODO: does this affect historical build up because there was certainly much larger observation error on catch before 1996.

```{r desc-obs, results = knitr_results, echo = knitr_echo}
obs@Cobs <- c(0, 0)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Cbiascv {#app:desc-obs-cbiascv}

*Log-normal coefficient of variation controlling the sampling of bias in catch observations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers*

We will keep the at 0 because observation error on catch should be very small with 100% on board and dockside monitoring.

FIXME: what about the historical period?

```{r desc-obs-cbiascv, results = knitr_results, echo = knitr_echo}
obs@Cbiascv <- c(0, 0)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CAA_nsamp {#app:desc-obs-caa_nsamp}

*Number of catch-at-age observation per time step. Uniform distribution lower and upper bounds. Positive real numbers*

TODO: critical to get this right

```{r desc-obs-caa_nsamp, results = knitr_results, echo = knitr_echo}
obs@CAA_nsamp
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CAA_ESS {#app:desc-obs-caa_ess}

*Effective sample size (independent age draws) of the multinomial catch-at-age observation error model. Uniform distribution lower and upper bounds. Positive integers*

TODO: critical to get this right

```{r desc-obs-caa_ess, results = knitr_results, echo = knitr_echo}
obs@CAA_ESS
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CAL_nsamp {#app:desc-obs-cal_nsamp}

*Number of catch-at-length observation per time step. Uniform distribution lower and upper bounds. Positive integers*

TODO: critical to get this right

```{r desc-obs-cal_nsamp, results = knitr_results, echo = knitr_echo}
obs@CAL_nsamp
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CAL_ESS {#app:desc-obs-cal_ess}

*Effective sample size (independent length draws) of the multinomial catch-at-length observation error model. Uniform distribution lower and upper bounds. Positive integers*


```{r desc-obs-cal_ess, results = knitr_results, echo = knitr_echo}
obs@CAL_ESS
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Iobs {#app:desc-obs}

*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers*

```{r}
average_cv <- dplyr::filter(drex$survey_index, survey_abbrev == "SYN WCVI") %>%
  dplyr::pull(re) %>%
  mean() %>%
  round(2)
```
This will depend on whether we want to use one or more of the trawl surveys or commercial CPUE as the index. For now I will assume that we will work with one of the trawl surveys. In that case, the CV on the index is quite large for this species. For example, the best sampling is probably on the West Coast of Haidai Gwaii, and there the average CV is `r average_cv`. Let's use that for now but we could add some uncertainty around this. FIXME

```{r desc-obs, results = knitr_results, echo = knitr_echo}
obs@Iobs <- c(average_cv, average_cv)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Ibiascv {#app:desc-obs-ibiascv}

*Log-normal coefficient of variation controlling error in observations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-ibiascv, results = knitr_results, echo = knitr_echo}
obs@Ibiascv <- c(0, 0)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Btobs {#app:desc-obs}

*Log-normal coefficient of variation controlling error in observations of current stock biomass among years. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs, results = knitr_results, echo = knitr_echo}
obs@Btobs <- obs@Iobs
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Btbiascv {#app:desc-obs-btbiascv}

*Uniform-log bounds for sampling persistent bias in current stock biomass. Uniform-log distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-btbiascv, results = knitr_results, echo = knitr_echo}
obs@Btbiascv <- obs@Ibiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### beta {#app:desc-obs-beta}

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers*

We probably don't have a lot to go on here so let's allow for a wide range:

```{r desc-obs-beta, results = knitr_results, echo = knitr_echo}
obs@beta <- c(0.666, 1.500)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LenMbiascv {#app:desc-obs-lenmbiascv}

*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*

It is possible there is some persistent bias in estimates such as length at 50% maturity. Let's set this to a range from a little bit to a moderate amount:

```{r desc-obs-lenmbiascv, results = knitr_results, echo = knitr_echo}
obs@LenMbiascv <- c(0.05, 0.10)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Mbiascv {#app:desc-obs-mbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers*

We don't have good data to go on for natural mortality rate so let's allow for a fairly large range in persistent bias. As a reminder, we set M to be drawn from a uniform distribution between `r stock@M[[1]]` and `r stock@M[[2]]`.

```{r desc-obs-mbiascv, results = knitr_results, echo = knitr_echo}
obs@Mbiascv <- c(0.05, 0.20)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Kbiascv {#app:desc-obs-kbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers*

```{r desc-obs-kbiascv, results = knitr_results, echo = knitr_echo}
obs@Kbiascv <- c(0.05, 0.10)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### t0biascv {#app:desc-obs-t0biascv}

*Log-normal coefficient of variation for sampling persistent bias in observed t0. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-t0biascv, results = knitr_results, echo = knitr_echo}
obs@t0biascv <- c(0.05, 0.10)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Linfbiascv {#app:desc-obs-linfbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed maximum length. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-linfbiascv, results = knitr_results, echo = knitr_echo}
obs@Linfbiascv <- c(0.05, 0.10)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFCbiascv {#app:desc-obs-lfcbiascv}

*Log-normal coefficient of variation for sampling persistent bias in observed length at first capture. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-lfcbiascv, results = knitr_results, echo = knitr_echo}
obs@LFCbiascv <- c(0.05, 0.10)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFSbiascv {#app:desc-obs-lfsbiascv}

*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-lfsbiascv, results = knitr_results, echo = knitr_echo}
obs@LFSbiascv <- c(0.05, 0.10)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### FMSYbiascv {#app:desc-obs-fmsybiascv}

*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-fmsybiascv, results = knitr_results, echo = knitr_echo}
obs@FMSYbiascv <- c(0.05, 0.20)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### FMSY_Mbiascv {#app:desc-obs-fmsy_mbiascv}

*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-fmsy_mbiascv, results = knitr_results, echo = knitr_echo}
obs@FMSY_Mbiascv <- c(0.05, 0.20)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### BMSY_B0biascv {#app:desc-obs-bmsy_b0biascv}

*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-bmsy_b0biascv, results = knitr_results, echo = knitr_echo}
obs@BMSY_B0biascv <- c(0.05, 0.20)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Irefbiascv {#app:desc-obs-irefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-irefbiascv, results = knitr_results, echo = knitr_echo}
obs@Irefbiascv <- c(0.05, 0.20)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Brefbiascv {#app:desc-obs-brefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-brefbiascv, results = knitr_results, echo = knitr_echo}
obs@Brefbiascv <- c(0.05, 0.20)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Crefbiascv {#app:desc-obs-crefbiascv}

*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-crefbiascv, results = knitr_results, echo = knitr_echo}
obs@Crefbiascv <- c(0.05, 0.20)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Dbiascv {#app:desc-obs-dbiascv}

*Log-normal coefficient of variation for sampling persistent bias in stock depletion. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-dbiascv, results = knitr_results, echo = knitr_echo}
obs@Dbiascv <- c(0.1, 0.3)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Dobs {#app:desc-obs}

*Log-normal coefficient of variation controlling error in observations of stock depletion among years. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs, results = knitr_results, echo = knitr_echo}
obs@Dobs
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### hbiascv {#app:desc-obs-hbiascv}

*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-hbiascv, results = knitr_results, echo = knitr_echo}
obs@hbiascv <- 0.1
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Recbiascv {#app:desc-obs-recbiascv}

*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obs-recbiascv, results = knitr_results, echo = knitr_echo}
obs@Recbiascv <- c(0.05, 0.20)
```
<!-- slot-chunk-end -->

## IMP SLOT DESCRIPTIONS {#app:desc-imp}

```{r warnings = FALSE}
imp <- methods::new('Imp')
```

<!-- slot-chunk-begin -->
### Name {#app:desc-imp-name}

*The name of the Implementation error object. Single value. Character string.*


```{r desc-imp-name, results = knitr_results, echo = knitr_echo}
imp@Name <- "BC Implementation"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### TACFrac {#app:desc-imp-tacfrac}

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*


```{r desc-imp-tacfrac, results = knitr_results, echo = knitr_echo}
imp@TACFrac <- c(0.8, 1.0)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### TACSD {#app:desc-imp-tacsd}

*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r desc-imp-tacsd, results = knitr_results, echo = knitr_echo}
imp@TACSD <- c(0, 0)
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Output the OM

*Output the Operating model.*

```{r output-rex}
rex_om <- new('OM', stock, fleet, obs, imp)
saveRDS(rex_om, file = here::here("generated-data", "rex-om.rds"))

```
<!-- slot-chunk-end -->
