```{r message = FALSE}
library(DLMtool)
knitr_results <- TRUE
knitr_echo <- TRUE
```


## STOCK SLOT DESCRIPTIONS {#app:desc-stockrex-rex}

```{r warnings = FALSE}
stockrex <- methods::new('Stock')
```

<!-- slot-chunk-begin -->
### Name {#app:desc-stockrex-name-rex}

*The name of the Stock object. Single value. Character string*


```{r desc-stockrex-name-rex, results = knitr_results, echo = knitr_echo}
stockrex@Name <- "Rex Sole"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Common_Name {#app:desc-stockrex-common_name-rex}

*Common name of the species. Character string*


```{r desc-stockrex-common_name-rex, results = knitr_results, echo = knitr_echo}
stockrex@Common_Name <- "Rex Sole"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Species {#app:desc-stockrex-species-rex}

*Scientific name of the species. Genus and species name. Character string*


```{r desc-stockrex-species-rex, results = knitr_results, echo = knitr_echo}
stockrex@Species <- "Glyptocephalus zachirus"
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### maxage {#app:desc-stockrex-maxage-rex}

*The maximum age of individuals that is simulated (there is no plus group ). Single value. Positive integer*

From @turnock2005. This is the plus group value.

```{r desc-stockrex-maxage-rex, results = knitr_results, echo = knitr_echo}
stockrex@maxage <- 20
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### R0 {#app:desc-stockrex-r0-rex}

*The magnitude of unfished recruitment. Single value. Positive real number*

From @mcgilliard2017, Table 13, model 15.0.

```{r desc-stockrex-r0-rex, results = knitr_results, echo = knitr_echo}
stockrex@R0 <- exp(11.5683)
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### M {#app:desc-stockrex-m-rex}

*Natural mortality rate. Uniform distribution lower and upper bounds. Positive real number*

The value of $M=0.17$ is from @mcgilliard2017

```{r desc-stockrex-m-rex, results = knitr_results, echo = knitr_echo}
stockrex@M <- 0.17
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### M2 {#app:desc-stockrex-m2-rex}

*(Optional) Natural mortality rate at age. Vector of length maxage . Positive real number*


```{r desc-stockrex-m2-rex, results = knitr_results, echo = knitr_echo}
stockrex@M2
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Mexp {#app:desc-stockrex-mexp-rex}

*Exponent of the Lorenzen function assuming an inverse relationship between M and weight. Uniform distribution lower and upper bounds. Real numbers <= 0.*


```{r desc-stockrex-mexp-rex, results = knitr_results, echo = knitr_echo}
stockrex@Mexp
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Msd {#app:desc-stockrex-msd-rex}

*Inter-annual variability in natural mortality rate expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-stockrex-msd-rex, results = knitr_results, echo = knitr_echo}
stockrex@Msd
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### h {#app:desc-stockrex-h-rex}

*Steepness of the stockrex recruit relationship. Uniform distribution lower and upper bounds. Values from 1/5 to 1*


```{r desc-stockrex-h-rex, results = knitr_results, echo = knitr_echo}
stockrex@h
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### SRrel {#app:desc-stockrex-srrel-rex}

*Type of stockrex-recruit relationship. Single value, switch (1) Beverton-Holt (2) Ricker. Integer*


```{r desc-stockrex-srrel-rex, results = knitr_results, echo = knitr_echo}
stockrex@SRrel
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Perr {#app:desc-stockrex-perr-rex}

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-stockrex-perr-rex, results = knitr_results, echo = knitr_echo}
stockrex@Perr
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### AC {#app:desc-stockrex-ac-rex}

*Autocorrelation in recruitment deviations rec(t)=AC*rec(t-1)+(1-AC)*sigma(t). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-stockrex-ac-rex, results = knitr_results, echo = knitr_echo}
stockrex@AC
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Period {#app:desc-stockrex-period-rex}

*(Optional) Period for cyclical recruitment pattern in years. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-stockrex-period-rex, results = knitr_results, echo = knitr_echo}
stockrex@Period
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Amplitude {#app:desc-stockrex-amplitude-rex}

*(Optional) Amplitude in deviation from long-term average recruitment during recruitment cycle (eg a range from 0 to 1 means recruitment decreases or increases by up to 100% each cycle). Uniform distribution lower and upper bounds. 0 < Amplitude < 1*


```{r desc-stockrex-amplitude-rex, results = knitr_results, echo = knitr_echo}
stockrex@Amplitude
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Linf {#app:desc-stockrex-linf-rex}

*Maximum length. Uniform distribution lower and upper bounds. Positive real numbers*

Females only, from @turnock2005, table 4.12
Male = 39.5

```{r desc-stockrex-linf-rex, results = knitr_results, echo = knitr_echo}
stockrex@Linf <- 44.9
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### K {#app:desc-stockrex-k-rex}

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds. Positive real numbers*

Females only, from @turnock2005, table 4.12
Male = 0.38

```{r desc-stockrex-k-rex, results = knitr_results, echo = knitr_echo}
stockrex@K <- 0.31
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### t0 {#app:desc-stockrex-t0-rex}

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds. Non-positive real numbers*

Females only, from @turnock2005, table 4.12
Male = 0.79
t0 was not reported in @mcgilliard2015, so @turnock2005 was used for all values t0, K, and Linf

```{r desc-stockrex-t0-rex, results = knitr_results, echo = knitr_echo}
stockrex@t0 <- 0.69
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LenCV {#app:desc-stockrex-lencv-rex}

*Coefficient of variation of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-stockrex-lencv-rex, results = knitr_results, echo = knitr_echo}
stockrex@LenCV
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Ksd {#app:desc-stockrex-ksd-rex}

*Inter-annual variability in growth parameter k expressed as coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-stockrex-ksd-rex, results = knitr_results, echo = knitr_echo}
stockrex@Ksd
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Linfsd {#app:desc-stockrex-linfsd-rex}

*Inter-annual variability in maximum length expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-stockrex-linfsd-rex, results = knitr_results, echo = knitr_echo}
stockrex@Linfsd
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L50 {#app:desc-stockrex-l50-rex}

*Length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*

From @abookire2006, Table 3, in cm.

```{r desc-stockrex-l50-rex, results = knitr_results, echo = knitr_echo}
stockrex@L50 <- 35.17
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L50_95 {#app:desc-stockrex-l50_95-rex}

*Length increment from 50 percent to 95 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*

From @abookire2006, Table 3, in cm.

```{r desc-stockrex-l50_95-rex, results = knitr_results, echo = knitr_echo}
stockrex@L50_95 <- 35.97
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### D {#app:desc-stockrex-d-rex}

*Current level of stockrex depletion SSB(current)/SSB(unfished). Uniform distribution lower and upper bounds. Fraction*


```{r desc-stockrex-d-rex, results = knitr_results, echo = knitr_echo}
stockrex@D
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### a {#app:desc-stockrex-a-rex}

*Length-weight parameter alpha. Single value. Positive real number*

From @mcgilliard2015, female only.
Male = 2.18e-06

```{r desc-stockrex-a-rex, results = knitr_results, echo = knitr_echo}
stockrex@a <- 1.35e-06
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### b {#app:desc-stockrex-b-rex}

*Length-weight parameter beta. Single value. Positive real number*

From @mcgilliard2015, female only.
Male = 3.30571

```{r desc-stockrex-b-rex, results = knitr_results, echo = knitr_echo}
stockrex@b <- 3.44963
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Size_area_1 {#app:desc-stockrex-size_area_1-rex}

*The size of area 1 relative to the total area (area 1 + area 2). Set to 0.5 to approximate single area model. Uniform distribution lower and upper bounds. Positive real numbers.*


```{r desc-stockrex-size_area_1-rex, results = knitr_results, echo = knitr_echo}
stockrex@Size_area_1
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Frac_area_1 {#app:desc-stockrex-frac_area_1-rex}

*The fraction of the unfished biomass in area 1 relative to the total area (area 1 + area 2). Uniform distribution lower and upper bounds. Positive real numbers.*


```{r desc-stockrex-frac_area_1-rex, results = knitr_results, echo = knitr_echo}
stockrex@Frac_area_1
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Prob_staying {#app:desc-stockrex-prob_staying-rex}

*The probability of inviduals in area 1 remaining in area 1 over the course of one year. Uniform distribution lower and upper bounds. Positive fraction.*


```{r desc-stockrex-prob_staying-rex, results = knitr_results, echo = knitr_echo}
stockrex@Prob_staying
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Fdisc {#app:desc-stockrex-fdisc-rex}

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-stockrex-fdisc-rex, results = knitr_results, echo = knitr_echo}
stockrex@Fdisc
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Source {#app:desc-stockrex-source-rex}

*A reference to a website or article from which parameters were taken to define the stockrex object. Single value. Character string.*


```{r desc-stockrex-source-rex, results = knitr_results, echo = knitr_echo}
stockrex@Source
```
<!-- slot-chunk-end -->

## FLEET SLOT DESCRIPTIONS {#app:desc-fleetrex-rex}

```{r warnings = FALSE}
Fleet <- DLMtool::Generic_Fleet # TODO: temporary
```

<!-- slot-chunk-begin -->
### Name {#app:desc-fleetrex-name-rex}

*Name of the Fleet object. Single value. Character string.*


```{r desc-fleetrex-name-rex, results = knitr_results, echo = knitr_echo}
fleetrex@Name
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### nyears {#app:desc-fleetrex-nyears-rex}

*The number of years for the historical spool-up simulation. Single value. Positive integer*


```{r desc-fleetrex-nyears-rex, results = knitr_results, echo = knitr_echo}
fleetrex@nyears
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Spat_targ {#app:desc-fleetrex-spat_targ-rex}

*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^Spat_targ. Uniform distribution lower and upper bounds. Real numbers*


```{r desc-fleetrex-spat_targ-rex, results = knitr_results, echo = knitr_echo}
fleetrex@Spat_targ
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### EffYears {#app:desc-fleetrex-effyears-rex}

*Years representing join-points (vertices) of time-varying effort. Vector. Non-negative real numbers*


```{r desc-fleetrex-effyears-rex, results = knitr_results, echo = knitr_echo}
fleetrex@EffYears
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### EffLower {#app:desc-fleetrex-efflower-rex}

*Lower bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*


```{r desc-fleetrex-efflower-rex, results = knitr_results, echo = knitr_echo}
fleetrex@EffLower
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### EffUpper {#app:desc-fleetrex-effupper-rex}

*Upper bound on relative effort corresponding to EffYears. Vector. Non-negative real numbers*


```{r desc-fleetrex-effupper-rex, results = knitr_results, echo = knitr_echo}
fleetrex@EffUpper
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Esd {#app:desc-fleetrex-esd-rex}

*Additional inter-annual variability in fishing mortality rate. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleetrex-esd-rex, results = knitr_results, echo = knitr_echo}
fleetrex@Esd
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### qinc {#app:desc-fleetrex-qinc-rex}

*Average percentage change in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleetrex-qinc-rex, results = knitr_results, echo = knitr_echo}
fleetrex@qinc
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### qcv {#app:desc-fleetrex-qcv-rex}

*Inter-annual variability in fishing efficiency (applicable only to forward projection and input controls). Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleetrex-qcv-rex, results = knitr_results, echo = knitr_echo}
fleetrex@qcv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L5 {#app:desc-fleetrex-l5-rex}

*Shortest length corresponding to 5 percent vulnerability. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-fleetrex-l5-rex, results = knitr_results, echo = knitr_echo}
fleetrex@L5
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFS {#app:desc-fleetrex-lfs-rex}

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-fleetrex-lfs-rex, results = knitr_results, echo = knitr_echo}
fleetrex@LFS
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Vmaxlen {#app:desc-fleetrex-vmaxlen-rex}

*The vulnerability of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Fraction*


```{r desc-fleetrex-vmaxlen-rex, results = knitr_results, echo = knitr_echo}
fleetrex@Vmaxlen
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### isRel {#app:desc-fleetrex-isrel-rex}

*Selectivity parameters in units of size-of-maturity (or absolute eg cm). Single value. Boolean.*


```{r desc-fleetrex-isrel-rex, results = knitr_results, echo = knitr_echo}
fleetrex@isRel
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LR5 {#app:desc-fleetrex-lr5-rex}

*Shortest length corresponding ot 5 percent retention. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleetrex-lr5-rex, results = knitr_results, echo = knitr_echo}
fleetrex@LR5
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFR {#app:desc-fleetrex-lfr-rex}

*Shortest length that is fully retained. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleetrex-lfr-rex, results = knitr_results, echo = knitr_echo}
fleetrex@LFR
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Rmaxlen {#app:desc-fleetrex-rmaxlen-rex}

*The retention of fish at `Stock@Linf` . Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-fleetrex-rmaxlen-rex, results = knitr_results, echo = knitr_echo}
fleetrex@Rmaxlen
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### DR {#app:desc-fleetrex-dr-rex}

*Discard rate - the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction*


```{r desc-fleetrex-dr-rex, results = knitr_results, echo = knitr_echo}
fleetrex@DR
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### SelYears {#app:desc-fleetrex-selyears-rex}

*(Optional) Years representing join-points (vertices) at which historical selectivity pattern changes. Vector. Positive real numbers*


```{r desc-fleetrex-selyears-rex, results = knitr_results, echo = knitr_echo}
fleetrex@SelYears
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### AbsSelYears {#app:desc-fleetrex-absselyears-rex}

*(Optional) Calendar years corresponding with SelYears (eg 1951, rather than 1), used for plotting only. Vector (of same length as SelYears). Positive real numbers*


```{r desc-fleetrex-absselyears-rex, results = knitr_results, echo = knitr_echo}
fleetrex@AbsSelYears
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L5Lower {#app:desc-fleetrex-l5lower-rex}

*(Optional) Lower bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r desc-fleetrex-l5lower-rex, results = knitr_results, echo = knitr_echo}
fleetrex@L5Lower
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### L5Upper {#app:desc-fleetrex-l5upper-rex}

*(Optional) Upper bound of L5 (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r desc-fleetrex-l5upper-rex, results = knitr_results, echo = knitr_echo}
fleetrex@L5Upper
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFSLower {#app:desc-fleetrex-lfslower-rex}

*(Optional) Lower bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r desc-fleetrex-lfslower-rex, results = knitr_results, echo = knitr_echo}
fleetrex@LFSLower
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFSUpper {#app:desc-fleetrex-lfsupper-rex}

*(Optional) Upper bound of LFS (use ChooseSelect function to set these). Vector. Non-negative real numbers*


```{r desc-fleetrex-lfsupper-rex, results = knitr_results, echo = knitr_echo}
fleetrex@LFSUpper
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### VmaxLower {#app:desc-fleetrex-vmaxlower-rex}

*(Optional) Lower bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*


```{r desc-fleetrex-vmaxlower-rex, results = knitr_results, echo = knitr_echo}
fleetrex@VmaxLower
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### VmaxUpper {#app:desc-fleetrex-vmaxupper-rex}

*(Optional) Upper bound of Vmaxlen (use ChooseSelect function to set these). Vector. Fraction*


```{r desc-fleetrex-vmaxupper-rex, results = knitr_results, echo = knitr_echo}
fleetrex@VmaxUpper
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CurrentYr {#app:desc-fleetrex-currentyr-rex}

*The current calendar year (final year) of the historical simulations (eg 2011). Single value. Positive integer.*


```{r desc-fleetrex-currentyr-rex, results = knitr_results, echo = knitr_echo}
fleetrex@CurrentYr
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### MPA {#app:desc-fleetrex-mpa-rex}

*(Optional) Matrix specifying spatial closures for historical years.*


```{r desc-fleetrex-mpa-rex, results = knitr_results, echo = knitr_echo}
fleetrex@MPA
```
<!-- slot-chunk-end -->

## OBS SLOT DESCRIPTIONS {#app:desc-obsrex-rex}

```{r warnings = FALSE}
obsrex <- methods::new('Obs')
```

<!-- slot-chunk-begin -->
### Name {#app:desc-obsrex-name-rex}

*The name of the obsrexervation model object. Single value. Character string.*


```{r desc-obsrex-name-rex, results = knitr_results, echo = knitr_echo}
obsrex@Name
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Cobsrex {#app:desc-obsrex-cobsrex-rex}

*Log-normal catch obsrexervation error expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-obsrex-cobsrex-rex, results = knitr_results, echo = knitr_echo}
obsrex@Cobsrex
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Cbiascv {#app:desc-obsrex-cbiascv-rex}

*Log-normal coefficient of variation controlling the sampling of bias in catch obsrexervations for each simulation. Uniform distribution lower and upper bounds. Non-negative real numbers*


```{r desc-obsrex-cbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Cbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CAA_nsamp {#app:desc-obsrex-caa_nsamp-rex}

*Number of catch-at-age obsrexervation per time step. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-caa_nsamp-rex, results = knitr_results, echo = knitr_echo}
obsrex@CAA_nsamp
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CAA_ESS {#app:desc-obsrex-caa_ess-rex}

*Effective sample size (independent age draws) of the multinomial catch-at-age obsrexervation error model. Uniform distribution lower and upper bounds. Positive integers*


```{r desc-obsrex-caa_ess-rex, results = knitr_results, echo = knitr_echo}
obsrex@CAA_ESS
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CAL_nsamp {#app:desc-obsrex-cal_nsamp-rex}

*Number of catch-at-length obsrexervation per time step. Uniform distribution lower and upper bounds. Positive integers*


```{r desc-obsrex-cal_nsamp-rex, results = knitr_results, echo = knitr_echo}
obsrex@CAL_nsamp
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### CAL_ESS {#app:desc-obsrex-cal_ess-rex}

*Effective sample size (independent length draws) of the multinomial catch-at-length obsrexervation error model. Uniform distribution lower and upper bounds. Positive integers*


```{r desc-obsrex-cal_ess-rex, results = knitr_results, echo = knitr_echo}
obsrex@CAL_ESS
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Iobsrex {#app:desc-obsrex-iobsrex-rex}

*Observation error in the relative abundance indices expressed as a coefficient of variation. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-iobsrex-rex, results = knitr_results, echo = knitr_echo}
obsrex@Iobsrex
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Ibiascv {#app:desc-obsrex-ibiascv-rex}

*Log-normal coefficient of variation controlling error in obsrexervations of relative abundance index. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-ibiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Ibiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Btobsrex {#app:desc-obsrex-btobsrex-rex}

*Log-normal coefficient of variation controlling error in obsrexervations of current stockrex biomass among years. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-btobsrex-rex, results = knitr_results, echo = knitr_echo}
obsrex@Btobsrex
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Btbiascv {#app:desc-obsrex-btbiascv-rex}

*Uniform-log bounds for sampling persistent bias in current stockrex biomass. Uniform-log distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-btbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Btbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### beta {#app:desc-obsrex-beta-rex}

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases slower than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-beta-rex, results = knitr_results, echo = knitr_echo}
obsrex@beta
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LenMbiascv {#app:desc-obsrex-lenmbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in length at 50 percent maturity. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-lenmbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@LenMbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Mbiascv {#app:desc-obsrex-mbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in obsrexerved natural mortality rate. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-mbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Mbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Kbiascv {#app:desc-obsrex-kbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in obsrexerved growth parameter K. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-kbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Kbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### t0biascv {#app:desc-obsrex-t0biascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in obsrexerved t0. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-t0biascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@t0biascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Linfbiascv {#app:desc-obsrex-linfbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in obsrexerved maximum length. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-linfbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Linfbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFCbiascv {#app:desc-obsrex-lfcbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in obsrexerved length at first capture. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-lfcbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@LFCbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### LFSbiascv {#app:desc-obsrex-lfsbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in length-at-full selection. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-lfsbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@LFSbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### FMSYbiascv {#app:desc-obsrex-fmsybiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in FMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-fmsybiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@FMSYbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### FMSY_Mbiascv {#app:desc-obsrex-fmsy_mbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in FMSY/M. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-fmsy_mbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@FMSY_Mbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### BMSY_B0biascv {#app:desc-obsrex-bmsy_b0biascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in BMSY relative to unfished. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-bmsy_b0biascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@BMSY_B0biascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Irefbiascv {#app:desc-obsrex-irefbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-irefbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Irefbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Brefbiascv {#app:desc-obsrex-brefbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in BMSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-brefbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Brefbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Crefbiascv {#app:desc-obsrex-crefbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in MSY. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-crefbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Crefbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Dbiascv {#app:desc-obsrex-dbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in stockrex depletion. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-dbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Dbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Dobsrex {#app:desc-obsrex-dobsrex-rex}

*Log-normal coefficient of variation controlling error in obsrexervations of stockrex depletion among years. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-dobsrex-rex, results = knitr_results, echo = knitr_echo}
obsrex@Dobsrex
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### hbiascv {#app:desc-obsrex-hbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in steepness. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-hbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@hbiascv
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### Recbiascv {#app:desc-obsrex-recbiascv-rex}

*Log-normal coefficient of variation for sampling persistent bias in recent recruitment strength. Uniform distribution lower and upper bounds. Positive real numbers*


```{r desc-obsrex-recbiascv-rex, results = knitr_results, echo = knitr_echo}
obsrex@Recbiascv
```
<!-- slot-chunk-end -->

## IMP SLOT DESCRIPTIONS {#app:desc-imprex-rex}

```{r warnings = FALSE}
imprex <- methods::new('Imp')
```

<!-- slot-chunk-begin -->
### Name {#app:desc-imprex-name-rex}

*The name of the Implementation error object. Single value. Character string.*


```{r desc-imprex-name-rex, results = knitr_results, echo = knitr_echo}
imprex@Name
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### TACFrac {#app:desc-imprex-tacfrac-rex}

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds. Positive real number.*


```{r desc-imprex-tacfrac-rex, results = knitr_results, echo = knitr_echo}
imprex@TACFrac
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### TACSD {#app:desc-imprex-tacsd-rex}

*Log-normal coefficient of variation in the fraction of Total Allowable Catch (TAC) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r desc-imprex-tacsd-rex, results = knitr_results, echo = knitr_echo}
imprex@TACSD
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### TAEFrac {#app:desc-imprex-taefrac-rex}

*Mean fraction of TAE taken. Uniform distribution lower and upper bounds. Positive real number.*


```{r desc-imprex-taefrac-rex, results = knitr_results, echo = knitr_echo}
imprex@TAEFrac
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### TAESD {#app:desc-imprex-taesd-rex}

*Log-normal coefficient of variation in the fraction of Total Allowable Effort (TAE) taken. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r desc-imprex-taesd-rex, results = knitr_results, echo = knitr_echo}
imprex@TAESD
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### SizeLimFrac {#app:desc-imprex-sizelimfrac-rex}

*The real minimum size that is retained expressed as a fraction of the size. Uniform distribution lower and upper bounds. Positive real number.*


```{r desc-imprex-sizelimfrac-rex, results = knitr_results, echo = knitr_echo}
imprex@SizeLimFrac
```
<!-- slot-chunk-end -->
<!-- slot-chunk-begin -->
### SizeLimSD {#app:desc-imprex-sizelimsd-rex}

*Log-normal coefficient of variation controlling mismatch between a minimum size limit and the real minimum size retained. Uniform distribution lower and upper bounds. Non-negative real numbers.*


```{r desc-imprex-sizelimsd-rex, results = knitr_results, echo = knitr_echo}
imprex@SizeLimSD
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Output the OM

*Output the Operating model.*

```{r output-rex}
rex_om <- new('OM', stockrex, fleetrex, obsrex, imprex)
saveRDS(rex_om, file = here::here("generated-data", "rex-om.rds"))

```
<!-- slot-chunk-end -->
