\newpage

# SHORTRAKER: MANAGEMENT PROCEDURE SPECIFICATIONS {#app:desc-mp-sr}

Use the management procedures that passed the screening test

```{r}
mpsr <- c("AvC", 
          "CC2", 
          "CC3",
          "DD", 
          "DD4010", 
          "GB_CC", 
          "GB_target",  
          "Islope1", 
          "Islope2",
          "Islope4", 
          "IT5", 
          "ITM", 
          "LstepCC2",
          "LstepCC3", 
          "LstepCC4", 
          "Ltarget1", 
          "Ltarget2", 
          "Ltarget3",
          "SBT2", 
          "SP_4010", 
          "SP_MSY")

#Group MPs into similar types
mpsr_group <- list()
mpsr_group[[1]] <- mpsr[1:3]
mpsr_group[[2]] <- mpsr[4:5]
mpsr_group[[3]] <- mpsr[6:7]
mpsr_group[[4]] <- mpsr[8:10]
mpsr_group[[5]] <- mpsr[c(11:12,19)]
mpsr_group[[6]] <- mpsr[13:15]
mpsr_group[[7]] <- mpsr[16:18]
mpsr_group[[8]] <- mpsr[20:21]

mptypenames <- c("Av Catch", "Delay Difference","Catch Target", "Index Slope", "Index Target","Stepwise Constant Catch", "Length Target","Surplus Production")

```


```{r, results='asis'}
csasdown::csas_table(MPtype(mpsr))
```

# Shortraker: RESULTS 

## Constructing the operating model

Get the operating model. 


```{r echo = TRUE}
omsr <- new('OM', stock, fleet, obs, imp)

omsr@nsim <- 200

saveRDS(omsr, file = here::here("generated-data", "shortraker-om.rds"))
```

Run the historical part of the MSE. 

One thing we can do to check our operating model calibration is check some random samples from the historical simulation against our observed data. For example, here are 11 samples from the simulated historical catch timeseries compared to the observed (reconstructed/corrected) catch timeseries.

```{r, fig.asp=0.8}
omsr@nsim <- 50
short_historical <- runMSE(omsr, Hist = TRUE, parallel=TRUE, ntrials=1000)
omsr@nsim <- 200

## names(short_historical@TSdata)
## dim(short_historical@TSdata$Catch)

real_catch <- read.csv(here::here("report/data/shortraker-corrected-catch.csv"))
real_catch <- mutate(real_catch, synthetic = ifelse(Year >= 1990 & Year <= 1995, Predicted.catch, Observed.catch))

all_years <- data.frame(Year = (2018 - fleet@nyears):2018)
real_catch <- dplyr::left_join(all_years, real_catch)

set.seed(1567)
catch <- short_historical@TSdata$Catch %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 11)) %>%
  transmute(sample_id = Var1, year = Var2 + min(real_catch$Year) - 1,
    catch = value, type = "Simulated") %>%
  bind_rows(data.frame(sample_id = 0, year = real_catch$Year,
    catch = real_catch$synthetic, type = "Observed", stringsAsFactors = FALSE))

catch %>%
  filter(!is.na(catch)) %>%
  group_by(sample_id) %>%
  mutate(catch = catch/max(catch)) %>%
  ggplot(aes(year, catch, colour = type)) +
  geom_line() +
  facet_wrap(~sample_id) +
  ylab("Historical catch") +
  xlab("Year")

short_historical@TSdata$B %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 12)) %>%
  ggplot(aes(Var2, value)) +
  geom_line() +
  facet_wrap(~Var1, scales = "free_y") +
  ylab("Simulated historical biomass") +
  xlab("Year")

```


Now run the closed loop simulation with the MPs above.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "shortraker-mse.rds")
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  shortraker_mse <- runMSE(OM = omsr, MPs = mpsr, parallel = TRUE, ntrials=1000)
  saveRDS(shortraker_mse, file = file_name)
} else {
  shortraker_mse <- readRDS(file_name)
}
```

Check convergence. This is to test whether enough simulations have been run ... does the order of the MPs change across iterations? If so, increase the number of iterations.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
DLMtool::Converge(shortraker_mse)
```

Seems to be okay.
*FIXME: Can't read the y axis labels*

Now look to see if we have redundant MPs by plotting the range of catches across replicates for a subset of years.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
shortraker_mse_C <- shortraker_mse@C

nSim <- omsr@nsim
nYear <- ncol(shortraker_mse_C[,1,]) 
nMP <- length(mpsr)
dimnames(shortraker_mse_C) <- list(1:nSim, mpsr, 1:nYear)

#convert to data frame
z1 <- apply(shortraker_mse_C, 3L, c)
z2 <- expand.grid(dimnames(shortraker_mse_C)[1:2])
mp_catch_sr <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "Catch"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch from similar MPs for a subset of years
for(i in seq_along(mptypenames))
{
  mpgroup <- mpsr_group[[i]]
  ggcatch <- mp_catch_sr %>% 
    filter(MP %in% mpgroup) %>% 
    filter(Year %in% c(1,10,20,30,40,50)) %>%
    ggplot(aes(x=as.factor(Year),y=Catch,fill=MP))+
    geom_boxplot()+
    ggtitle(mptypenames[i]) + xlab("Year") + ylab("Catch")
  print(ggcatch)
} 

```

It seems as if we have some redundancy among similar MPs based on the catch. Before removing MPs check biomass as well.


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
shortraker_mse_SSB <- shortraker_mse@SSB

nSim <- omsr@nsim
nYear <- ncol(shortraker_mse_SSB[,1,]) 
nMP <- length(mpsr)
dimnames(shortraker_mse_SSB) <- list(1:nSim, mpsr, 1:nYear)

#convert to data frame
z1 <- apply(shortraker_mse_SSB, 3L, c)
z2 <- expand.grid(dimnames(shortraker_mse_SSB)[1:2])
mp_ssb_sr <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "SBiomass"=value) %>% 
  mutate(Year=as.numeric(Year))

#Make boxplots of catch from similar MPs for a subset of years
for(i in seq_along(mptypenames))
{
  mpgroup <- mpsr_group[[i]]
  ggssb <- mp_ssb_sr %>% 
    filter(MP %in% mpgroup) %>% 
    filter(Year %in% c(1,10,20,30,40,50)) %>%
    ggplot(aes(x=as.factor(Year),y=SBiomass,fill=MP))+
    geom_boxplot()+
    ggtitle(mptypenames[i])+ xlab("Year")+ ylab("Spawning Biomass")
  print(ggssb)
} 

```


We can remove some MPs to make comparison of results easier. Here is the shortened list.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
mpsr_short <- c("AvC", 
          "DD", 
          "GB_CC", 
          "Islope1", 
          "IT5", 
          "LstepCC2",
          "Ltarget1", 
          "SP_MSY")
```

```{r, results='asis'}
csasdown::csas_table(MPtype(mpsr_short))
```

Rather than subsetting all the results, run the mse again on the shorter set. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "shortraker-mse-short.rds")
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  shortraker_mse_short <- runMSE(OM = omsr, MPs = mpsr_short, parallel = TRUE, ntrials=1000)
  saveRDS(shortraker_mse_short, file = file_name)
} else {
  shortraker_mse_short <- readRDS(file_name)
}
```

Check basline states for performance metrics from the OM. We want to see OM-simulated FMSY, BMSY and reference Yield.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
library(reshape2)
bmsy_sr <- shortraker_mse@OM$SSBMSY
USR_sr <- 0.8*bmsy_sr
LRP_sr <- 0.4*bmsy_sr
fmsy_sr <- shortraker_mse@OM$FMSY
refY_sr <- shortraker_mse@OM$RefY

baseline_names <- c("FMSY", "BMSY", "USR=0.8BMSY", "LRP=0.4BMSY","RefYield")

p <- baselines_sr <- as.data.frame(cbind(bmsy_sr,USR_sr,LRP_sr,refY_sr)) %>% 
  reshape2::melt() %>% 
  ggplot() + 
  geom_boxplot(aes(variable,value))+
  ylab("Simulated Value") +
  xlab("Baseline metric") +
  scale_x_discrete(labels=baseline_names[-1]) 
print(p)
  

```

Get median values

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
med_fmsy_sr <- median(shortraker_mse@OM$FMSY)
med_bmsy_sr <- median(shortraker_mse@OM$SSBMSY)
med_USR_sr <- median(0.8*bmsy_sr)
med_LRP_sr <- median(0.4*bmsy_sr)
med_refY_sr <- median(shortraker_mse@OM$RefY)

baseline_medians <- c(med_fmsy_sr, med_bmsy_sr,med_USR_sr,med_LRP_sr,med_refY_sr)
baseline_medians <- as.matrix(cbind(baseline_names, round(baseline_medians,3)))
colnames(baseline_medians) <- c("Metric", "Median")
knitr::kable(baseline_medians, format="markdown")

```


Now look at results from the shortlist of MPs together. Show biomass with median LRP and USR.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
shortraker_mse_SSB_short <- shortraker_mse_short@SSB
shortraker_mse_C_short <- shortraker_mse_short@C

nSim <- omsr@nsim
nYear <- ncol(shortraker_mse_SSB[,1,]) 
nMP <- length(mpsr_short)
dimnames(shortraker_mse_SSB_short) <- list(1:nSim, mpsr_short, 1:nYear)
dimnames(shortraker_mse_C_short) <- list(1:nSim, mpsr_short, 1:nYear)

#convert arrays to data frames
z1 <- apply(shortraker_mse_C_short, 3L, c)
z2 <- expand.grid(dimnames(shortraker_mse_C_short)[1:2])
mp_catch_sr_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "Catch"=value) %>% 
  mutate(Year=as.numeric(Year)) 

z1 <- apply(shortraker_mse_SSB_short, 3L, c)
z2 <- expand.grid(dimnames(shortraker_mse_SSB_short)[1:2])
mp_ssb_sr_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "SBiomass"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch and biomass from the short list of MPs 
ggcatch <- mp_catch_sr_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=Catch,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Catch")+ xlab("Year")+ ylab("Catch")
print(ggcatch)

ggssb2 <- mp_ssb_sr_short %>% 
filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=SBiomass,fill=MP))+
  geom_boxplot()+
  geom_hline(yintercept=med_USR_sr, linetype="dashed", color = "darkgreen")+
  geom_hline(yintercept=med_LRP_sr, linetype="dashed", color = "red")+
  ggtitle("Shortlist of MPs: Spawning Biomass")+ xlab("Year")+ ylab("Spawning Biomass")
print(ggssb2)

```

Look at Catch relative to RefY for each MP
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
nSim <- omsr@nsim
RefYield_sr <- data.frame("Sim"=1:nSim, "MP"=rep("RefY",nSim),"Year"=rep(1,nSim),  "Catch"=shortraker_mse_short@OM$RefY)

#Make a new object so we don't accidentally keep appending to mp_catch_sr_short
mp_catch_sr_short2 <- rbind(mp_catch_sr_short,RefYield_sr)

ggcatch <- mp_catch_sr_short2 %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=Catch,fill=MP))+
  geom_boxplot()+
  geom_hline(yintercept=med_refY_sr, linetype="dashed", color = "black")+
  ggtitle("Shortlist of MPs: Catch showing ref yield")+ xlab("Year")+ ylab("Catch") 
print(ggcatch)


```

Look at Catch/RefY for each MP
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
#For each MP and sim need to divide Catch by annual RefY
RefYield <- shortraker_mse_short@OM$RefY
RefYieldRep <- rep(RefYield,nMP*nYear)
mp_catch_sr_shortRel <- mp_catch_sr_short %>% 
  mutate("RefY"=RefYieldRep,"CatchRelRefY"=Catch/RefYieldRep)

ggcatch <- mp_catch_sr_shortRel %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=CatchRelRefY,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Catch relative to RefY")+ xlab("Year")+ ylab("Relative Catch")  
print(ggcatch)

```


Look at B/BMSY trajectories under each MP. 

<!--- Try Cowplot grid version, hard to read but could lay it out better

```{r}
shortraker_mse_BBMSY_short <- shortraker_mse_short@B_BMSY
dim(shortraker_mse_BBMSY_short) #dimensions of array are 1:nSim, 1:nMP, 1:nYear

#USR_sr

#Give names to the array so they can be used for plotting
dimnames(shortraker_mse_BBMSY_short) <- list(1:nSim, mpsr_short, 1:nYear)

gg <- list()
lapply(1:nMP, function(x){
 tmp <- shortraker_mse_BBMSY_short[,x,] %>% 
   reshape2::melt() 
   gg[[x]] <<- ggplot(tmp, aes(x=as.factor(Var2),y=value)) +
   geom_boxplot() +
   xlab("Year")+ ylab("B/BMSY") 
})
cowplot::plot_grid(plotlist=gg)

```
--->


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
shortraker_mse_BBMSY_short <- shortraker_mse_short@B_BMSY
dim(shortraker_mse_BBMSY_short) #dimensions of array are 1:nSim, 1:nMP, 1:nYear

#Give names to the array so they can be used for plotting
nSim <- omsr@nsim
nYear <- ncol(shortraker_mse_BBMSY_short[,1,]) #find global parameter for number of projection years
dimnames(shortraker_mse_BBMSY_short) <- list(c(1:nSim), mpsr_short, 1:nYear)

#convert to data frame and plot
z1 <- apply(shortraker_mse_BBMSY_short, 3L, c)
z2 <- expand.grid(dimnames(shortraker_mse_BBMSY_short)[1:2])
mp_bbmsy_sr_short <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "BBMSY"=value) %>% 
  mutate(Year=as.numeric(Year)) 

p <-  filter(mp_bbmsy_sr_short, MP %in% mpsr_short[1:4]) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY))+
  geom_boxplot()+
  facet_grid(rows=vars(MP)) + xlab("Year")+ ylab("B/BMSY") 
print(p)

p1 <-  filter(mp_bbmsy_sr_short, MP %in% mpsr_short[5:8]) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY))+
  geom_boxplot()+
  facet_grid(rows=vars(MP)) + xlab("Year")+ ylab("B/BMSY") 
print(p1)

```

Make the subsetted years version. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
ggcatch <- mp_bbmsy_sr_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: B/BMSY")+ xlab("Year")+ ylab("B/BMSY")  
print(ggcatch)

ggcatch <- mp_bbmsy_sr_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: B/BMSY")+ xlab("Year")+ ylab("B/BMSY")  
print(ggcatch)

```



Show probabilities of meeting performance metrics

```{r probability-table-abs-sr, fig.width = 9, fig.asp = 1, out.width = "4in"}
probs <- get_probs(shortraker_mse_short, PMlist = c("P40", "P80", "PNOF", "AAVY", "LTY"))
plot_probs(probs)
```



```{r}
Tplot(shortraker_mse_short)
Tplot2(shortraker_mse_short)
```



```{r}
summary(shortraker_mse_short)
```

Illustrating the built-in plotting functions:

```{r}
wormplot(shortraker_mse_short)
```

```{r}
Pplot(shortraker_mse_short)

```

```{r}
Pplot2(shortraker_mse_short, traj="quant", quants=c(0.2, 0.8))
```

```{r}
Kplot(shortraker_mse_short)
```

```{r}
Cplot(shortraker_mse_short)
```

And examine the output.

```{r}
 plot(shortraker_mse_short)
 oldpar <- par()
##DFO_hist(shortraker_mse_short)
par(mfrow = c(1, 1))
DFO_plot(shortraker_mse_short)
# DFO_plot2(shortraker_mse_short)
```

```{r, fig.asp=1, warning=FALSE}
DFO_proj(shortraker_mse_short)
#DFO_hist(shortraker_om)
# DFO_plot2(shortraker_mse_short)

# d <- DFO_plot2(shortraker_mse_short)
# ggplot(d, aes(B50/100, LTY/100, label = MPs, colour = Satisfice)) +
#   geom_vline(xintercept = 0.5, col = "grey50") +
#   geom_hline(yintercept = 0.5, col = "grey50") +
#   geom_text() + ggsidekick::theme_sleek() +
#   scale_colour_manual(values = c("grey60", "black")) +
#   guides(colour = FALSE) +
#   xlab(expression(Pr(B>0.5~B[MSY]))) +
#   ylab(expression(Pr(yield>0.5~yield~at~F[MSY]))) +
#   xlim(0, 1) + ylim(0, 1)
par(oldpar)
```

The following are some plots I was playing with a long time ago. We should wrap the useful ones into their own functions in our package.

```{r, fig.asp=1}
yend <- max(shortraker_mse_short@proyears)
ffmsy <- shortraker_mse_short@F_FMSY[,,yend]
bbmsy <- shortraker_mse_short@B_BMSY[,,yend]

ffmsy <- reshape2::melt(ffmsy) %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value)
bbmsy <- reshape2::melt(bbmsy) %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value)

d <- dplyr::inner_join(ffmsy, bbmsy)

nmp <- data.frame(mp = seq_along(shortraker_mse_short@MPs), mp_name = shortraker_mse_short@MPs)
# nmp$mp_name <- paste(1:nrow(n), nmp$mp_name)

d <- dplyr::left_join(d, nmp)

library(ggplot2)
ggplot(dplyr::filter(d, !mp_name %in% c("NFref")), aes(bbmsy, ffmsy)) +
  geom_vline(xintercept = c(0.4, 0.8), alpha = 0.2) +
  geom_hline(yintercept = 1, alpha = 0.2) +
  geom_density_2d(aes(colour = ..level..), bins = 5) +
  viridis::scale_colour_viridis() +
  ggsidekick::theme_sleek() +
  facet_wrap(~mp_name) +
  ylim(0, 3.5) + xlim(0, 3.5) +
  geom_point(alpha = 0.2) +
  labs(colour = "Prob. density", x = expression(B/B[MSY]),
    y = expression(F/F[MSY])) +
  guides(colour = FALSE)
#ggsave("analysis/shortraker-bbmsy-ffmsy-multi.pdf", width = 8, height = 8)
```

```{r, fig.asp=1.9, out.width = "4.8in", fig.width=7}
library(dplyr)
library(RColorBrewer)
nmp <- data.frame(mp = seq_along(pcod_mse_short@MPs), mp_name = pcod_mse_short@MPs)

ffmsy <- shortraker_mse_short@F_FMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value, year = Var3)
bbmsy <- shortraker_mse_short@B_BMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value, year = Var3)
cat <- shortraker_mse_short@C[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, catch = value, year = Var3)
biomass <- shortraker_mse_short@SSB[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, Biomass = value, year = Var3)
d <- dplyr::inner_join(ffmsy, bbmsy) 
d <- dplyr::inner_join(d, cat) 
d <- dplyr::inner_join(d, biomass)
d <- dplyr::left_join(d, nmp)
d <- reshape2::melt(d, id.vars = c("iter", "mp", "year", "mp_name"))
levels(d$variable) <- c(expression(F/F[MSY]), expression(B/B[MSY]), expression(Catch), expression(Biomass))

d_median <- d %>% group_by(mp_name, year, variable) %>%
  summarise(median_value = median(value)) %>%
  mutate(iter = NA)

fudge <- 3.5
d$over <- FALSE
d$over[d$value > fudge & d$variable %in% c(expression(F/F[MSY]), expression(B/B[MSY]))] <- TRUE
d$value[d$over] <- fudge
d_median$median_value[d_median$median_value > fudge] <- fudge

d_last <- dplyr::filter(d, year == max(year)) %>%
  select(-over, -year) %>%
  rename(last_value = value)
d <- inner_join(d, d_last)

cols <- brewer.pal(3, "RdBu")
cols[2] <- "grey80"

plot_timeseries <- function(dat, dat_median, title = "",
  ylim = c(0, fudge), cols, values, labels = TRUE, yaxis = TRUE) {
  g <- ggplot(dat, aes_string("year", "value", group = "iter")) +
    geom_line(aes_string(colour = "last_value"), alpha = 0.3) +
    facet_grid(mp_name~., labeller = label_parsed) +
    ggsidekick::theme_sleek() +
    scale_colour_gradientn(colours = cols,
      values = values) +
    geom_line(data = dat_median, aes_string("year", "median_value"),
      colour = "black", lwd = 1.5) +
    ylim(ylim[1], ylim[2]) +
    ggtitle(title) +
    guides(colour = FALSE) +
    ylab("Value") + xlab("Year")

  if (!labels)
    g <- g + theme(strip.background = element_blank(),
      strip.text.y = element_blank())

  if (!yaxis)
    g <- g + theme(axis.text.y = element_blank())
  g
}

cols <- brewer.pal(5, "RdBu")
cols <- c(cols[1], "grey50", cols[length(cols)])
set.seed(42)
# d_ <- filter(d, iter %in% sample(seq_len(max(d$iter)), 30))
d_ <- d

maxC <- d_ %>% 
  dplyr::filter(variable=="Catch") %>% 
  select(value) %>% 
  max()

maxB <- d_ %>% 
  dplyr::filter(variable=="Biomass") %>% 
  select(value) %>% 
  max()

#
mps <- unique(d_$mp_name)
# mps <- mps[-which(mps %in% c("CC4"))]
p1 <- plot_timeseries(filter(d_, variable == "B/B[MSY]", mp_name %in% mps),
  filter(d_median, variable == "B/B[MSY]", mp_name %in% mps), expression(B/B[MSY]),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, fudge)),
  labels = TRUE, ylim = c(0,fudge))
p2 <- plot_timeseries(filter(d_, variable == "F/F[MSY]", mp_name %in% mps),
  filter(d_median, variable == "F/F[MSY]", mp_name %in% mps), expression(F/F[MSY]),
  cols = cols, values = scales::rescale(c(fudge, 1.2, 0.8, 0)),
  labels = TRUE, ylim = c(0,fudge), yaxis = TRUE)
p3 <- plot_timeseries(filter(d_, variable == "Catch", mp_name %in% mps),
  filter(d_median, variable == "Catch", mp_name %in% mps), expression(Catch),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxC))
p4 <- plot_timeseries(filter(d_, variable == "Biomass", mp_name %in% mps),
  filter(d_median, variable == "Biomass", mp_name %in% mps), expression(Biomass),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxB))

gridExtra::grid.arrange(p4,p3,  p1, p2, ncol = 4)

# pdf("analysis/shortraker-bbmsy-ffmsy-ts-ex-all.pdf", width = 6, height = 6)
# gridExtra::grid.arrange(p1, p2, ncol = 2)
# dev.off()

#########3
ffmsy <- shortraker_mse_short@F_FMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value, year = Var3)
bbmsy <- shortraker_mse_short@B_BMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value, year = Var3)
d <- dplyr::inner_join(ffmsy, bbmsy)
d <- dplyr::left_join(d, nmp)
d <- reshape2::melt(d, id.vars = c("iter", "mp", "year", "mp_name"))
levels(d$variable) <- c(expression(F/F[MSY]), expression(B/B[MSY]))

d_sum <- d %>% group_by(mp_name, year, variable) %>%
  summarise(median_value = median(value),
    l = quantile(value, probs = 0.75),
    u = quantile(value, probs = 0.25),
    ll = quantile(value, probs = 0.95),
    uu = quantile(value, probs = 0.05))


# d_sum$median_value[d_sum$median_value > fudge] <- fudge
# d_sum$u[d_sum$u > fudge] <- fudge
# d_sum$l[d_sum$l > fudge] <- fudge

d <- inner_join(d, d_last)

d$last_value[d$last_value > fudge] <- fudge
# d$value[d$value > fudge] <- fudge


cols <- brewer.pal(5, "RdBu")
cols <- c(cols[1], "grey50", cols[length(cols)])
g <- ggplot(d_sum, aes_string("year", "median_value")) +
  facet_grid(mp_name~variable, labeller = label_parsed) +
  geom_ribbon(aes(ymin = ll, ymax = uu), fill = "grey90") +
  geom_ribbon(aes(ymin = l, ymax = u), fill = "grey70") +
  ggsidekick::theme_sleek() +
  geom_line(lwd = 1.5) +
  coord_cartesian(ylim = c(0, 4)) +
  guides(colour = FALSE) +
  xlim(25, 50) +
  geom_hline(yintercept = 1,
    col = "black", lty = 2) +
  ylab("Value") + xlab("Year")
  # geom_line(data = filter(d, iter %in% c(1:10)),
  #   aes(y = value, group = iter),
  #   alpha = 0.4, colour = "blue")
  # scale_colour_gradientn(colours = cols,
  #     values = c(0, 0.8, 1.2, 3))
  # viridis::scale_colour_viridis()
g
```

```{r, fig.asp=1.2}
voi_out <- DLMtool::VOI(shortraker_mse_short)
```
