\newpage

# PACIFIC COD: MANAGEMENT PROCEDURE SPECIFICATIONS {#app:desc-mp-sr}

Use the management procedures that passed the screening test

```{r}
mppc <- c("AvC", 
          "CC2", 
          "CC3",
          "DD", 
          "DD4010", 
          "GB_CC", 
          "GB_target",  
          "Islope1", 
          "Islope2",
          "Islope4", 
          "IT5", 
          "ITM", 
          "LstepCC2",
          "LstepCC3", 
          "LstepCC4", 
          "Ltarget1", 
          "Ltarget2", 
          "Ltarget3",
          "SBT2", 
          "SP_4010", 
          "SP_MSY")

#Group MPs into similar types
mppc_group <- list()
mppc_group[[1]] <- mppc[1:3]
mppc_group[[2]] <- mppc[4:5]
mppc_group[[3]] <- mppc[6:7]
mppc_group[[4]] <- mppc[8:10]
mppc_group[[5]] <- mppc[c(11:12,19)]
mppc_group[[6]] <- mppc[13:15]
mppc_group[[7]] <- mppc[16:18]
mppc_group[[8]] <- mppc[20:21]

mptypenames <- c("Av Catch", "Delay Difference","Catch Target", "Index Slope", "Index Target","Stepwise Constant Catch", "Length Target","Surplus Production")

```


```{r, results='asis'}
csasdown::csas_table(MPtype(mppc))
```

# PACIFIC COD: RESULTS 

## Constructing the operating model

Get the operating model. For Pacific Cod we are using the operating model fit using the SRA Scoping method fit to commercial CPUE and trawl survey indices.


```{r echo = TRUE}
#ompc <- new('OM', stock_pc, fleet_pc, obs_pc, imp_pc)

#Use OM that was made in sra-data-pcod.R 
ompc <- readRDS(here::here("sra/pcod_no_comps_om.rds"))
```

\newpage

Run the historical part of the MSE. For Pacific Cod, OM historical catch is set to the observed catch.

```{r, fig.asp=0.8}

DLMtool::setup(cpus = parallel::detectCores())
ompc@nsim <- 50
pcod_historical <- runMSE(ompc, Hist = TRUE, parallel = TRUE, ntrials=1000)
ompc@nsim <- 200
#saveRDS(ompc,file="C:/GitHub/gfmp/generated-data/ompc.RDS")


real_catchpc <- read.csv(here::here("report/data/pcod-corrected-catch.csv"))
real_catchpc <- mutate(real_catchpc, synthetic = real_catchpc$Observed.catch) #Don't use predicted catchpc for P cod

all_years <- data.frame(Year = (2018 - fleet_pc@nyears):2018)
real_catchpc <- dplyr::left_join(all_years, real_catchpc)

set.seed(193812)
catchpc <- pcod_historical@TSdata$Catch %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 11)) %>%
  transmute(sample_id = Var1, year = Var2 + min(real_catchpc$Year) - 1,
    catchpc = value, type = "Simulated") %>%
  bind_rows(data.frame(sample_id = 0, year = real_catchpc$Year,
    catchpc = real_catchpc$synthetic, type = "Observed", stringsAsFactors = FALSE))

catchpc %>%
  filter(!is.na(catchpc)) %>%
  group_by(sample_id) %>%
  mutate(catchpc = catchpc/max(catchpc)) %>%
  ggplot(aes(year, catchpc, colour = type)) +
  geom_line() +
  facet_wrap(~sample_id) +
  ylab("Historical catch") +
  xlab("Year")


```

\newpage

Look at the simulated biomass from a random set of replicates. Looks similar to the 2018 stock assessment [@forrest2019].

```{r, fig.asp=0.8}
pcod_historical@TSdata$B %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 12)) %>%
  ggplot(aes(Var2, value)) +
  geom_line() +
  facet_wrap(~Var1, scales = "free_y") +
  ylab("Simulated historical biomass") +
  xlab("Year")
```

\newpage

Now run the closed loop simulation with the MPs above.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "pcod-mse.rds")
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  pcod_mse <- runMSE(OM = ompc, MPs = mppc, parallel = TRUE, ntrials=1000)
  saveRDS(pcod_mse, file = file_name)
} else {
  pcod_mse <- readRDS(file_name)
}
```

Check convergence. This is to test whether enough simulations have been run ... does the order of the MPs change across iterations? If so, increase the number of iterations.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
DLMtool::Converge(pcod_mse)
```

Seems to be okay.

*FIXME: Can't read the y axis labels*

\newpage

Now look to see if we have redundant MPs by plotting the range of catches across replicates for a subset of years. Each graph shows results from MPs of a similar "type". The group type is shown in the title of each graph. Robyn made up the group types.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
pcod_mse_C <- pcod_mse@C

nSim <- ompc@nsim
nYear <- ncol(pcod_mse_C[,1,]) 
nMP <- length(pcod_mse@MPs)
dimnames(pcod_mse_C) <- list(1:nSim, pcod_mse@MPs, 1:nYear)

#convert to data frame
z1 <- apply(pcod_mse_C, 3L, c)
z2 <- expand.grid(dimnames(pcod_mse_C)[1:2])
mp_catch_pc <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "Catch"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch from similar MPs for a subset of years
for(i in seq_along(mptypenames))
{
  mpgroup <- mppc_group[[i]]
  ggcatch <- mp_catch_pc %>% 
    filter(MP %in% mpgroup) %>% 
    filter(Year %in% c(1,10,20,30,40,50)) %>%
    ggplot(aes(x=as.factor(Year),y=Catch,fill=MP))+
    geom_boxplot()+
    ggtitle(mptypenames[i]) + xlab("Year") + ylab("Catch")
  print(ggcatch)
} 

```


\newpage

It seems as if we have some redundancy among similar MPs based on the catch. Before removing MPs check biomass as well.


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
pcod_mse_SSB <- pcod_mse@SSB

nSim <- ompc@nsim
nYear <- ncol(pcod_mse_SSB[,1,]) 
nMP <- length(pcod_mse@MPs)
dimnames(pcod_mse_SSB) <- list(1:nSim, pcod_mse@MPs, 1:nYear)

#convert to data frame
z1 <- apply(pcod_mse_SSB, 3L, c)
z2 <- expand.grid(dimnames(pcod_mse_SSB)[1:2])
mp_ssb_pc <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "SBiomass"=value) %>% 
  mutate(Year=as.numeric(Year))

#Make boxplots of catch from similar MPs for a subset of years
for(i in seq_along(mptypenames))
{
  mpgroup <- mppc_group[[i]]
  ggssb <- mp_ssb_pc %>% 
    filter(MP %in% mpgroup) %>% 
    filter(Year %in% c(1,10,20,30,40,50)) %>%
    ggplot(aes(x=as.factor(Year),y=SBiomass,fill=MP))+
    geom_boxplot()+
    ggtitle(mptypenames[i])+ xlab("Year")+ ylab("Spawning Biomass")
  print(ggssb)
} 

```


\newpage

We can remove some MPs to make comparison of results easier. Here is the shortlist.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
mppc_short <- c("AvC",
                "CC2",
                "SBT2",
                "DD4010", 
                "GB_CC", 
                "Islope1", 
                "IT5",
                "ITM",
                "LstepCC2",
                "LstepCC3",
                "LstepCC4",
                "Ltarget1",
                "Ltarget2",
                "Ltarget3",
                "SP_MSY")
```

```{r, results='asis'}
csasdown::csas_table(MPtype(mppc_short))
```

Rather than subsetting all the results, run the mse again on the shorter set. 



```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "pcod-mse-short.rds")
# TODO: pcod_mse_short <- Sub(pcod_mse, MPs = mppc_short)
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  pcod_mse_short <- runMSE(OM = ompc, MPs = mppc_short, parallel = TRUE, ntrials=1000)
  saveRDS(pcod_mse_short, file = file_name)
} else {
  pcod_mse_short <- readRDS(file_name)
}
```


\newpage

Check baseline states for performance metrics from the OM. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
library(reshape2)
bmsy_pc <- pcod_mse@OM$SSBMSY
USR_pc <- 0.8*bmsy_pc
LRP_pc <- 0.4*bmsy_pc
fmsy_pc <- pcod_mse@OM$FMSY
refY_pc <- pcod_mse@OM$RefY

baseline_names <- c("FMSY", "BMSY", "USR=0.8BMSY", "LRP=0.4BMSY","RefYield")

p <- baselines_pc <- as.data.frame(cbind(bmsy_pc,USR_pc,LRP_pc,refY_pc)) %>% 
  reshape2::melt() %>% 
  ggplot() + 
  geom_boxplot(aes(variable,value))+
  ylab("Simulated Value (tonnes)") +
  xlab("Baseline metric") +
  scale_x_discrete(labels=baseline_names[-1]) 
print(p)

p <- baselines_pc <- as.data.frame(fmsy_pc) %>% 
  reshape2::melt() %>% 
  ggplot() + 
  geom_boxplot(aes(variable,value))+
  ylab("Simulated Value (tonnes)") +
  xlab("Baseline metric") +
  scale_x_discrete(labels=baseline_names[1]) 
print(p)
  

```


\newpage

Get median values of baseline metrics (reference points).

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
med_fmsy_pc <- median(pcod_mse@OM$FMSY)
med_bmsy_pc <- median(pcod_mse@OM$SSBMSY)
med_USR_pc <- median(0.8*bmsy_pc)
med_LRP_pc <- median(0.4*bmsy_pc)
med_refY_pc <- median(pcod_mse@OM$RefY)

baseline_medians <- c(med_fmsy_pc, med_bmsy_pc,med_USR_pc,med_LRP_pc,med_refY_pc)
baseline_medians <- as.matrix(cbind(baseline_names, round(baseline_medians,3)))
colnames(baseline_medians) <- c("Metric", "Median")
knitr::kable(baseline_medians, format="markdown")

```


\newpage

Now look at Catch and Biomass results from the shortlist of MPs together. Biomass plot shows median LRP and USR as dashed lines.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
pcod_mse_SSB_short <- pcod_mse_short@SSB
pcod_mse_C_short <- pcod_mse_short@C

nSim <- ompc@nsim
nYear <- ncol(pcod_mse_SSB[,1,]) 
nMP <- length(pcod_mse_short@MPs)
dimnames(pcod_mse_SSB_short) <- list(1:nSim, pcod_mse_short@MPs, 1:nYear)
dimnames(pcod_mse_C_short) <- list(1:nSim, pcod_mse_short@MPs, 1:nYear)

#convert arrays to data frames
z1 <- apply(pcod_mse_C_short, 3L, c)
z2 <- expand.grid(dimnames(pcod_mse_C_short)[1:2])
mp_catch_pc_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "Catch"=value) %>% 
  mutate(Year=as.numeric(Year)) 

z1 <- apply(pcod_mse_SSB_short, 3L, c)
z2 <- expand.grid(dimnames(pcod_mse_SSB_short)[1:2])
mp_ssb_pc_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "SBiomass"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch and biomass from the short list of MPs 
ggcatch <- mp_catch_pc_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=Catch,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Catch")+ xlab("Year")+ ylab("Catch")
print(ggcatch)

ggssb2 <- mp_ssb_pc_short %>% 
filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=SBiomass,fill=MP))+
  geom_boxplot()+
  geom_hline(yintercept=med_USR_pc, linetype="dashed", color = "darkgreen")+
  geom_hline(yintercept=med_LRP_pc, linetype="dashed", color = "red")+
  ggtitle("Shortlist of MPs: Spawning Biomass")+ xlab("Year")+ ylab("Spawning Biomass")
print(ggssb2)

```


\newpage

Look at Catch/RefY for each MP.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
#For each MP and sim need to divide Catch by annual RefY
RefYield <- pcod_mse_short@OM$RefY
RefYieldRep <- rep(RefYield,nMP*nYear)
mp_catch_pc_shortRel <- mp_catch_pc_short %>% 
  mutate("RefY"=RefYieldRep,"CatchRelRefY"=Catch/RefYieldRep)

ggcatch <- mp_catch_pc_shortRel %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=CatchRelRefY,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Catch relative to RefY")+ xlab("Year")+ ylab("Relative Catch")  
print(ggcatch)

```


RefY is a proxy for MSY. Not a very useful target for P cod. Perhaps we need to be able to set RefY to an agreed reference value. The OM thinks the stock is very productive (RefY >> average recent catches). 


\newpage

Look at projected fishing mortality.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
pcod_mse_F_short <- pcod_mse_short@FM
dimnames(pcod_mse_F_short) <- list(1:nSim, pcod_mse_short@MPs, 1:nYear)

#convert arrays to data frames
z1 <- apply(pcod_mse_F_short, 3L, c)
z2 <- expand.grid(dimnames(pcod_mse_F_short)[1:2])
mp_F_pc_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "FM"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch and biomass from the short list of MPs 
ggF <- mp_F_pc_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=FM,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Fishing Mortality")+ xlab("Year")+ ylab("Fishing Mortality")
print(ggF)

```

\newpage
Look at vulnerable biomass ... as expected it's the same more or less as spawning biomass because selectivity in the OM is almost knife-edged and close to maturity ogive.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
pcod_mse_VB_short <- pcod_mse_short@VB
dimnames(pcod_mse_VB_short) <- list(1:nSim, pcod_mse_short@MPs, 1:nYear)

#convert arrays to data frames
z1 <- apply(pcod_mse_VB_short, 3L, c)
z2 <- expand.grid(dimnames(pcod_mse_VB_short)[1:2])
mp_VB_pc_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "VBiomass"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch and biomass from the short list of MPs 
ggVB <- mp_VB_pc_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=VBiomass,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Vulnerable Biomass")+ xlab("Year")+ ylab(" Vulnerable Biomass")
print(ggVB)

```




```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
pcod_mse_BBMSY_short <- pcod_mse_short@B_BMSY
dim(pcod_mse_BBMSY_short) #dimensions of array are 1:nSim, 1:nMP, 1:nYear

#Give names to the array so they can be used for plotting
nSim <- ompc@nsim
nYear <- ncol(pcod_mse_BBMSY_short[,1,]) #find global parameter for number of projection years
dimnames(pcod_mse_BBMSY_short) <- list(c(1:nSim), pcod_mse_short@MPs, 1:nYear)

#convert to data frame and plot
z1 <- apply(pcod_mse_BBMSY_short, 3L, c)
z2 <- expand.grid(dimnames(pcod_mse_BBMSY_short)[1:2])
mp_bbmsy_pc_short <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "BBMSY"=value) %>% 
  mutate(Year=as.numeric(Year)) 

p <-  filter(mp_bbmsy_pc_short, MP %in% mppc_short[1:4]) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY))+
  geom_boxplot()+
  facet_grid(rows=vars(MP)) + xlab("Year")+ ylab("B/BMSY") 
print(p)

p1 <-  filter(mp_bbmsy_pc_short, MP %in% mppc_short[5:8]) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY))+
  geom_boxplot()+
  facet_grid(rows=vars(MP)) + xlab("Year")+ ylab("B/BMSY") 
print(p1)

```


\newpage

Dig into some results further 


```{r, fig.asp=1.9, out.width = "4.8in", fig.width=7}
library(dplyr)
library(RColorBrewer)
nmp <- data.frame(mp = seq_along(pcod_mse_short@MPs), mp_name = pcod_mse_short@MPs)

ffmsy <- pcod_mse_short@F_FMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value, year = Var3)
bbmsy <- pcod_mse_short@B_BMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value, year = Var3)
cat <- pcod_mse_short@C[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, catch = value, year = Var3)
biomass <- pcod_mse_short@SSB[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, Biomass = value, year = Var3)
d <- dplyr::inner_join(ffmsy, bbmsy) 
d <- dplyr::inner_join(d, cat) 
d <- dplyr::inner_join(d, biomass)
d <- dplyr::left_join(d, nmp)
d <- reshape2::melt(d, id.vars = c("iter", "mp", "year", "mp_name"))
levels(d$variable) <- c(expression(F/F[MSY]), expression(B/B[MSY]), expression(Catch), expression(Biomass))

d_median <- d %>% group_by(mp_name, year, variable) %>%
  summarise(median_value = median(value)) %>%
  mutate(iter = NA)

d_last <- dplyr::filter(d, year == max(year)) %>%
  select(-year) %>%
  rename(last_value = value)
d <- inner_join(d, d_last)

cols <- brewer.pal(3, "RdBu")
cols[2] <- "grey80"

plot_timeseries <- function(dat, dat_median, title = "",
  ylim = c(0, fudge), cols, values, labels = TRUE, yaxis = TRUE) {
  g <- ggplot(dat, aes_string("year", "value", group = "iter")) +
    geom_line(aes_string(colour = "last_value"), alpha = 0.3) +
    facet_grid(mp_name~., labeller = label_parsed) +
    ggsidekick::theme_sleek() +
    scale_colour_gradientn(colours = cols,
      values = values) +
    geom_line(data = dat_median, aes_string("year", "median_value"),
      colour = "black", lwd = 1.5) +
    ylim(ylim[1], ylim[2]) +
    ggtitle(title) +
    guides(colour = FALSE) +
    ylab("Value") + xlab("Year")

  if (!labels)
    g <- g + theme(strip.background = element_blank(),
      strip.text.y = element_blank())

  if (!yaxis)
    g <- g + theme(axis.text.y = element_blank())
  g
}

cols <- brewer.pal(5, "RdBu")
cols <- c(cols[1], "grey50", cols[length(cols)])
set.seed(42)
# d_ <- filter(d, iter %in% sample(seq_len(max(d$iter)), 30))
d_ <- d

maxC <- d_ %>% 
  dplyr::filter(variable=="Catch") %>% 
  select(value) %>% 
  max()

maxB <- d_ %>% 
  dplyr::filter(variable=="Biomass") %>% 
  select(value) %>% 
  max()

#
mps <- unique(d_$mp_name)
# mps <- mps[-which(mps %in% c("CC4"))]
p1 <- plot_timeseries(filter(d_, variable == "B/B[MSY]", mp_name %in% mps),
  filter(d_median, variable == "B/B[MSY]", mp_name %in% mps), expression(B/B[MSY]),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,5))
p2 <- plot_timeseries(filter(d_, variable == "F/F[MSY]", mp_name %in% mps),
  filter(d_median, variable == "F/F[MSY]", mp_name %in% mps), expression(F/F[MSY]),
  cols = cols, values = scales::rescale(c(5, 1.2, 0.8, 0)),
  labels = TRUE, ylim = c(0,5), yaxis = TRUE)
p3 <- plot_timeseries(filter(d_, variable == "Catch", mp_name %in% mps),
  filter(d_median, variable == "Catch", mp_name %in% mps), expression(Catch),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxC))
p4 <- plot_timeseries(filter(d_, variable == "Biomass", mp_name %in% mps),
  filter(d_median, variable == "Biomass", mp_name %in% mps), expression(Biomass),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxB))

gridExtra::grid.arrange(p4,p3,  p1, p2, ncol = 4)

#########3
ffmsy <- pcod_mse_short@F_FMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value, year = Var3)
bbmsy <- pcod_mse_short@B_BMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value, year = Var3)
d <- dplyr::inner_join(ffmsy, bbmsy)
d <- dplyr::left_join(d, nmp)
d <- reshape2::melt(d, id.vars = c("iter", "mp", "year", "mp_name"))
levels(d$variable) <- c(expression(F/F[MSY]), expression(B/B[MSY]))

d_sum <- d %>% group_by(mp_name, year, variable) %>%
  summarise(median_value = median(value),
    l = quantile(value, probs = 0.75),
    u = quantile(value, probs = 0.25),
    ll = quantile(value, probs = 0.95),
    uu = quantile(value, probs = 0.05))

d <- inner_join(d, d_last)

cols <- brewer.pal(5, "RdBu")
cols <- c(cols[1], "grey50", cols[length(cols)])
g <- ggplot(d_sum, aes_string("year", "median_value")) +
  facet_grid(mp_name~variable, labeller = label_parsed) +
  geom_ribbon(aes(ymin = ll, ymax = uu), fill = "grey90") +
  geom_ribbon(aes(ymin = l, ymax = u), fill = "grey70") +
  ggsidekick::theme_sleek() +
  geom_line(lwd = 1.5) +
  #coord_cartesian(ylim = c(0, 4)) +
  guides(colour = FALSE) +
  xlim(25, 50) +
  geom_hline(yintercept = 1,
    col = "black", lty = 2) +
  ylab("Value") + xlab("Year")
  
g
```

\newpage


```{r, fig.asp=1.9, out.width = "4.8in", fig.width=7}
mps <-  c("AvC", "SBT2", "DD4010")
p1 <- plot_timeseries(filter(d_, variable == "B/B[MSY]", mp_name %in% mps),
  filter(d_median, variable == "B/B[MSY]", mp_name %in% mps), expression(B/B[MSY]),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,10))
p2 <- plot_timeseries(filter(d_, variable == "F/F[MSY]", mp_name %in% mps),
  filter(d_median, variable == "F/F[MSY]", mp_name %in% mps), expression(F/F[MSY]),
  cols = cols, values = scales::rescale(c(5, 1.2, 0.8, 0)),
  labels = TRUE, ylim = c(0,10), yaxis = TRUE)
p3 <- plot_timeseries(filter(d_, variable == "Catch", mp_name %in% mps),
  filter(d_median, variable == "Catch", mp_name %in% mps), expression(Catch),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxC))
p4 <- plot_timeseries(filter(d_, variable == "Biomass", mp_name %in% mps),
  filter(d_median, variable == "Biomass", mp_name %in% mps), expression(Biomass),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxB))

gridExtra::grid.arrange(p4, p3, p2, nrow = 3)

```

\newpage

Look at the proportions at age. DLMtool doesn't output annual age comps so plot CAA for the first 16 reps. For now assume this is the CAA in the final year? Plots 1-3 show the MPs AvC, SBT2 and DD4010 for comparison. They seem to be identical as well.

AvC:

```{r}
nAge <- dim(pcod_mse_short@CAA)[3]

#For each MP pcod_mse_short@CAA contains nSim rows of nAge proportions
#Let's assume each replicate shows the final CAA
MSEtool::plot_composition(1:16, obs=pcod_mse_short@CAA[1:16,1,])

```

SBT2:

```{r}
nAge <- dim(pcod_mse_short@CAA)[3]

#For each MP pcod_mse_short@CAA contains nSim rows of nAge proportions
#Let's assume each replicate shows the final CAA
MSEtool::plot_composition(1:16, obs=pcod_mse_short@CAA[1:16,2,])

```

DD4010:

```{r}
#For each MP pcod_mse_short@CAA contains nSim rows of nAge proportions
#Let's assume each replicate shows the final CAA
MSEtool::plot_composition(1:16, obs=pcod_mse_short@CAA[1:16,3,])


```



DD4010:

```{r}
#For each MP pcod_mse_short@CAA contains nSim rows of nAge proportions
#Let's assume each replicate shows the final CAA
MSEtool::plot_composition(1:16, obs=pcod_mse_short@CAA[1:16,3,])


```

\newpage

Show probabilities of meeting performance metrics

```{r probability-table-abs-pc, fig.width = 9, fig.asp = 1, out.width = "4in"}
probs <- get_probs(pcod_mse_short, PMlist = c("P40", "P80","P100", "PNOF", "AAVY", "LTY"))
plot_probs(probs)
```

\newpage
Show radar plot. They all do more or less the same. DD is worst. I think we should remove this from the MPs. Delay-difference models are not data-limited and have too many decisions to throw into our toolkit of simple models. Plus it is behaving strangelY.

```{r}
library(ggspider)
pm_probs <- eval_pm(pcod_mse_short,
             pm_list = list("LTY",
                            "P10",
                            "P40",
                            "P80",
                            "P100",
                            "PNOF",
                            "AAVY")) 

#r_plot(x, fill_polys = TRUE, inc_yrs = FALSE)
ggspider::spider_web(pm_probs, "mp", "pm", "prob")

```


\newpage


Illustrating the built-in plotting functions:

```{r}
Tplot(pcod_mse_short)
Tplot2(pcod_mse_short)
```



```{r}
summary(pcod_mse_short)
```



```{r}
wormplot(pcod_mse_short)
```

```{r}
Pplot(pcod_mse_short)

```

```{r}
Pplot2(pcod_mse_short, traj="quant", quants=c(0.2, 0.8))
```

```{r}
Kplot(pcod_mse_short)
```

```{r}
#Cplot(pcod_mse_short)
```

And examine the output.


```{r, fig.asp=1}
yend <- max(pcod_mse_short@proyears)
ffmsy <- pcod_mse_short@F_FMSY[,,yend]
bbmsy <- pcod_mse_short@B_BMSY[,,yend]

ffmsy <- reshape2::melt(ffmsy) %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value)
bbmsy <- reshape2::melt(bbmsy) %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value)

d <- dplyr::inner_join(ffmsy, bbmsy)

n <- data.frame(mp = seq_along(pcod_mse_short@MPs), mp_name = pcod_mse_short@MPs)
# n$mp_name <- paste(1:nrow(n), n$mp_name)

d <- dplyr::left_join(d, n)

library(ggplot2)
p <- ggplot(dplyr::filter(d, !mp_name %in% c("NFref")), aes(bbmsy, ffmsy)) +
  geom_vline(xintercept = c(0.4, 0.8), alpha = 0.2) +
  geom_hline(yintercept = 1, alpha = 0.2) +
  geom_density_2d(aes(colour = ..level..), bins = 5) +
  viridis::scale_colour_viridis() +
  ggsidekick::theme_sleek() +
  facet_wrap(~mp_name) +
  ylim(0, 3.5) + xlim(0, 3.5) +
  geom_point(alpha = 0.2) +
  labs(colour = "Prob. density", x = expression(B/B[MSY]),
    y = expression(F/F[MSY])) +
  guides(colour = FALSE)
print(p)
#ggsave("analysis/pcod-bbmsy-ffmsy-multi.pdf", width = 8, height = 8)
```

```{r}
 plot(pcod_mse_short)
 oldpar <- par()
##DFO_hist(pcod_mse)
par(mfrow = c(1, 1))
DFO_plot(pcod_mse_short)
# DFO_plot2(pcod_mse)
```

```{r, fig.asp=1, warning=FALSE}
DFO_proj(pcod_mse_short)
#DFO_hist(pcod_om)
# DFO_plot2(pcod_mse)

# d <- DFO_plot2(pcod_mse)
# ggplot(d, aes(B50/100, LTY/100, label = MPs, colour = Satisfice)) +
#   geom_vline(xintercept = 0.5, col = "grey50") +
#   geom_hline(yintercept = 0.5, col = "grey50") +
#   geom_text() + ggsidekick::theme_sleek() +
#   scale_colour_manual(values = c("grey60", "black")) +
#   guides(colour = FALSE) +
#   xlab(expression(Pr(B>0.5~B[MSY]))) +
#   ylab(expression(Pr(yield>0.5~yield~at~F[MSY]))) +
#   xlim(0, 1) + ylim(0, 1)
par(oldpar)
```

```{r, fig.asp=1.2}
voi_out <- DLMtool::VOI(pcod_mse_short)
```
