\newpage

# REX SOLE: MANAGEMENT PROCEDURE SPECIFICATIONS {#app:desc-mp-rex}

Use the management procedures that passed the screening test

```{r}
mprex <- c(
  "AvC",
  "CC2",
  "CC3",
  "DD",
  "DD4010",
  "GB_CC",
  "GB_target",
  "Islope1",
  "Islope2",
  "Islope4",
  "IT5",
  "ITM",
  "LstepCC2",
  "LstepCC3",
  "LstepCC4",
  "Ltarget1",
  "Ltarget2",
  "Ltarget3",
  "SBT2",
  "SP_4010",
  "SP_MSY"
)

# Group MPs into similar types
# mprex_group <- list()
# mprex_group[[1]] <- mprex[1:3]
# mprex_group[[2]] <- mprex[4:5]
# mprex_group[[3]] <- mprex[6:7]
# mprex_group[[4]] <- mprex[8:10]
# mprex_group[[5]] <- mprex[c(11:12,19)]
# mprex_group[[6]] <- mprex[13:15]
# mprex_group[[7]] <- mprex[16:18]
# mprex_group[[8]] <- mprex[20:21]
#
# mptypenames <- c("Av Catch", "Delay Difference","Catch Target", "Index Slope", "Index Target","Stepwise Constant Catch", "Length Target","Surplus Production")
```

# REX SOLE: RESULTS 

## Constructing the operating model

Get the operating model. For Shortraker we are using the DLMtool operating model.

```{r echo = TRUE}
omrex <- readRDS(here::here("generated-data", "rex-om-sra.rds"))
```

\newpage

Run the historical part of the MSE. 

```{r, fig.asp=0.8}
DLMtool::setup(cpus = parallel::detectCores())
rex_historical <- runMSE(omrex, Hist = TRUE, parallel = TRUE, ntrials = 1000)
snowfall::sfStop()

# real_catch <- read.csv(here::here("report/data/shortraker-corrected-catch.csv"))
# real_catch <- mutate(real_catch, synthetic = ifelse(Year >= 1990 & Year <= 1995, Predicted.catch, Observed.catch))
#
# all_years <- data.frame(Year = (2018 - fleet@nyears):2018)
# real_catch <- dplyr::left_join(all_years, real_catch)

# set.seed(1567)
catch <- rex_historical@TSdata$Catch %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 100)) %>%
  transmute(
    sample_id = Var1, year = Var2 + min(all_years) - 1,
    catch = value, type = "Simulated"
  ) # %>%
# bind_rows(data.frame(sample_id = 0, year = real_catch$Year,
#   catch = real_catch$synthetic, type = "Observed", stringsAsFactors = FALSE))

library(ggplot2)
catch %>%
  filter(!is.na(catch)) %>%
  group_by(sample_id) %>%
  mutate(catch = catch / max(catch)) %>%
  ggplot(aes(year, catch, colour = type, group = sample_id)) +
  geom_line() +
  # facet_wrap(~sample_id) +
  ylab("Historical catch") +
  xlab("Year")

# Look at the simulated biomass from a random set of replicates.
rex_historical@TSdata$B %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 100)) %>%
  ggplot(aes(Var2, value, group = Var1)) +
  geom_line() +
  # facet_wrap(~Var1, scales = "free_y") +
  ylab("Simulated historical biomass") +
  xlab("Year")
```

\newpage

Now run the closed loop simulation with the MPs above.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "rex-mse.rds")
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  rex_mse <- runMSE(OM = omrex, MPs = mprex, parallel = TRUE, ntrials = 1000)
  snowfall::sfStop()
  saveRDS(rex_mse, file = file_name)
} else {
  rex_mse <- readRDS(file_name)
}
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}
DLMtool::Converge(rex_mse)
```

```{r probability-table-abs-rex, fig.width = 9, fig.asp = 1, out.width = "4in"}
STY <- pm_factory("LTY", 0.5, c(6, 20))
LTY <- pm_factory("LTY", 0.5, c(36, 50))

PM <- c("P40_yrs36_50", "P80_yrs36_50", "STY", "LTY", "AAVY", "PNOF")

# TODO: Error: PNOF_yrs36_50  is not a valid PM method
probs <- get_probs(rex_mse, PMlist = as.list(PM))
plot_probs(probs)
```

```{r probability-table-0-1-rex, fig.width = 9, fig.asp = 1, out.width = "4in"}
# plot_probs(probs, scale_0_1 = TRUE)
```

```{r}
x <- eval_pm(rex_mse,
  pm_list = as.list(PM)
) %>% select(mp, pm, prob)
satisficed <- filter(probs[[1]], P40_yrs36_50 >= 0.8) %>% pull(MP)
xx <- dplyr::filter(x, mp %in% satisficed)
ggspider::spider_web(xx, "mp", "pm", "prob")
```

