---
title: "Investigating the Delay Difference model in DLMtool and MSEtool"
author: "Robyn Forrest"
date: "July 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The function DLMtool::DD_ is saved in the file R/DLMtool_DD_.R as myDLDD_()

The function optimized by DD_ is DLMtool::DD_R, which is the actual model code. It is saved in the file R/DLMtool_DD_R.R as myDLDD_R().

First source the DD_ functions.

```{r}
source(here::here("DD_investigation/DLMtool_DD_.R"))
source(here::here("DD_investigation/DLMtool_DD_R.R"))

```

Now make a data object. Use the red snapper data csv from the DLMtool library, then check whether the delay difference model is possible with this dataset using the Can function.

```{r}
library(DLMtool)
dat <- DLMtool::XL2Data(here::here("DD_investigation/Red_snapper.csv"))

#Check whether DD is possible with this dataset
DLMtool::Can(dat)

```

DD is on the list, meaning there is sufficient data to run DD_.

Now run the model with the data object ... check it is working. Note that we call myDLDD_(), which has been modified to optimize myDLDD_R() for this exercise.

```{r}
myDDresults <- myDLDD_(1,dat,reps=1, hcr=NULL)

#plot results
plot(myDDresults$Year, myDDresults$C_hist, type="l")
points(myDDresults$Year, myDDresults$Cpredict,col=2,pch=19)

#plot(myDDresults$Year, myDDresults$I_hist, type="l")
plot(myDDresults$Year, myDDresults$E_hist, type="l")


plot(myDDresults$Year, myDDresults$B_DD[-length(myDDresults$B_DD)], type="l")

```

Yes it is working, but doing a bad job of fitting recent catch data. 

Now check on what parameters are estimated and what data the model is fitting to.


Parameters are estimated by minimizing the neg log likelihood using the optim function.  

The actual delay difference model that gets optimized is internal function DLMtool::DD_R, which RF renamed myDLDD_R for this exercise:

* params <- log(c(UMSYpriorpar[1]/(1 - UMSYpriorpar[1]), 3 *
                    mean(C_hist, na.rm = T), Data@Mort[x]))
                    
* opt <- optim(params, DD_R, opty = 1, So_DD = So_DD, Alpha_DD = Alpha_DD,
               Rho_DD = Rho_DD, ny_DD = ny_DD, k_DD = k_DD, wa_DD = wa_DD,
               E_hist = E_hist, C_hist = C_hist, UMSYprior = UMSYprior,
               method = "BFGS", hessian = TRUE)



**Estimated parameters**

Umsy -- starting value = UMSYpriorpar[1]/(1 - UMSYpriorpar[1])

MSY -- starting value = 3 * mean(C_hist, na.rm = T)

q -- starting value = Data@Mort[x], where x is the iteration number. For a real data file, x=1.

According to the code in DD_R, the third parameter is q, which is used with the effort data to derive F (F = qE). Odd to initialise this parameter at the value for M.

UMSYpriorpar[1] = 1 - exp(-Data@Mort[x] * 0.5)  This is half the annual natural mortality rate 

There is also a prior on Umsy. We will return to UMSYprior below.


**Fixed model inputs to DD_R**

So_DD -- Unfished (natural) survival rate = (exp(-M))

k_DD -- age-at-recruitment (knife-edged age at selectivity and maturity) Derived from back-calculation of age at L50 from inverted VB curve --- a bit dodgy

wa_DD -- weight at age at recruitment --- from k_DD and growth parameters

Once you have k_DD and wa_DD you can calculate Alpha and Rho from the VB function:

Alpha_DD -- Ford-Walford growth parameter (intercept) 

Rho_DD -- Ford-Walford growth parameter (slope)

ny_DD -- length of catch history



**Data inputs to DD_R**

C_hist -- historical catch. This comes from the data object Data@Cat[x, yind]

E_hist -- historical effort. This is calculated as a function of catch and the index. 
    
E_hist <- C_hist/I_hist

This is essentially a back calculation assuming I_hist = C_hist/E_hist (i.e., CPUE). 

This seems dodgy as the catch and the index are coming from different sources (fishery-dependent and fishery independent). At this point I am wondering if this is grounds to reject this MP ...

Note that if there are any NA values in either the catch or the index, they are interpolated using R's approx function.

**Prior on the productivity parameter Umsy**

* UMSYpriorpar <- c(1 - exp(-Data@Mort[x] * 0.5), 0.3)  The two parameters here are a mean and sd

* UMSYprior <- c(alphaconv(UMSYpriorpar[1], prod(UMSYpriorpar)),
                 betaconv(UMSYpriorpar[1], prod(UMSYpriorpar)))

Convert this mean and sd to the alpha and beta parameters of the beta dist:

DLMtool::alphaconv gives

function (m, sd) 

m * (((m * (1 - m))/(sd^2)) - 1)

DLMtool::betaconv gives

function (m, sd) 

(1 - m) * (((m * (1 - m))/(sd^2)) - 1)

Test what this is doing:

```{r}
mort <- dat@Mort
par1 <- 1 - exp(-mort * 0.5)
umsypriorpar <- c(par1,0.3)
prod(umsypriorpar)
alphaconv(umsypriorpar[1],prod(umsypriorpar))
betaconv(umsypriorpar[1],prod(umsypriorpar))


umsyprior <- c(alphaconv(umsypriorpar[1], prod(umsypriorpar)),
                 betaconv(umsypriorpar[1], prod(umsypriorpar)))

plot(density(rbeta(100000, umsyprior[1], umsyprior[2])))
```

OK so it is giving a prior for Umsy centred on about half of natural mortality. TAC is then calculated as Umsy * B_DD_nyr+1.

*RF modified myDLDD_() to output UMSY*

```{r}

UMSY <- myDDresults$UMSY
B_DD_proj <- myDDresults$B_DD[length(myDDresults$B_DD)] #projection year
TAC <- myDDresults$TAC
TACtest <- UMSY*B_DD_proj

UMSY
B_DD_proj
TAC
TACtest

```


How sensitive is the TAC to the input M value?

```{r}
#increase dat@Mort to 0.2
mort_orig <- dat@Mort
dat@Mort <- 0.2
mort <- dat@Mort
par1 <- 1 - exp(-mort * 0.5)
umsypriorpar <- c(par1,0.3)
prod(umsypriorpar)
alphaconv(umsypriorpar[1],prod(umsypriorpar))
betaconv(umsypriorpar[1],prod(umsypriorpar))


umsyprior2 <- c(alphaconv(umsypriorpar[1], prod(umsypriorpar)),
                 betaconv(umsypriorpar[1], prod(umsypriorpar)))

x2 <- density(rbeta(100000, umsyprior2[1], umsyprior2[2]))

plot(density(rbeta(100000, umsyprior2[1], umsyprior2[2])), ylim=c(0,2.2*max(x2$y)), xlab="UMSY", ylab="Density", main= "UMSY prior")
lines(density(rbeta(100000, umsyprior[1], umsyprior[2])), col=2)
legend("topright", legend=c(paste("Mort=",mort),paste("Mort=",mort_orig)), lty=1, col=1:2)

#rerun the DD model with the new dat@Mort and prior
myDDresults2 <- myDLDD_(1,dat,reps=1, hcr=NULL)

UMSY2 <- myDDresults2$UMSY
TAC2 <- myDDresults2$TAC

UMSY2
TAC2

uresult <- cbind(c(mort_orig, mort), c(UMSY,UMSY2))
barplot(uresult[,2], names.arg=uresult[,1], col="salmon", xlab="Input Mortality", ylab="UMSY")

tacresult <- cbind(c(mort_orig, mort), c(TAC,TAC2))
barplot(tacresult[,2], names.arg=tacresult[,1], col="lightblue", xlab="Input Mortality", ylab="TAC")


```

## Simulation test

Use the Pacific Cod OM. Run with the basic OM.
```{r echo = TRUE}

ompc <- readRDS(here::here("sra/pcod_no_comps_om.rds"))

ompc@nsim <- 150L
setup()
pcod_mse <- DLMtool::runMSE(OM = ompc, MPs = "DD", ntrials = 1000, PPD = TRUE, parallel=TRUE)
saveRDS(pcod_mse,here::here("DD_investigation/pcod_mse.R"))

```

Plot the results

```{r, fig.asp=1.9, out.width = "4.8in", fig.width=7}
library(tidyverse)
library(RColorBrewer)

Btrue <- pcod_mse@SSB
nSim <- dim(Btrue)[1]
nMP <-  dim(Btrue)[2]
nYear <- dim(Btrue)[3]
dimnames(Btrue) <- list(1:nSim, "DD", 1:nYear)

#convert to data frame and plot
z1 <- apply(Btrue, 3L, c)
z2 <- expand.grid(dimnames(Btrue)[1:2])
Btrue <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"MP"=Var2,"fYear"=variable, "Biomass"=value) %>%
  mutate(Year=as.numeric(as.factor(fYear)))

Bmed <- Btrue %>% 
  dplyr::group_by(Year) %>% 
  dplyr::summarise(Median = median(Biomass),
    q75th = quantile(Biomass, probs = 0.75),
    q25th = quantile(Biomass, probs = 0.25),
    q95th = quantile(Biomass, probs = 0.95),
    q5th = quantile(Biomass, probs = 0.05))


g <- ggplot(Bmed,aes(x=Year)) +
    geom_ribbon(aes(ymin = q5th, ymax = q95th), fill = "grey90") +
    geom_ribbon(aes(ymin = q25th, ymax = q75th), fill = "grey70") +
    geom_line(aes(y=Median), lwd=2) +
    ggsidekick::theme_sleek() +
      guides(colour = FALSE) +
    ylab("Biomass") + xlab("Year")
print(g) 
  
Mtrue <- pcod_mse@OM$M
FMSYtrue <- pcod_mse@OM$FMSY
Productivity <- cbind(Mtrue,FMSYtrue)
boxplot(Productivity, names=c("True M", "True FMSY"), col="lightgray")


```

Get the whole time series including the historical biomass

```{r}


B1 <- pcod_mse@SSB_hist[,,,1]
B2 <- pcod_mse@SSB_hist[,,,2]
nSim <- dim(B1)[1]
nAge <- dim(B1)[2]
nYear <- dim(B1)[3]
dimnames(B1) <- list(1:nSim, 1:nAge, as.numeric(1:nYear))
dimnames(B2) <- list(1:nSim, 1:nAge, as.numeric(1:nYear))

#convert to data frames and get total biomass per year per area
z1 <- apply(B1, 3L, c)
z2 <- expand.grid(dimnames(B1)[1:2])
Btrue_hist_area1 <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"Age"=Var2,"fYear"=variable, "Biomass"=value) %>% 
  mutate(Year=as.numeric(as.factor(fYear))) %>% 
  group_by(Sim,Year) %>%
  summarise(Btot1=sum(Biomass))

z1 <- apply(B2, 3L, c)
z2 <- expand.grid(dimnames(B2)[1:2])
Btrue_hist_area2 <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"Age"=Var2,"fYear"=variable, "Biomass"=value) %>% 
  mutate(Year=as.numeric(as.factor(fYear))) %>% 
  group_by(Sim,Year) %>%
  summarise(Btot2=sum(Biomass))

#Get total biomass per year
Btrue_hist <- left_join(Btrue_hist_area1, Btrue_hist_area2) %>% 
  mutate(Biomass = Btot1 + Btot2)

#Now get medians and quantiles
Bmed_hist <- Btrue_hist %>% 
  dplyr::group_by(Year) %>% 
  dplyr::summarise(Median = median(Biomass),
    q75th = quantile(Biomass, probs = 0.75),
    q25th = quantile(Biomass, probs = 0.25),
    q95th = quantile(Biomass, probs = 0.95),
    q5th = quantile(Biomass, probs = 0.05))

#Now join up with MSE results
#First renumber the years
nhistYear <- nYear
Bmed$Year <- Bmed$Year + nhistYear

Bmed_all <- rbind(Bmed_hist, Bmed)

#Plot
g <- ggplot(Bmed_all,aes(x=Year)) +
    geom_ribbon(aes(ymin = q5th, ymax = q95th), fill = "grey90") +
    geom_ribbon(aes(ymin = q25th, ymax = q75th), fill = "grey70") +
    geom_line(aes(y=Median), lwd=1.5) +
    ggsidekick::theme_sleek() +
    geom_vline(xintercept=nhistYear, linetype="dashed", lwd=0.5)+
    guides(colour = FALSE) +
    ylab("Biomass") + xlab("Year")
print(g) 
  


```

Now look at what the DD model thought the biomass was

First look at one "slice" from the OM simulated data. Use the standalone version of the DD model to get more outputs (UMSY and M)

```{r}

#Function by Sean to get the output from a delay difference model
DD_output <- function(x, Data, reps = 1, plot=FALSE) {
  runDD <- DLMtool:::DD_(x, Data, reps)
  TAC <- DLMtool:::TACfilter(runDD$TAC)
  
  if (plot) DLMtool:::DD_plot(x, runDD, Data, TAC) #Dlmtool function that plots the delay difference MP's estimate of biomass
  
  # Rec <- new("Rec")
  # Rec@TAC <- TAC
  runDD
}

#Note, always set pcod_mse@Misc$Data[[x]] to x=1
out <- DD_output(1, pcod_mse@Misc$Data[[1]], reps = 1, plot = TRUE)

```


Now get the DD estimates of biomass from all the MSE replicates

```{r}

nsims <- 1:nSim

DD_sims_output <- function(x){
  out <- DD_output(x, pcod_mse@Misc$Data[[1]], reps = 1, plot = FALSE)
  return(out$B_DD)
}

ddout <- sapply(nsims,DD_sims_output)
dim(ddout)

Bmed_mp <- ddout %>% 
  reshape2::melt() %>% 
  rename("Year"=Var1,"Sim"=Var2,"MPBiomass"=value) %>%
  dplyr::group_by(Year) %>% 
  dplyr::summarise(MedianMP = median(MPBiomass),
    q75thMP = quantile(MPBiomass, probs = 0.75),
    q25thMP = quantile(MPBiomass, probs = 0.25),
    q95thMP = quantile(MPBiomass, probs = 0.95),
    q5thMP = quantile(MPBiomass, probs = 0.05))


#Plot
g <- ggplot(Bmed_mp,aes(x=Year)) +
    geom_ribbon(aes(ymin = q5thMP, ymax = q95thMP), fill = "pink1") +
    geom_ribbon(aes(ymin = q25thMP, ymax = q75thMP), fill = "lightcoral") +
    geom_line(aes(y=MedianMP), lwd=1.5, colour="red") +
    ggsidekick::theme_sleek() +
    geom_vline(xintercept=nhistYear, linetype="dashed", lwd=0.5)+
    guides(colour = FALSE) +
    ylab("Biomass") + xlab("Year")
print(g) 

```


Now overlay the two plots

```{r}
Bmed_all_short <- Bmed_all %>% 
  dplyr::filter(Year %in% 1:(nrow(Bmed_all)-1))  #Not sure whether the first or last year is missing from B_DD!

Bmed_combined <- inner_join(Bmed_all_short, Bmed_mp)

g <- ggplot(Bmed_combined,aes(x=Year)) +
    geom_ribbon(aes(ymin = q5th, ymax = q95th), fill = "grey90") +
    geom_ribbon(aes(ymin = q25th, ymax = q75th), fill = "grey70") +
    geom_line(aes(y=Median), lwd=1.5) +
  
    geom_ribbon(aes(ymin = q5thMP, ymax = q95thMP), fill = "pink1", alpha=0.4) +
    geom_ribbon(aes(ymin = q25thMP, ymax = q75thMP), fill = "lightcoral", alpha=0.4) +
    geom_line(aes(y=MedianMP), lwd=1.5, colour="red", alpha=0.5) +
  
    ggsidekick::theme_sleek() +
    geom_vline(xintercept=nhistYear, linetype="dashed", lwd=0.5)+
    guides(colour = FALSE) +
    ylab("Biomass") + xlab("Year")
print(g) 


```


*Try a different operating model with  bias in M*

Use the Pacific Cod OM. Run with the basic OM.
```{r echo = TRUE}

ompc2 <- readRDS(here::here("sra/pcod_no_comps_om_Mbias.rds"))

ompc2@nsim <- 150L
setup()
pcod_mse2 <- DLMtool::runMSE(OM = ompc2, MPs = "DD", ntrials = 1000, PPD = TRUE, parallel=TRUE)
saveRDS(pcod_mse2,here::here("DD_investigation/pcod_mse_Mbias.R"))

```

Plot the results

```{r, fig.asp=1.9, out.width = "4.8in", fig.width=7}
library(tidyverse)
library(RColorBrewer)

Btrue2 <- pcod_mse2@SSB
nSim <- dim(Btrue2)[1]
nMP <-  dim(Btrue2)[2]
nYear <- dim(Btrue2)[3]
dimnames(Btrue2) <- list(1:nSim, "DD", 1:nYear)

#convert to data frame and plot
z1 <- apply(Btrue2, 3L, c)
z2 <- expand.grid(dimnames(Btrue2)[1:2])
Btrue2 <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"MP"=Var2,"fYear"=variable, "Biomass"=value) %>%
  mutate(Year=as.numeric(as.factor(fYear)))

Bmed2 <- Btrue2 %>% 
  dplyr::group_by(Year) %>% 
  dplyr::summarise(Median = median(Biomass),
    q75th = quantile(Biomass, probs = 0.75),
    q25th = quantile(Biomass, probs = 0.25),
    q95th = quantile(Biomass, probs = 0.95),
    q5th = quantile(Biomass, probs = 0.05))


g <- ggplot(Bmed2,aes(x=Year)) +
    geom_ribbon(aes(ymin = q5th, ymax = q95th), fill = "grey90") +
    geom_ribbon(aes(ymin = q25th, ymax = q75th), fill = "grey70") +
    geom_line(aes(y=Median), lwd=2) +
    ggsidekick::theme_sleek() +
      guides(colour = FALSE) +
    ylab("Biomass") + xlab("Year")
print(g) 

Mtrue2 <- pcod_mse2@OM$M
FMSYtrue2 <- pcod_mse2@OM$FMSY
Productivity2 <- cbind(Mtrue2,FMSYtrue2)
boxplot(Productivity2, names=c("True M", "True FMSY"), col="lightblue")

```

Get the whole time series including the historical biomass

```{r}


B1 <- pcod_mse2@SSB_hist[,,,1]
B2 <- pcod_mse2@SSB_hist[,,,2]
nSim <- dim(B1)[1]
nAge <- dim(B1)[2]
nYear <- dim(B1)[3]
dimnames(B1) <- list(1:nSim, 1:nAge, as.numeric(1:nYear))
dimnames(B2) <- list(1:nSim, 1:nAge, as.numeric(1:nYear))

#convert to data frames and get total biomass per year per area
z1 <- apply(B1, 3L, c)
z2 <- expand.grid(dimnames(B1)[1:2])
Btrue2_hist_area1 <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"Age"=Var2,"fYear"=variable, "Biomass"=value) %>% 
  mutate(Year=as.numeric(as.factor(fYear))) %>% 
  group_by(Sim,Year) %>%
  summarise(Btot1=sum(Biomass))

z1 <- apply(B2, 3L, c)
z2 <- expand.grid(dimnames(B2)[1:2])
Btrue2_hist_area2 <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"Age"=Var2,"fYear"=variable, "Biomass"=value) %>% 
  mutate(Year=as.numeric(as.factor(fYear))) %>% 
  group_by(Sim,Year) %>%
  summarise(Btot2=sum(Biomass))

#Get total biomass per year
Btrue2_hist <- left_join(Btrue2_hist_area1, Btrue2_hist_area2) %>% 
  mutate(Biomass = Btot1 + Btot2)

#Now get medians and quantiles
Bmed2_hist <- Btrue2_hist %>% 
  dplyr::group_by(Year) %>% 
  dplyr::summarise(Median = median(Biomass),
    q75th = quantile(Biomass, probs = 0.75),
    q25th = quantile(Biomass, probs = 0.25),
    q95th = quantile(Biomass, probs = 0.95),
    q5th = quantile(Biomass, probs = 0.05))

#Now join up with MSE results
#First renumber the years
nhistYear <- nYear
Bmed2$Year <- Bmed2$Year + nhistYear

Bmed2_all <- rbind(Bmed2_hist, Bmed2)

#Plot
g <- ggplot(Bmed2_all,aes(x=Year)) +
    geom_ribbon(aes(ymin = q5th, ymax = q95th), fill = "grey90") +
    geom_ribbon(aes(ymin = q25th, ymax = q75th), fill = "grey70") +
    geom_line(aes(y=Median), lwd=1.5) +
    ggsidekick::theme_sleek() +
    geom_vline(xintercept=nhistYear, linetype="dashed", lwd=0.5)+
    guides(colour = FALSE) +
    ylab("Biomass") + xlab("Year")
print(g) 
  


```

Now look at what the DD model thought the biomass was. Get the DD estimates of biomass from all the MSE replicates.

```{r}

nsims <- 1:nSim

DD_sims_output2 <- function(x){
  out <- DD_output(x, pcod_mse2@Misc$Data[[1]], reps = 1, plot = FALSE)
  return(out$B_DD)
}

ddout2 <- sapply(nsims,DD_sims_output2)
dim(ddout2)

Bmed2_mp <- ddout2 %>% 
  reshape2::melt() %>% 
  rename("Year"=Var1,"Sim"=Var2,"MPBiomass"=value) %>%
  dplyr::group_by(Year) %>% 
  dplyr::summarise(MedianMP = median(MPBiomass),
    q75thMP = quantile(MPBiomass, probs = 0.75),
    q25thMP = quantile(MPBiomass, probs = 0.25),
    q95thMP = quantile(MPBiomass, probs = 0.95),
    q5thMP = quantile(MPBiomass, probs = 0.05))


#Plot
g <- ggplot(Bmed2_mp,aes(x=Year)) +
    geom_ribbon(aes(ymin = q5thMP, ymax = q95thMP), fill = "pink1") +
    geom_ribbon(aes(ymin = q25thMP, ymax = q75thMP), fill = "lightcoral") +
    geom_line(aes(y=MedianMP), lwd=1.5, colour="red") +
    ggsidekick::theme_sleek() +
    geom_vline(xintercept=nhistYear, linetype="dashed", lwd=0.5)+
    guides(colour = FALSE) +
    ylab("Biomass") + xlab("Year")
print(g) 

```


Now overlay the two plots

```{r}
Bmed2_all_short <- Bmed2_all %>% 
  dplyr::filter(Year %in% 1:(nrow(Bmed2_all)-1))  #Not sure whether the first or last year is missing from B_DD!

Bmed2_combined <- inner_join(Bmed2_all_short, Bmed2_mp)

g <- ggplot(Bmed2_combined,aes(x=Year)) +
    geom_ribbon(aes(ymin = q5th, ymax = q95th), fill = "grey90") +
    geom_ribbon(aes(ymin = q25th, ymax = q75th), fill = "grey70") +
    geom_line(aes(y=Median), lwd=1.5) +
  
    geom_ribbon(aes(ymin = q5thMP, ymax = q95thMP), fill = "pink1", alpha=0.4) +
    geom_ribbon(aes(ymin = q25thMP, ymax = q75thMP), fill = "lightcoral", alpha=0.4) +
    geom_line(aes(y=MedianMP), lwd=1.5, colour="red", alpha=0.5) +
  
    ggsidekick::theme_sleek() +
    geom_vline(xintercept=nhistYear, linetype="dashed", lwd=0.5)+
    guides(colour = FALSE) +
    ylab("Biomass") + xlab("Year")
print(g) 


```

Look at the TAC recommended in the two cases

```{r}
TACbase <- pcod_mse@TAC
TACbias <- pcod_mse2@TAC

TACcompare <- cbind(TACbase, TACbias)
boxplot(TACcompare, names=c("TAC base", "TAC M bias"), col=c("lightgray", "lightblue"), outline=FALSE)



```

Hmm, well I am not sure we are really putting this model to the test. The TACs for the red snapper model on a real dataset were extremely sensitive to the input M value. I tried putting the MBiasCV parameter up to a very high level. It had a big effect on biomass but hardly affected TAC. I'd be curious to know what M is being passed to the DD MP. Can't test it right now as custom MPs aren't working.

Look at the distribution of M in the two OMs. Should be the same because only MbiasCV is changed

```{r}
Mtrue <- pcod_mse@OM$M
Mtrue2 <- pcod_mse2@OM$M
Mcompare <- cbind(Mtrue,Mtrue2)
boxplot(Mcompare, names=c("True M  base", "True M bias"), col=c("lightgray", "lightblue"), outline=FALSE)

```

Now look at M passed to the delay difference model from each OM

```{r}
Mdat1 <- pcod_mse@Misc$Data[[1]]@Mort
Mdat2 <- pcod_mse2@Misc$Data[[1]]@Mort
Mdat_compare <- cbind(Mdat1,Mdat2)
boxplot(Mdat_compare, names=c("DD M  base", "DD M bias"), col=c("lightgray", "lightblue"), outline=FALSE)

```

Compare True M and the M passed to the delay difference model from each OM

```{r}
library(reshape2)

om1 <- readRDS(here::here("sra/pcod_no_comps_om.rds"))
om2 <- readRDS(here::here("sra/pcod_no_comps_om_Mbias.rds"))

mbias1 <- om1@Mbiascv
mbias2 <- om2@Mbiascv

Mall <- as.data.frame(cbind(Mcompare,Mdat_compare))
colnames(Mall) <- c("True_M_base", "True_M_bias","DD_M_base", "DD_M_bias")

upper.limit <- quantile(Mall$DD_M_bias)[4] + 1.5*IQR(Mall$DD_M_bias)
lower.limit <- quantile(Mall$DD_M_bias)[2] - 1.5*IQR(Mall$DD_M_bias)

g <- Mall %>% 
  melt() %>% 
  mutate(OM=c(rep("M No Bias",nSim), rep("M Bias",nSim),rep("M No Bias",nSim), rep("M Bias",nSim))) %>% 
  rename(Model=variable, M=value) %>% 
  ggplot(aes(x=Model,y=M, fill=OM)) +
  geom_boxplot(outlier.shape=NA)+
  coord_cartesian(ylim=c(lower.limit, upper.limit))
print(g)
  


```

Try subsetting the MP results and plotting the TAC for the upper and lower slices

```{r}
below1 <- pcod_mse@Misc$Data[[1]]@Mort < median(pcod_mse@Misc$Data[[1]]@Mort)
above1 <- pcod_mse@Misc$Data[[1]]@Mort > median(pcod_mse@Misc$Data[[1]]@Mort)

belowMSE1 <- Sub(pcod_mse, sims=below1)
aboveMSE1 <- Sub(pcod_mse, sims=above1)

below2 <- pcod_mse2@Misc$Data[[1]]@Mort < median(pcod_mse2@Misc$Data[[1]]@Mort)
above2 <- pcod_mse2@Misc$Data[[1]]@Mort > median(pcod_mse2@Misc$Data[[1]]@Mort)

belowMSE2 <- Sub(pcod_mse2, sims=below2)
aboveMSE2 <- Sub(pcod_mse2, sims=above2)

belowMSE1@nsim
aboveMSE1@nsim
belowMSE2@nsim
aboveMSE2@nsim

TAC1_below <- belowMSE1@TAC
TAC2_below <- belowMSE2@TAC

TACcompare <- cbind(TAC1_below, TAC2_below)
boxplot(TACcompare, names=c("TAC base", "TAC M bias"), col=c("lightgray", "lightblue"), outline=FALSE, main="Lower slice of M in MP")

TAC1_above <- aboveMSE1@TAC
TAC2_above <- aboveMSE2@TAC

TACcompare <- cbind(TAC1_above, TAC2_above)
boxplot(TACcompare, names=c("TAC base", "TAC M bias"), col=c("lightgray", "lightblue"), outline=FALSE, main="Upper slice of M in MP")


```

<!-- Try running the custom DD model (myDLDD) to look at Umsy -->
<!-- *TO DO: export the myDLDD MP so can run in parallel* -->

<!-- ```{r} -->
<!-- ompc1 <- readRDS(here::here("sra/pcod_no_comps_om.rds")) -->
<!-- ompc2 <- readRDS(here::here("sra/pcod_no_comps_om_Mbias.rds")) -->
<!-- ompc3 <- readRDS(here::here("generated-data/pcod-om.rds")) -->
<!-- pcod_mse2b <- DLMtool::runMSE(OM = ompc3, MPs = "myDLDD", ntrials = 1000, PPD = TRUE, parallel=FALSE) -->


<!-- ``` -->







