# Hook and line effort for Shortraker

Quick glance at catches in merged catch gffos table for relevant fisheries:

```{r}
.d <- gfdata::run_sql(database = "GFFOS", "SELECT FISHERY_SECTOR
		, CAST(SUM(LANDED_KG) AS INT) LANDED_KG
	FROM GF_MERGED_CATCH C
	WHERE C.SPECIES_CODE = '403' 
		AND GEAR = 'HOOK AND LINE'
	GROUP BY FISHERY_SECTOR
	ORDER BY LANDED_KG DESC")
tot_catch <- sum(.d$LANDED_KG)
prop <- .d %>% mutate(landed_prop = LANDED_KG/tot_catch)
prop
```

So several of the fisheries only catch minimal Shortraker and wouldn't be 
included calculating effort. We will continue on with the top shortraker-
catching fisheries: ZN/Rockfish outside, Halibut and sablefish, Sabelfish, and
Halibut.

Looking at the catch of shortraker by these fisheries by year:

```{r}
.d <- gfdata::run_sql(database = "GFFOS", "SELECT YEAR(BEST_DATE) YEAR
		, FISHERY_SECTOR
		, CAST(SUM(LANDED_KG) AS INT) LANDED_KG
	FROM GF_MERGED_CATCH C
	WHERE C.SPECIES_CODE = '403' 
		AND GEAR = 'HOOK AND LINE'
		AND FISHERY_SECTOR IN ('HALIBUT', 'ZN', 'HALIBUT AND SABLEFISH', 'ROCKFISH OUTSIDE', 'SABLEFISH')
	GROUP BY FISHERY_SECTOR
		, YEAR(BEST_DATE)
	ORDER BY YEAR, FISHERY_SECTOR")
tot_catch <- .d %>% group_by(YEAR) %>%
  summarize(sum(LANDED_KG))
tot_catch
join <- inner_join(.d, tot_catch, by = "YEAR")
join %>% mutate(prop = formatC(LANDED_KG/sum(LANDED_KG), digits = 2))

```

Fishing event level data are not available for the Halibut fishery prior to 2006.
These data do exist and are held by the IPHC; however, we do not have access
to them. Therefore, we must look at effort in terms of trips.

(Alternatively, could look at fishing event level data and exclude Halibut fishery.
This could include depth and locality.)

To define the fleet, we can look at how much of the annual Shortraker catch is
encompassed by different combinations of threshold min catch in a threshold 
number of trips catching. The combination of thresholds that account for perhaps
~80% of catch may define the vessels that are targetting shortraker.

We could additionally examine other species caught with shortraker to define the
fleet that is targetting shortraker (with or without targetting other species
simultaneously).

Latitude is missing for > 181,500 out of 1,704,952 records so will not filter on 
latitudinal bounds.
SR, in a threshold number of years.

Separate within function between trip-level and fishing event-level dataset.

For fe-level, removed fe_start_date and fe_end_date qualifiers - these are often not available
and we would lose a lot of data. Were relevant for trawl to calculate tow time. 
Not necessary for hl.

Note years each fishery was active:
ZN 1985-2006 / Outside RF 2006-present
Halibut 1991-present
Sablefish 1995-present
Halibut and sablefish 2006-present

Many trips report fishing in multiple fishery areas, so 
cannot use major/minor/locality for trip-level.

TO DO: Some trips can cross over the boundary of fishing year (fishing events falling on different sides of the first day of the 'fishing year' on the same trip) and so the trip falls into two years when an alternate fishing year (to the calendar year) is specified. This probably shouldn't happen, and when looking at a fishery with alt-start-date individually instead of all fisheries which do not have the same start date it's probably fine. I have left alt-year out for now. I imagine just a filter for the max or min of alt-year by trip would fix it, but not sure at this point if it should be the min or max (max = offload, but min = fishing season open/not open).

When data are rolled up by everything trip related (376,829): 
-	Trip id
-	Year
-	Month (no duplicate records for a trip in different months)
-	Fishery sector
-	Vessel name and reg number
-	And species
-	With catch, landed and discarded columns summed


To check for duplicate trip_id's:
    check_trip_ids <- catch[!duplicated(catch$trip_id), , drop = FALSE]

If above reduces records from 'catch',...
To investigate:
  check_trip_ids <- catch[duplicated(catch$trip_id), , drop = FALSE]
    dup_trip_ids = check_trip_ids$trip_id
    check_trip_ids = catch %>% filter(trip_id %in% dup_trip_ids)
    
After much digging, several trips had records with the species of interest
and zero catch. This was throwing off the positive trips calculation (inflating it)
and throwing off balance the total trips returned. I filtered out 0 species
catch early in function to deal with this.

In addition, some trips go over a break between months or years, leading to
multiple records for a trip (2 years or 2 months or some combination). I set 
year and month to be the min year or month for a trip.

Note that records without a vessel registration number (for all of these there
is also no vessel name) are not included in the analysis as the fleet definition
is based on vessel reg number, year, trip id and catch. 2670 records removed (1,282,918 remain)

There are many records where the same vessel catches the same weight of the
same species multiple times in a month. This is in the merged catch and PacHarvHL
official catch tables, too. But may be worth checking the original catches to be sure.




