\newpage

# SHORTRAKER: MANAGEMENT PROCEDURE SPECIFICATIONS {#app:desc-mp-sr}

Use the management procedures that passed the screening test

```{r}
mpsr <- c("AvC", 
          "CC2", 
          "CC3",
          "DD", 
          "DD4010", 
          "GB_CC", 
          "GB_target",  
          "Islope1", 
          "Islope2",
          "Islope4", 
          "IT5", 
          "ITM", 
          "LstepCC2",
          "LstepCC3", 
          "LstepCC4", 
          "Ltarget1", 
          "Ltarget2", 
          "Ltarget3",
          "SBT2", 
          "SP_4010", 
          "SP_MSY")

#Group MPs into similar types
mpsr_group <- list()
mpsr_group[[1]] <- mpsr[1:3]
mpsr_group[[2]] <- mpsr[4:5]
mpsr_group[[3]] <- mpsr[6:7]
mpsr_group[[4]] <- mpsr[8:10]
mpsr_group[[5]] <- mpsr[c(11:12,19)]
mpsr_group[[6]] <- mpsr[13:15]
mpsr_group[[7]] <- mpsr[16:18]
mpsr_group[[8]] <- mpsr[20:21]

mptypenames <- c("Av Catch", "Delay Difference","Catch Target", "Index Slope", "Index Target","Stepwise Constant Catch", "Length Target","Surplus Production")

```


```{r, results='asis'}
csasdown::csas_table(MPtype(mpsr))
```

# SHORTRAKER: RESULTS 

## Constructing the operating model

Get the operating model. For Shortraker we are using the DLMtool operating model.


```{r echo = TRUE}
short_om <- readRDS(here::here("generated-data", "shortraker-om.rds"))
```

\newpage

Run the historical part of the MSE. 

```{r, fig.asp=0.8}

DLMtool::setup(cpus = parallel::detectCores())
short_om@nsim <- 50
short_historical <- runMSE(short_om, Hist = TRUE, parallel = TRUE, ntrials=1000)
short_om@nsim <- 200
#saveRDS(short_om,file="C:/GitHub/gfmp/generated-data/short_om.RDS")


real_catch <- read.csv(here::here("report/data/shortraker-corrected-catch.csv"))
real_catch <- mutate(real_catch, synthetic = ifelse(Year >= 1990 & Year <= 1995, Predicted.catch, Observed.catch))

all_years <- data.frame(Year = (2018 - fleet@nyears):2018)
real_catch <- dplyr::left_join(all_years, real_catch)

set.seed(1567)
catch <- short_historical@TSdata$Catch %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 11)) %>%
  transmute(sample_id = Var1, year = Var2 + min(real_catch$Year) - 1,
    catch = value, type = "Simulated") %>%
  bind_rows(data.frame(sample_id = 0, year = real_catch$Year,
    catch = real_catch$synthetic, type = "Observed", stringsAsFactors = FALSE))

catch %>%
  filter(!is.na(catch)) %>%
  group_by(sample_id) %>%
  mutate(catch = catch/max(catch)) %>%
  ggplot(aes(year, catch, colour = type)) +
  geom_line() +
  facet_wrap(~sample_id) +
  ylab("Historical catch") +
  xlab("Year")

short_historical@TSdata$B %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 12)) %>%
  ggplot(aes(Var2, value)) +
  geom_line() +
  facet_wrap(~Var1, scales = "free_y") +
  ylab("Simulated historical biomass") +
  xlab("Year")


```

\newpage

Look at the simulated biomass from a random set of replicates. 

```{r, fig.asp=0.8}
short_historical@TSdata$B %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 12)) %>%
  ggplot(aes(Var2, value)) +
  geom_line() +
  facet_wrap(~Var1, scales = "free_y") +
  ylab("Simulated historical biomass") +
  xlab("Year")
```

\newpage

Now run the closed loop simulation with the MPs above.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "shortraker-mse.rds")
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  short_mse <- runMSE(OM = short_om, MPs = mpsr, parallel = TRUE, ntrials=1000)
  saveRDS(short_mse, file = file_name)
} else {
  short_mse <- readRDS(file_name)
}
```

Check convergence. This is to test whether enough simulations have been run ... does the order of the MPs change across iterations? If so, increase the number of iterations.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
DLMtool::Converge(short_mse)
```

Seems to be okay.

*FIXME: Can't read the y axis labels*

\newpage

Now look to see if we have redundant MPs by plotting the range of catches across replicates for a subset of years. Each graph shows results from MPs of a similar "type". The group type is shown in the title of each graph. Robyn made up the group types.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
short_mse_C <- short_mse@C

nSim <- short_om@nsim
nYear <- ncol(short_mse_C[,1,]) 
nMP <- length(mpsr)
dimnames(short_mse_C) <- list(1:nSim, mpsr, 1:nYear)

#convert to data frame
z1 <- apply(short_mse_C, 3L, c)
z2 <- expand.grid(dimnames(short_mse_C)[1:2])
mp_catch_sr <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "Catch"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch from similar MPs for a subset of years
for(i in seq_along(mptypenames))
{
  mpgroup <- mpsr_group[[i]]
  ggcatch <- mp_catch_sr %>% 
    filter(MP %in% mpgroup) %>% 
    filter(Year %in% c(1,10,20,30,40,50)) %>%
    ggplot(aes(x=as.factor(Year),y=Catch,fill=MP))+
    geom_boxplot()+
    ggtitle(mptypenames[i]) + xlab("Year") + ylab("Catch")
  print(ggcatch)
} 

```


\newpage

It seems as if we have some redundancy among similar MPs based on the catch. Before removing MPs check biomass as well.


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
short_mse_SSB <- short_mse@SSB

nSim <- short_om@nsim
nYear <- ncol(short_mse_SSB[,1,]) 
nMP <- length(mpsr)
dimnames(short_mse_SSB) <- list(1:nSim, mpsr, 1:nYear)

#convert to data frame
z1 <- apply(short_mse_SSB, 3L, c)
z2 <- expand.grid(dimnames(short_mse_SSB)[1:2])
mp_ssb_sr <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "SBiomass"=value) %>% 
  mutate(Year=as.numeric(Year))

#Make boxplots of catch from similar MPs for a subset of years
for(i in seq_along(mptypenames))
{
  mpgroup <- mpsr_group[[i]]
  ggssb <- mp_ssb_sr %>% 
    filter(MP %in% mpgroup) %>% 
    filter(Year %in% c(1,10,20,30,40,50)) %>%
    ggplot(aes(x=as.factor(Year),y=SBiomass,fill=MP))+
    geom_boxplot()+
    ggtitle(mptypenames[i])+ xlab("Year")+ ylab("Spawning Biomass")
  print(ggssb)
} 

```


\newpage

We can remove some MPs to make comparison of results easier. Here is the shortlist.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
mpsr_short <- c("AvC",
                "SBT2",
                "DD4010", 
                "GB_CC", 
                "Islope1", 
                "IT5", 
                "LstepCC2",
                "Ltarget1", 
                "SP_MSY")
```

```{r, results='asis'}
csasdown::csas_table(MPtype(mpsr_short))
```

Rather than subsetting all the results, run the mse again on the shorter set. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "short-mse-short.rds")
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  short_mse_short <- runMSE(OM = short_om, MPs = mpsr_short, parallel = TRUE, ntrials=1000)
  saveRDS(short_mse_short, file = file_name)
} else {
  short_mse_short <- readRDS(file_name)
}
```


\newpage

Check basline states for performance metrics from the OM. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
library(reshape2)
bmsy_sr <- short_mse@OM$SSBMSY
USR_sr <- 0.8*bmsy_sr
LRP_sr <- 0.4*bmsy_sr
fmsy_sr <- short_mse@OM$FMSY
refY_sr <- short_mse@OM$RefY

baseline_names <- c("FMSY", "BMSY", "USR=0.8BMSY", "LRP=0.4BMSY","RefYield")

p <- baselines_sr <- as.data.frame(cbind(bmsy_sr,USR_sr,LRP_sr,refY_sr)) %>% 
  reshape2::melt() %>% 
  ggplot() + 
  geom_boxplot(aes(variable,value))+
  ylab("Simulated Value (tonnes)") +
  xlab("Baseline metric") +
  scale_x_discrete(labels=baseline_names[-1]) 
print(p)

p <- baselines_sr <- as.data.frame(fmsy_sr) %>% 
  reshape2::melt() %>% 
  ggplot() + 
  geom_boxplot(aes(variable,value))+
  ylab("Simulated Value (tonnes)") +
  xlab("Baseline metric") +
  scale_x_discrete(labels=baseline_names[1]) 
print(p)
  

```


\newpage

Get median values of baseline metrics (reference points).

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
med_fmsy_sr <- median(short_mse@OM$FMSY)
med_bmsy_sr <- median(short_mse@OM$SSBMSY)
med_USR_sr <- median(0.8*bmsy_sr)
med_LRP_sr <- median(0.4*bmsy_sr)
med_refY_sr <- median(short_mse@OM$RefY)

baseline_medians <- c(med_fmsy_sr, med_bmsy_sr,med_USR_sr,med_LRP_sr,med_refY_sr)
baseline_medians <- as.matrix(cbind(baseline_names, round(baseline_medians,3)))
colnames(baseline_medians) <- c("Metric", "Median")
knitr::kable(baseline_medians, format="markdown")

```


\newpage

Now look at Catch and Biomass results from the shortlist of MPs together. Biomass plot shows median LRP and USR as dashed lines.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
short_mse_SSB_short <- short_mse_short@SSB
short_mse_C_short <- short_mse_short@C

nSim <- short_om@nsim
nYear <- ncol(short_mse_SSB[,1,]) 
nMP <- length(mpsr_short)
dimnames(short_mse_SSB_short) <- list(1:nSim, mpsr_short, 1:nYear)
dimnames(short_mse_C_short) <- list(1:nSim, mpsr_short, 1:nYear)

#convert arrays to data frames
z1 <- apply(short_mse_C_short, 3L, c)
z2 <- expand.grid(dimnames(short_mse_C_short)[1:2])
mp_catch_sr_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "Catch"=value) %>% 
  mutate(Year=as.numeric(Year)) 

z1 <- apply(short_mse_SSB_short, 3L, c)
z2 <- expand.grid(dimnames(short_mse_SSB_short)[1:2])
mp_ssb_sr_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "SBiomass"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch and biomass from the short list of MPs 
ggcatch <- mp_catch_sr_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=Catch,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Catch")+ xlab("Year")+ ylab("Catch")
print(ggcatch)

ggssb2 <- mp_ssb_sr_short %>% 
filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=SBiomass,fill=MP))+
  geom_boxplot()+
  geom_hline(yintercept=med_USR_sr, linetype="dashed", color = "darkgreen")+
  geom_hline(yintercept=med_LRP_sr, linetype="dashed", color = "red")+
  ggtitle("Shortlist of MPs: Spawning Biomass")+ xlab("Year")+ ylab("Spawning Biomass")
print(ggssb2)

```


\newpage

All the MP give the same biomass results. Probably because the catch isn't touching the biomass really.


To check, look at Catch relative to RefY for each MP.The pink box in Year 1 shows the range of refY values from the OM, with the median shown as a dashed line.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
nSim <- short_om@nsim
RefYield_sr <- data.frame("Sim"=1:nSim, "MP"=rep("RefY",nSim),"Year"=rep(1,nSim),  "Catch"=short_mse_short@OM$RefY)

#Replace RefY with truncated set, just for plotting
RefYield_sr$Catch <- RefY_sr_trunc

#Make a new object so we don't accidentally keep appending to mp_catch_sr_short
mp_catch_sr_short2 <- rbind(mp_catch_sr_short,RefYield_sr)

ggcatch <- mp_catch_sr_short2 %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=Catch,fill=MP))+
  geom_boxplot()+
  geom_hline(yintercept=med_refY_sr, linetype="dashed", color = "black")+
  ggtitle("Shortlist of MPs: Catch showing ref yield")+ xlab("Year")+ ylab("Catch") +
print(ggcatch)


```


\newpage

Look at Catch/RefY for each MP.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
#For each MP and sim need to divide Catch by annual RefY
RefYield <- short_mse_short@OM$RefY
RefYieldRep <- rep(RefYield,nMP*nYear)
mp_catch_sr_shortRel <- mp_catch_sr_short %>% 
  mutate("RefY"=RefYieldRep,"CatchRelRefY"=Catch/RefYieldRep)

ggcatch <- mp_catch_sr_shortRel %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=CatchRelRefY,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Catch relative to RefY")+ xlab("Year")+ ylab("Relative Catch")  
print(ggcatch)

```


Perhaps we need to be able to set RefY to an agreed reference value. The OM thinks the stock is very productive. 


\newpage

Look at projected fishing mortality. This is odd. The DD4010 MP produces much higher F than any other MP, yet the biomass is the same across all MPs and catches are the same as the AvC MP, which doesn't have such high F.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
short_mse_F_short <- short_mse_short@FM
dimnames(short_mse_F_short) <- list(1:nSim, mpsr_short, 1:nYear)

#convert arrays to data frames
z1 <- apply(short_mse_F_short, 3L, c)
z2 <- expand.grid(dimnames(short_mse_F_short)[1:2])
mp_F_sr_short <- data.frame(z2, z1) %>% 
  reshape2::melt() %>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "FM"=value) %>% 
  mutate(Year=as.numeric(Year)) 

#Make boxplots of catch and biomass from the short list of MPs 
ggF <- mp_F_sr_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=FM,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: Fishing Mortality")+ xlab("Year")+ ylab("Fishing Mortality")
print(ggF)

```


\newpage

Look at B/BMSY trajectories under each MP. They seem identical for each MP.

<!--- Try Cowplot grid version, hard to read but could lay it out better

```{r}
short_mse_BBMSY_short <- short_mse_short@B_BMSY
dim(short_mse_BBMSY_short) #dimensions of array are 1:nSim, 1:nMP, 1:nYear

#USR_sr

#Give names to the array so they can be used for plotting
dimnames(short_mse_BBMSY_short) <- list(1:nSim, mpsr_short, 1:nYear)

gg <- list()
lapply(1:nMP, function(x){
 tmp <- short_mse_BBMSY_short[,x,] %>% 
   reshape2::melt() 
   gg[[x]] <<- ggplot(tmp, aes(x=as.factor(Var2),y=value)) +
   geom_boxplot() +
   xlab("Year")+ ylab("B/BMSY") 
})
cowplot::plot_grid(plotlist=gg)

```
--->


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
short_mse_BBMSY_short <- short_mse_short@B_BMSY
dim(short_mse_BBMSY_short) #dimensions of array are 1:nSim, 1:nMP, 1:nYear

#Give names to the array so they can be used for plotting
nSim <- short_om@nsim
nYear <- ncol(short_mse_BBMSY_short[,1,]) #find global parameter for number of projection years
dimnames(short_mse_BBMSY_short) <- list(c(1:nSim), mpsr_short, 1:nYear)

#convert to data frame and plot
z1 <- apply(short_mse_BBMSY_short, 3L, c)
z2 <- expand.grid(dimnames(short_mse_BBMSY_short)[1:2])
mp_bbmsy_sr_short <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "BBMSY"=value) %>% 
  mutate(Year=as.numeric(Year)) 

p <-  filter(mp_bbmsy_sr_short, MP %in% mpsr_short[1:4]) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY))+
  geom_boxplot()+
  facet_grid(rows=vars(MP)) + xlab("Year")+ ylab("B/BMSY") 
print(p)

p1 <-  filter(mp_bbmsy_sr_short, MP %in% mpsr_short[5:8]) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY))+
  geom_boxplot()+
  facet_grid(rows=vars(MP)) + xlab("Year")+ ylab("B/BMSY") 
print(p1)

```


\newpage

Make the subsetted years version of the B/BMSY and F/FMSY plots. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
short_mse_FFMSY_short <- short_mse_short@F_FMSY
dim(short_mse_FFMSY_short) #dimensions of array are 1:nSim, 1:nMP, 1:nYear
dimnames(short_mse_FFMSY_short) <- list(c(1:nSim), mpsr_short, 1:nYear)

#convert to data frame and plot
z1 <- apply(short_mse_FFMSY_short, 3L, c)
z2 <- expand.grid(dimnames(short_mse_FFMSY_short)[1:2])
mp_ffmsy_sr_short <- data.frame(z2, z1) %>% 
  reshape2::melt()%>% 
  rename("Sim"=Var1,"MP"=Var2,"Year"=variable, "FFMSY"=value) %>% 
  mutate(Year=as.numeric(Year)) 


ggb <- mp_bbmsy_sr_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=BBMSY,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: B/BMSY")+ xlab("Year")+ ylab("B/BMSY")  
print(ggb)

ggf <- mp_ffmsy_sr_short %>% 
  filter(Year %in% c(1,10,20,30,40,50)) %>%
  ggplot(aes(x=as.factor(Year),y=FFMSY,fill=MP))+
  geom_boxplot()+
  ggtitle("Shortlist of MPs: F/FMSY")+ xlab("Year")+ ylab("F/FMSY")  
print(ggf)

```

\newpage

Dig into some results further ... like what is going on with the delay difference model (DD4010)? Show four metrics for all MPs.


```{r, fig.asp=1.9, out.width = "4.8in", fig.width=7}
library(dplyr)
library(RColorBrewer)
nmp <- data.frame(mp = seq_along(short_mse_short@MPs), mp_name = short_mse_short@MPs)

ffmsy <- short_mse_short@F_FMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value, year = Var3)
bbmsy <- short_mse_short@B_BMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value, year = Var3)
cat <- short_mse_short@C[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, catch = value, year = Var3)
biomass <- short_mse_short@SSB[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, Biomass = value, year = Var3)
d <- dplyr::inner_join(ffmsy, bbmsy) 
d <- dplyr::inner_join(d, cat) 
d <- dplyr::inner_join(d, biomass)
d <- dplyr::left_join(d, nmp)
d <- reshape2::melt(d, id.vars = c("iter", "mp", "year", "mp_name"))
levels(d$variable) <- c(expression(F/F[MSY]), expression(B/B[MSY]), expression(Catch), expression(Biomass))

d_median <- d %>% group_by(mp_name, year, variable) %>%
  summarise(median_value = median(value)) %>%
  mutate(iter = NA)

d_last <- dplyr::filter(d, year == max(year)) %>%
  select(-year) %>%
  rename(last_value = value)
d <- inner_join(d, d_last)

cols <- brewer.pal(3, "RdBu")
cols[2] <- "grey80"

plot_timeseries <- function(dat, dat_median, title = "",
  ylim = c(0, fudge), cols, values, labels = TRUE, yaxis = TRUE) {
  g <- ggplot(dat, aes_string("year", "value", group = "iter")) +
    geom_line(aes_string(colour = "last_value"), alpha = 0.3) +
    facet_grid(mp_name~., labeller = label_parsed) +
    ggsidekick::theme_sleek() +
    scale_colour_gradientn(colours = cols,
      values = values) +
    geom_line(data = dat_median, aes_string("year", "median_value"),
      colour = "black", lwd = 1.5) +
    ylim(ylim[1], ylim[2]) +
    ggtitle(title) +
    guides(colour = FALSE) +
    ylab("Value") + xlab("Year")

  if (!labels)
    g <- g + theme(strip.background = element_blank(),
      strip.text.y = element_blank())

  if (!yaxis)
    g <- g + theme(axis.text.y = element_blank())
  g
}

cols <- brewer.pal(5, "RdBu")
cols <- c(cols[1], "grey50", cols[length(cols)])
set.seed(42)
# d_ <- filter(d, iter %in% sample(seq_len(max(d$iter)), 30))
d_ <- d

maxC <- d_ %>% 
  dplyr::filter(variable=="Catch") %>% 
  select(value) %>% 
  max()

maxB <- d_ %>% 
  dplyr::filter(variable=="Biomass") %>% 
  select(value) %>% 
  max()

#
mps <- unique(d_$mp_name)
# mps <- mps[-which(mps %in% c("CC4"))]
p1 <- plot_timeseries(filter(d_, variable == "B/B[MSY]", mp_name %in% mps),
  filter(d_median, variable == "B/B[MSY]", mp_name %in% mps), expression(B/B[MSY]),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,5))
p2 <- plot_timeseries(filter(d_, variable == "F/F[MSY]", mp_name %in% mps),
  filter(d_median, variable == "F/F[MSY]", mp_name %in% mps), expression(F/F[MSY]),
  cols = cols, values = scales::rescale(c(5, 1.2, 0.8, 0)),
  labels = TRUE, ylim = c(0,5), yaxis = TRUE)
p3 <- plot_timeseries(filter(d_, variable == "Catch", mp_name %in% mps),
  filter(d_median, variable == "Catch", mp_name %in% mps), expression(Catch),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxC))
p4 <- plot_timeseries(filter(d_, variable == "Biomass", mp_name %in% mps),
  filter(d_median, variable == "Biomass", mp_name %in% mps), expression(Biomass),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxB))

gridExtra::grid.arrange(p4,p3,  p1, p2, ncol = 4)

#########3
ffmsy <- short_mse_short@F_FMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value, year = Var3)
bbmsy <- short_mse_short@B_BMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value, year = Var3)
d <- dplyr::inner_join(ffmsy, bbmsy)
d <- dplyr::left_join(d, nmp)
d <- reshape2::melt(d, id.vars = c("iter", "mp", "year", "mp_name"))
levels(d$variable) <- c(expression(F/F[MSY]), expression(B/B[MSY]))

d_sum <- d %>% group_by(mp_name, year, variable) %>%
  summarise(median_value = median(value),
    l = quantile(value, probs = 0.75),
    u = quantile(value, probs = 0.25),
    ll = quantile(value, probs = 0.95),
    uu = quantile(value, probs = 0.05))

d <- inner_join(d, d_last)

cols <- brewer.pal(5, "RdBu")
cols <- c(cols[1], "grey50", cols[length(cols)])
g <- ggplot(d_sum, aes_string("year", "median_value")) +
  facet_grid(mp_name~variable, labeller = label_parsed) +
  geom_ribbon(aes(ymin = ll, ymax = uu), fill = "grey90") +
  geom_ribbon(aes(ymin = l, ymax = u), fill = "grey70") +
  ggsidekick::theme_sleek() +
  geom_line(lwd = 1.5) +
  #coord_cartesian(ylim = c(0, 4)) +
  guides(colour = FALSE) +
  xlim(25, 50) +
  geom_hline(yintercept = 1,
    col = "black", lty = 2) +
  ylab("Value") + xlab("Year")
  
g
```

\newpage

This result is confusing. Isolate DD4010 and AvC. Why is F/FMSY different between the DD4010 and AvC MPs  when catch and biomass look identical?

```{r, fig.asp=1.9, out.width = "4.8in", fig.width=7}
mps <-  c("AvC", "SBT2", "DD4010")
p1 <- plot_timeseries(filter(d_, variable == "B/B[MSY]", mp_name %in% mps),
  filter(d_median, variable == "B/B[MSY]", mp_name %in% mps), expression(B/B[MSY]),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,10))
p2 <- plot_timeseries(filter(d_, variable == "F/F[MSY]", mp_name %in% mps),
  filter(d_median, variable == "F/F[MSY]", mp_name %in% mps), expression(F/F[MSY]),
  cols = cols, values = scales::rescale(c(5, 1.2, 0.8, 0)),
  labels = TRUE, ylim = c(0,10), yaxis = TRUE)
p3 <- plot_timeseries(filter(d_, variable == "Catch", mp_name %in% mps),
  filter(d_median, variable == "Catch", mp_name %in% mps), expression(Catch),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxC))
p4 <- plot_timeseries(filter(d_, variable == "Biomass", mp_name %in% mps),
  filter(d_median, variable == "Biomass", mp_name %in% mps), expression(Biomass),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, 5)),
  labels = TRUE, ylim = c(0,maxB))

gridExtra::grid.arrange(p4, p3, p2, nrow = 3)



```

\newpage

Look at the proportions at age. DLMtool doesn't output annual age comps so plot CAA for the first 16 reps. For now assume this is the CAA in the final year? Plots 1-2 show the MPs AvC and DD4010. They seem to be identical as well.

AvC:

```{r}
nAge <- dim(short_mse_short@CAA)[3]

#For each MP short_mse_short@CAA contains nSim rows of nAge proportions
#Let's assume each replicate shows the final CAA
MSEtool::plot_composition(1:16, obs=short_mse_short@CAA[1:16,1,])

```

DD4010:

```{r}
#For each MP short_mse_short@CAA contains nSim rows of nAge proportions
#Let's assume each replicate shows the final CAA
MSEtool::plot_composition(1:16, obs=short_mse_short@CAA[1:16,2,])


```



DD4010:

```{r}
#For each MP short_mse_short@CAA contains nSim rows of nAge proportions
#Let's assume each replicate shows the final CAA
MSEtool::plot_composition(1:16, obs=short_mse_short@CAA[1:16,3,])


```

\newpage

Show probabilities of meeting performance metrics

```{r probability-table-abs-sr, fig.width = 9, fig.asp = 1, out.width = "4in"}
probs <- gfdlm:::get_probs(short_mse_short, PMlist = c("P40", "P80","P100", "PNOF", "AAVY", "LTY"))
plot_probs(probs)
```

\newpage
Show radar plot. They all do more or less the same. DD is worst. I think we should remove this from the MPs. Delay-difference models are not data-limited and have too many decisions to throw into our toolkit of simple models. Plus it is behaving strangelY.

```{r}
library(ggspider)
pm_probs <- gfdlm:::eval_pm(short_mse_short,
             pm_list = list("LTY",
                            "P10",
                            "P40",
                            "P80",
                            "P100",
                            "PNOF",
                            "AAVY")) 

#r_plot(x, fill_polys = TRUE, inc_yrs = FALSE)
ggspider::spider_web(pm_probs, "mp", "pm", "prob")


```



\newpage


Illustrating the built-in plotting functions:

```{r}
Tplot(short_mse_short)
Tplot2(short_mse_short)
```



```{r}
summary(short_mse_short)
```



```{r}
wormplot(short_mse_short)
```

```{r}
Pplot(short_mse_short)

```

```{r}
Pplot2(short_mse_short, traj="quant", quants=c(0.2, 0.8))
```

```{r}
Kplot(short_mse_short)
```

```{r}
Cplot(short_mse_short)
```

And examine the output.


```{r, fig.asp=1}
yend <- max(short_mse_short@proyears)
ffmsy <- short_mse_short@F_FMSY[,,yend]
bbmsy <- short_mse_short@B_BMSY[,,yend]

ffmsy <- reshape2::melt(ffmsy) %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value)
bbmsy <- reshape2::melt(bbmsy) %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value)

d <- dplyr::inner_join(ffmsy, bbmsy)

n <- data.frame(mp = seq_along(short_mse_short@MPs), mp_name = short_mse_short@MPs)
# n$mp_name <- paste(1:nrow(n), n$mp_name)

d <- dplyr::left_join(d, n)

library(ggplot2)
p <- ggplot(dplyr::filter(d, !mp_name %in% c("NFref")), aes(bbmsy, ffmsy)) +
  geom_vline(xintercept = c(0.4, 0.8), alpha = 0.2) +
  geom_hline(yintercept = 1, alpha = 0.2) +
  geom_density_2d(aes(colour = ..level..), bins = 5) +
  viridis::scale_colour_viridis() +
  ggsidekick::theme_sleek() +
  facet_wrap(~mp_name) +
  ylim(0, 3.5) + xlim(0, 3.5) +
  geom_point(alpha = 0.2) +
  labs(colour = "Prob. density", x = expression(B/B[MSY]),
    y = expression(F/F[MSY])) +
  guides(colour = FALSE)
print(p)
#ggsave("analysis/short-bbmsy-ffmsy-multi.pdf", width = 8, height = 8)
```

```{r}
 plot(short_mse_short)
 oldpar <- par()
##DFO_hist(short_mse)
par(mfrow = c(1, 1))
DFO_plot(short_mse_short)
# DFO_plot2(short_mse)
```

```{r, fig.asp=1, warning=FALSE}
DFO_proj(short_mse_short)
#DFO_hist(short_om)
# DFO_plot2(short_mse)

# d <- DFO_plot2(short_mse)
# ggplot(d, aes(B50/100, LTY/100, label = MPs, colour = Satisfice)) +
#   geom_vline(xintercept = 0.5, col = "grey50") +
#   geom_hline(yintercept = 0.5, col = "grey50") +
#   geom_text() + ggsidekick::theme_sleek() +
#   scale_colour_manual(values = c("grey60", "black")) +
#   guides(colour = FALSE) +
#   xlab(expression(Pr(B>0.5~B[MSY]))) +
#   ylab(expression(Pr(yield>0.5~yield~at~F[MSY]))) +
#   xlim(0, 1) + ylim(0, 1)
par(oldpar)
```

```{r, fig.asp=1.2}
voi_out <- DLMtool::VOI(short_mse_short)
```
