\newpage

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
source(here::here("sra/sra-data-rex.R"))
```


# REX SOLE: MANAGEMENT PROCEDURE SPECIFICATIONS {#app:desc-mp-rex}

Use the management procedures that passed the screening test

```{r}
mprex <- c(
  "AvC",
  "CC2",
  "CC3",
  "DD",
  "DD4010",
  "GB_CC",
  "GB_target",
  "Islope1",
  "Islope2",
  "Islope4",
  "IT5",
  "ITM",
  "LstepCC2",
  "LstepCC3",
  "LstepCC4",
  "Ltarget1",
  "Ltarget2",
  "Ltarget3",
  "SBT2",
  "SP_4010",
  "SP_MSY"
)

# Group MPs into similar types
# mprex_group <- list()
# mprex_group[[1]] <- mprex[1:3]
# mprex_group[[2]] <- mprex[4:5]
# mprex_group[[3]] <- mprex[6:7]
# mprex_group[[4]] <- mprex[8:10]
# mprex_group[[5]] <- mprex[c(11:12,19)]
# mprex_group[[6]] <- mprex[13:15]
# mprex_group[[7]] <- mprex[16:18]
# mprex_group[[8]] <- mprex[20:21]
#
# mptypenames <- c("Av Catch", "Delay Difference","Catch Target", "Index Slope", "Index Target","Stepwise Constant Catch", "Length Target","Surplus Production")
```

# REX SOLE: RESULTS 

Get the operating model. For Shortraker we are using the DLMtool operating model.

```{r echo = TRUE}
omrex <- readRDS(here::here("generated-data", "rex-om-sra.rds"))
```

How well does the SRA OM fit the indices?

```{r}

rex_SRA_report <- readRDS(here::here("generated-data/rex-sra-report.rds"))

catch <- drex$catch %>%
    gfplot::tidy_catch() %>%
    group_by(year) %>%
    summarize(value = sum(value)) %>%
    right_join(tibble(year = all_years), by = "year") %>%
    pull(value)

indexes <- drex$survey_index %>%
  dplyr::filter(survey_abbrev %in% c("SYN WCVI")) %>%
  select(year, biomass, re) %>%
  right_join(tibble(year = all_years), by = "year") %>%
  # left_join(rename(select(cpue, year, est), trawl_cpue = est), by = "year") %>%
  select(-year) %>%
  as.matrix()

MSEtool:::plot_SRA_scope(omrex, Chist = matrix(catch, ncol = 1), Index=indexes[,1], report = rex_SRA_report)
```

\newpage

Run the historical part of the MSE. 

```{r, fig.asp=0.8, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}
DLMtool::setup(cpus = parallel::detectCores())
rex_historical <- runMSE(omrex, Hist = TRUE, parallel = TRUE, ntrials = 1000)
snowfall::sfStop()

# real_catch <- read.csv(here::here("report/data/shortraker-corrected-catch.csv"))
# real_catch <- mutate(real_catch, synthetic = ifelse(Year >= 1990 & Year <= 1995, Predicted.catch, Observed.catch))
#
all_years <- fleet_rex@EffYears
# real_catch <- dplyr::left_join(all_years, real_catch)

# set.seed(1567)
catch <- rex_historical@TSdata$Catch %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 100)) %>%
  transmute(
    sample_id = Var1, year = Var2 + min(all_years) - 1,
    catch = value, type = "Simulated"
  ) # %>%
# bind_rows(data.frame(sample_id = 0, year = real_catch$Year,
#   catch = real_catch$synthetic, type = "Observed", stringsAsFactors = FALSE))

library(ggplot2)
catch %>%
  filter(!is.na(catch)) %>%
  group_by(sample_id) %>%
  mutate(catch = catch / max(catch)) %>%
  ggplot(aes(year, catch, colour = type, group = sample_id)) +
  geom_line() +
  # facet_wrap(~sample_id) +
  ylab("Historical catch") +
  xlab("Year")

# Look at the simulated biomass from a random set of replicates.
rex_historical@TSdata$B %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 100)) %>%
  ggplot(aes(Var2, value, group = Var1)) +
  geom_line() +
  # facet_wrap(~Var1, scales = "free_y") +
  ylab("Simulated historical biomass") +
  xlab("Year")

# Look at historical length composition data:
names(rex_historical@TSdata)
rex_historical@Data@CAL_bins
dim(rex_historical@Data@CAL)
rex_historical@Data@CAL[1, , ]

bins <- rex_historical@Data@CAL_bins
bins <- bins[-length(bins)]

omrex@CAL_nsamp
omrex@CAL_ESS
x <- rex_historical@Data@CAL %>%
  reshape2::melt() %>%
  transmute(
    sample_id = Var1, year = Var2 + min(all_years) - 1,
    count = value, type = "Simulated"
  ) %>%
  mutate(length_bin = rep(bins, each = max(sample_id) * length(all_years)))

filter(x, year %in% seq(1995, 2020, 5)) %>%
  filter(sample_id %in% sample.int(150, 7)) %>%
  ggplot(aes(length_bin, count)) +
  geom_col() +
  facet_grid(year ~ sample_id)
```


Now run the closed loop simulation with the MPs.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "rex-mse.rds")
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  rex_mse <- runMSE(OM = omrex, MPs = mprex, parallel = TRUE, ntrials = 1000)
  snowfall::sfStop()
  saveRDS(rex_mse, file = file_name)
} else {
  rex_mse <- readRDS(file_name)
}
```

Check convergence. This is to test whether enough simulations have been run ... does the order of the MPs change across iterations? If so, increase the number of iterations.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
DLMtool::Converge(rex_mse)
```

Look at probabilities of performance metrics.

```{r probability-table-abs-rex, fig.width = 9, fig.asp = 1, out.width = "4in"}
STY <- gfdlm:::pm_factory("LTY", 0.5, c(6, 20))
LTY <- gfdlm:::pm_factory("LTY", 0.5, c(36, 50))

PM <- c("P40_yrs36_50", "P80_yrs36_50", "STY", "LTY", "AAVY", "PNOF")

probs <- gfdlm:::get_probs(rex_mse, PMlist = as.list(PM))
plot_probs(probs)
```

```{r probability-table-0-1-rex, fig.width = 9, fig.asp = 1, out.width = "4in"}
# plot_probs(probs, scale_0_1 = TRUE)
```

Which MPs are considered "satisficed"? Right now the only satisficing criteria is that long-term probability of the stock not being in the critical zone is greater than or equal to 75%.

```{r}
x <- gfdlm:::eval_pm(rex_mse,
  pm_list = as.list(PM)
) %>% select(mp, pm, prob)
satisficed <- dplyr::filter(probs, P40_yrs36_50 >= 0.70) %>% pull(MP)
satisficed
```


How does it look if we increase the probability to 75%?
```{r}
x <- gfdlm:::eval_pm(rex_mse,
  pm_list = as.list(PM)
) %>% select(mp, pm, prob)
satisficed75 <- dplyr::filter(probs, P40_yrs36_50 >= 0.75) %>% pull(MP)
satisficed75
```

How about 95%?
```{r}
x <- gfdlm:::eval_pm(rex_mse,
  pm_list = as.list(PM)
) %>% select(mp, pm, prob)
satisficed95 <- dplyr::filter(probs, P40_yrs36_50 >= 0.95) %>% pull(MP)
satisficed95
```

Only DD410

For now, stick with 70%. Look at the simulated trajectories of the satisficed MPs

```{r, echo=FALSE}
set.seed(1)
rex_mse_satisficed <- Sub(rex_mse, MPs=satisficed)
plot_projection_ts(rex_mse_satisficed)
```

Look at trade-offs of the satisficed MPs

```{r, echo=FALSE}
xx <- dplyr::filter(x, mp %in% satisficed)
ggspider::spider_web(xx, "mp", "pm", "prob")
```

Illustrating some built-in plotting functions:


These have DFO zones on them

```{r}
DFO_plot(rex_mse_satisficed)

```



```{r}

DFO_proj(rex_mse_satisficed)

```


These could be modified to show DFO zones



```{r}
wormplot(rex_mse_satisficed)
```


```{r}
Pplot2(rex_mse_satisficed, traj="quant", quants=c(0.2, 0.8))
```

```{r}
Kplot(rex_mse_satisficed)
```


