\newpage

# PACIFIC COD: MANAGEMENT PROCEDURE SPECIFICATIONS {#app:desc-mp-sr}

For now pick out some measure procedures that look plausible for our data. The next step is to run our data through the data conversion function and run `DLMtool::can()`. FIXME

```{r}
mppc <- c("AvC", "CC2", "CC3", "GB_CC", "GB_target", "Islope1", "Islope2",
"Islope4", "IT5", "ITM", "LstepCC2", "Ltarget1", "SBT2")
mppc <- sort(mppc)

#Group MPs into similar types
mppcg1 <- mppc[1:3]
mppcg2 <- mppc[4:5]
mppcg3 <- mppc[6:8]
mppcg4 <- mppc[9:10]
mppcg5 <- mppc[11:12]
mppcg6 <- mppc[11:12]

```


```{r, results='asis'}
csasdown::csas_table(MPtype(mppc))
```




# PACIFIC COD: RESULTS 

## Constructing the operating model

First, let's combine the stock, fleet, observation, and mp objects into a complete operating model:


```{r}
#avail("Output")
#avail("Reference")
```

```{r echo = TRUE}
#ompc <- new('OM', stockpc, fleetpc, obspc, imppc)

#Use OM that was made in sra-data-pcod.R 
ompc <- readRDS(here::here("sra/pcod_no_comps_om.rds"))

ompc@nsim <- 48L
```

```{r, eval=TRUE, fig.asp=1}
oldparpc <- par()
plotStock(ompc, nsamp = 3, incVB = TRUE)
```

```{r, eval=TRUE}
plotSelect(ompc, sim = 1) # one sample, others will look different
```

```{r, eval=TRUE, fig.asp=1}
plotFleet(fleetpc, Stock = stockpc)
```

```{r, eval=TRUE, fig.asp=1}
plotImp(imppc)
```

```{r, eval=TRUE, fig.asp=0.8}
plotObs(obspc)
```

csasdown::csas_table(MPtype(mppc))
```{r, fig.asp=0.8}

DLMtool::setup(cpus = parallel::detectCores())
ompc@nsim <- 150
pcod_historical <- runMSE(ompc, Hist = TRUE, parallel = TRUE, ntrials=1000)
ompc@nsim <- 250L #Why is this set again?
#saveRDS(ompc,file="C:/GitHub/gfmp/generated-data/ompc.RDS")

# names(pcod_historical@TSdata)
# dim(pcod_historical@TSdata$Catch)

real_catchpc <- read.csv(here::here("report/data/pcod-corrected-catch.csv"))
real_catchpc <- mutate(real_catchpc, synthetic = real_catchpc$Observed.catch) #Don't use predicted catchpc for P cod

all_years <- data.frame(Year = (2018 - fleetpc@nyears):2018)
real_catchpc <- dplyr::left_join(all_years, real_catchpc)

set.seed(1938)
catchpc <- pcod_historical@TSdata$Catch %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 11)) %>%
  transmute(sample_id = Var1, year = Var2 + min(real_catchpc$Year) - 1,
    catchpc = value, type = "Simulated") %>%
  bind_rows(data.frame(sample_id = 0, year = real_catchpc$Year,
    catchpc = real_catchpc$synthetic, type = "Observed", stringsAsFactors = FALSE))

catchpc %>%
  filter(!is.na(catchpc)) %>%
  group_by(sample_id) %>%
  mutate(catchpc = catchpc/max(catchpc)) %>%
  ggplot(aes(year, catchpc, colour = type)) +
  geom_line() +
  facet_wrap(~sample_id) +
  ylab("Historical catch") +
  xlab("Year")


```

Here is the simulated biomass

```{r, fig.asp=0.8}
pcod_historical@TSdata$B %>%
  reshape2::melt() %>%
  dplyr::filter(Var1 %in% sample(unique(Var1), size = 12)) %>%
  ggplot(aes(Var2, value)) +
  geom_line() +
  facet_wrap(~Var1, scales = "free_y") +
  ylab("Simulated historical biomass") +
  xlab("Year")
```


Now we can run closed-loop simulation:

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
file_name <- here::here("generated-data", "pcod-mse.rds")
if (!file.exists(file_name)) {
  DLMtool::setup(cpus = parallel::detectCores())
  pcod_mse <- runMSE(OM = ompc, MPs = mppc, parallel = TRUE, ntrials=1000)
  saveRDS(pcod_mse, file = file_name)
} else {
  pcod_mse <- readRDS(file_name)
}
```

Check convergence:

```{r}
DLMtool::Converge(pcod_mse)
```


Check basline states for performance metrics from th OM. We want to see OM-simulated FMSY, BMSY and reference Yield

```{r}
library(reshape2)
bmsy_pc <- pcod_mse@OM$SSBMSY
bmsy80_pc <- 0.8*bmsy_pc
bmsy40_pc <- 0.4*bmsy_pc
fmsy_pc <- pcod_mse@OM$FMSY
refY_pc <- pcod_mse@OM$RefY

baseline_names <- c("FMSY", "BMSY", "0.8BMSY", "0.4BMSY","RefYield")

p <- baselines_pc <- as.data.frame(cbind(bmsy_pc,bmsy80_pc,bmsy40_pc,refY_pc)) %>% 
  reshape2::melt() %>% 
  ggplot() + 
  geom_boxplot(aes(variable,value))+
  ylab("Simulated Value (tonnes)") +
  xlab("Baseline metric") +
  scale_x_discrete(labels=baseline_names[-1]) 
print(p)
  

```

Get median values

```{r}
med_fmsy_pc <- median(pcod_mse@OM$FMSY)
med_bmsy_pc <- median(pcod_mse@OM$SSBMSY)
med_bmsy80_pc <- median(0.8*bmsy_pc)
med_bmsy40_pc <- median(0.4*bmsy_pc)
med_refY_pc <- median(pcod_mse@OM$RefY)

baseline_medians <- c(med_fmsy_pc, med_bmsy_pc,med_bmsy80_pc,med_bmsy40_pc,med_refY_pc)
baseline_medians <- as.matrix(cbind(baseline_names, round(baseline_medians,3)))
colnames(baseline_medians) <- c("Metric", "Median")
knitr::kable(baseline_medians, format="markdown")

```

Look at B/BMSY trajectories under each MP

```{r}
bbmsy_pcod <- pcod_mse@B_BMSY
dim(bbmsy_pcod) #dimensions of array are 1:nSim, 1:nMP, 1:nYear

#Give names to the array so they can be used for plotting
nSim <- ompc@nsim
nYear <- ncol(bbmsy_pcod[,1,]) #find global parameter for number of projection years
nMP <- length(mppc)
#dimnames(bbmsy_pcod) <- list(paste0("Sim",1:nSim), mppc, 1:nYear)
dimnames(bbmsy_pcod) <- list(1:nSim, mppc, 1:nYear)

gg <- list()
lapply(1:nMP, function(x){
 tmp <- bbmsy_pcod[,x,] %>% 
   melt()  
   gg[[x]] <<- ggplot(tmp, aes(x=as.factor(Var2),y=value)) +
   geom_boxplot()
})
cowplot::plot_grid(plotlist=gg)


```


```{r}
bbmsy_pcod <- pcod_mse@B_BMSY
dim(bbmsy_pcod) #dimensions of array are 1:nSim, 1:nMP, 1:nYear

#Give names to the array so they can be used for plotting
nSim <- ompc@nsim
nYear <- ncol(bbmsy_pcod[,1,]) #find global parameter for number of projection years
dimnames(bbmsy_pcod) <- list(c(1:nSim), mppc, 1:nYear)

#convert to data frame and plot
z1 <- apply(bbmsy_pcod, 3L, c)
z2 <- expand.grid(dimnames(bbmsy_pcod)[1:2])
z3 <- data.frame(z2, z1) %>% 
  melt() 

#TODO: PLOT NEEDS LAYING OUT PROPERLY
#FIXME: why are they all the same? The MSE results don't vary over MPs ???
p <-  filter(z3, Var2 %in% mppc[1:4]) %>%
  ggplot(aes(x=variable,y=value,z=Var2))+
  geom_boxplot()+
  facet_grid(rows=vars(Var2))
print(p)

p1 <-  filter(z3, Var2 %in% mppc[5:8]) %>%
  ggplot(aes(x=variable,y=value,z=Var2))+
  geom_boxplot()+
  facet_grid(rows=vars(Var2))
print(p1)

p2 <-  filter(z3, Var2 %in% mppc[9:13]) %>%
  ggplot(aes(x=variable,y=value,z=Var2))+
  geom_boxplot()+
  facet_grid(rows=vars(Var2))
print(p2)


```


Show probabilities of meeting performance metrics

```{r probability-table-abs-pc, fig.width = 9, fig.asp = 1, out.width = "4in"}
probs <- gfdlm:::get_probs(pcod_mse, PMlist = c("P40", "P80", "PNOF", "AAVY", "LTY"))
plot_probs(probs)
```



```{r}
Tplot(pcod_mse)
Tplot2(pcod_mse)
```



```{r}
summary(pcod_mse)
```

Illustrating the built-in plotting functions:

```{r}
wormplot(pcod_mse)
```

```{r}
Pplot(pcod_mse)

```

```{r}
Pplot2(pcod_mse, traj="quant", quants=c(0.2, 0.8))
```

```{r}
Kplot(pcod_mse)
```

```{r}
Cplot(pcod_mse)
```

And examine the output.

```{r}
 plot(pcod_mse)
 oldpar <- par()
##DFO_hist(pcod_mse)
par(mfrow = c(1, 1))
DFO_plot(pcod_mse)
# DFO_plot2(pcod_mse)
```

```{r, fig.asp=1, warning=FALSE}
DFO_proj(pcod_mse)
#DFO_hist(pcod_om)
# DFO_plot2(pcod_mse)

# d <- DFO_plot2(pcod_mse)
# ggplot(d, aes(B50/100, LTY/100, label = MPs, colour = Satisfice)) +
#   geom_vline(xintercept = 0.5, col = "grey50") +
#   geom_hline(yintercept = 0.5, col = "grey50") +
#   geom_text() + ggsidekick::theme_sleek() +
#   scale_colour_manual(values = c("grey60", "black")) +
#   guides(colour = FALSE) +
#   xlab(expression(Pr(B>0.5~B[MSY]))) +
#   ylab(expression(Pr(yield>0.5~yield~at~F[MSY]))) +
#   xlim(0, 1) + ylim(0, 1)
par(oldpar)
```

The following are some plots I was playing with a long time ago. We should wrap the useful ones into their own functions in our package.

```{r, fig.asp=1}
yend <- max(pcod_mse@proyears)
ffmsy <- pcod_mse@F_FMSY[,,yend]
bbmsy <- pcod_mse@B_BMSY[,,yend]

ffmsy <- reshape2::melt(ffmsy) %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value)
bbmsy <- reshape2::melt(bbmsy) %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value)

d <- dplyr::inner_join(ffmsy, bbmsy)

n <- data.frame(mp = seq_along(pcod_mse@MPs), mp_name = pcod_mse@MPs)
# n$mp_name <- paste(1:nrow(n), n$mp_name)

d <- dplyr::left_join(d, n)

library(ggplot2)
ggplot(dplyr::filter(d, !mp_name %in% c("NFref")), aes(bbmsy, ffmsy)) +
  geom_vline(xintercept = c(0.4, 0.8), alpha = 0.2) +
  geom_hline(yintercept = 1, alpha = 0.2) +
  geom_density_2d(aes(colour = ..level..), bins = 5) +
  viridis::scale_colour_viridis() +
  ggsidekick::theme_sleek() +
  facet_wrap(~mp_name) +
  ylim(0, 3.5) + xlim(0, 3.5) +
  geom_point(alpha = 0.2) +
  labs(colour = "Prob. density", x = expression(B/B[MSY]),
    y = expression(F/F[MSY])) +
  guides(colour = FALSE)
#ggsave("analysis/pcod-bbmsy-ffmsy-multi.pdf", width = 8, height = 8)
```

```{r, fig.asp=1.9, out.width = "4.8in", fig.width=7}
library(dplyr)
library(RColorBrewer)
ffmsy <- pcod_mse@F_FMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value, year = Var3)
bbmsy <- pcod_mse@B_BMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value, year = Var3)
d <- dplyr::inner_join(ffmsy, bbmsy)
d <- dplyr::left_join(d, n)
d <- reshape2::melt(d, id.vars = c("iter", "mp", "year", "mp_name"))
levels(d$variable) <- c(expression(F/F[MSY]), expression(B/B[MSY]))

d_median <- d %>% group_by(mp_name, year, variable) %>%
  summarise(median_value = median(value)) %>%
  mutate(iter = NA)

fudge <- 3.5
d$over <- FALSE
d$over[d$value > fudge] <- TRUE
d$value[d$over] <- fudge
d_median$median_value[d_median$median_value > fudge] <- fudge

d_last <- dplyr::filter(d, year == max(year)) %>%
  select(-over, -year) %>%
  rename(last_value = value)
d <- inner_join(d, d_last)

cols <- brewer.pal(3, "RdBu")
cols[2] <- "grey80"

plot_timeseries <- function(dat, dat_median, title = "",
  ylim = c(0, fudge), cols, values, labels = TRUE, yaxis = TRUE) {
  g <- ggplot(dat, aes_string("year", "value", group = "iter")) +
    geom_line(aes_string(colour = "last_value"), alpha = 0.3) +
    facet_grid(mp_name~., labeller = label_parsed) +
    ggsidekick::theme_sleek() +
    scale_colour_gradientn(colours = cols,
      values = values) +
    geom_line(data = dat_median, aes_string("year", "median_value"),
      colour = "black", lwd = 1.5) +
    ylim(ylim[1], ylim[2]) +
    ggtitle(title) +
    guides(colour = FALSE) +
    ylab("Value") + xlab("Year")

  if (!labels)
    g <- g + theme(strip.background = element_blank(),
      strip.text.y = element_blank())

  if (!yaxis)
    g <- g + theme(axis.text.y = element_blank())
  g
}

cols <- brewer.pal(5, "RdBu")
cols <- c(cols[1], "grey50", cols[length(cols)])
set.seed(42)
# d_ <- filter(d, iter %in% sample(seq_len(max(d$iter)), 30))
d_ <- d

# plot_timeseries(d, d_median,
# cols = cols, values = scales::rescale(c(0, 0.8, 1.2, fudge)))

# mps <- c("DCAC", "DCAC_40")
# p1 <- plot_timeseries(filter(d_, variable == "B/B[MSY]", mp_name %in% mps),
#   filter(d_median, variable == "B/B[MSY]", mp_name %in% mps), expression(B/B[MSY]),
#   cols = cols, values = scales::rescale(c(0, 0.8, 1.2, fudge)),
#   labels = TRUE)
# p2 <- plot_timeseries(filter(d_, variable == "F/F[MSY]", mp_name %in% mps),
#   filter(d_median, variable == "F/F[MSY]", mp_name %in% mps), expression(F/F[MSY]),
#   cols = cols, values = scales::rescale(c(fudge, 1.2, 0.8, 0)),
#   labels = TRUE, yaxis = TRUE)
# gridExtra::grid.arrange(p1, p2, ncol = 2)

# pdf("analysis/pcod-bbmsy-ffmsy-ts-ex.pdf", width = 6, height = 3.5)
# gridExtra::grid.arrange(p1, p2, ncol = 2)
# dev.off()

# mps <- unique(d_$mp_name)
# # mps <- mps[-which(mps %in% c("CC4"))]
# p1 <- plot_timeseries(filter(d_, variable == "B/B[MSY]", mp_name %in% mps),
#   filter(d_median, variable == "B/B[MSY]", mp_name %in% mps), expression(B/B[MSY]),
#   cols = cols, values = scales::rescale(c(0, 0.8, 1.2, fudge)),
#   labels = TRUE)
# p2 <- plot_timeseries(filter(d_, variable == "F/F[MSY]", mp_name %in% mps),
#   filter(d_median, variable == "F/F[MSY]", mp_name %in% mps), expression(F/F[MSY]),
#   cols = cols, values = scales::rescale(c(fudge, 1.2, 0.8, 0)),
#   labels = TRUE, yaxis = TRUE)
# gridExtra::grid.arrange(p1, p2, ncol = 2)

# pdf("analysis/pcod-bbmsy-ffmsy-ts-ex-all.pdf", width = 6, height = 6)
# gridExtra::grid.arrange(p1, p2, ncol = 2)
# dev.off()

mps <- unique(d_$mp_name)
# mps <- mps[-which(mps %in% c("CC4"))]
p1 <- plot_timeseries(filter(d_, variable == "B/B[MSY]", mp_name %in% mps),
  filter(d_median, variable == "B/B[MSY]", mp_name %in% mps), expression(B/B[MSY]),
  cols = cols, values = scales::rescale(c(0, 0.8, 1.2, fudge)),
  labels = TRUE)
p2 <- plot_timeseries(filter(d_, variable == "F/F[MSY]", mp_name %in% mps),
  filter(d_median, variable == "F/F[MSY]", mp_name %in% mps), expression(F/F[MSY]),
  cols = cols, values = scales::rescale(c(fudge, 1.2, 0.8, 0)),
  labels = TRUE, yaxis = TRUE)
gridExtra::grid.arrange(p1, p2, ncol = 2)

# pdf("analysis/pcod-bbmsy-ffmsy-ts-ex-all.pdf", width = 6, height = 6)
# gridExtra::grid.arrange(p1, p2, ncol = 2)
# dev.off()

#########3
ffmsy <- pcod_mse@F_FMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, ffmsy = value, year = Var3)
bbmsy <- pcod_mse@B_BMSY[,,] %>% reshape2::melt() %>%
  dplyr::rename(iter = Var1, mp = Var2, bbmsy = value, year = Var3)
d <- dplyr::inner_join(ffmsy, bbmsy)
d <- dplyr::left_join(d, n)
d <- reshape2::melt(d, id.vars = c("iter", "mp", "year", "mp_name"))
levels(d$variable) <- c(expression(F/F[MSY]), expression(B/B[MSY]))

d_sum <- d %>% group_by(mp_name, year, variable) %>%
  summarise(median_value = median(value),
    l = quantile(value, probs = 0.75),
    u = quantile(value, probs = 0.25),
    ll = quantile(value, probs = 0.95),
    uu = quantile(value, probs = 0.05))


# d_sum$median_value[d_sum$median_value > fudge] <- fudge
# d_sum$u[d_sum$u > fudge] <- fudge
# d_sum$l[d_sum$l > fudge] <- fudge

d <- inner_join(d, d_last)

d$last_value[d$last_value > fudge] <- fudge
# d$value[d$value > fudge] <- fudge


cols <- brewer.pal(5, "RdBu")
cols <- c(cols[1], "grey50", cols[length(cols)])
g <- ggplot(d_sum, aes_string("year", "median_value")) +
  facet_grid(mp_name~variable, labeller = label_parsed) +
  geom_ribbon(aes(ymin = ll, ymax = uu), fill = "grey90") +
  geom_ribbon(aes(ymin = l, ymax = u), fill = "grey70") +
  ggsidekick::theme_sleek() +
  geom_line(lwd = 1.5) +
  coord_cartesian(ylim = c(0, 4)) +
  guides(colour = FALSE) +
  xlim(25, 50) +
  geom_hline(yintercept = 1,
    col = "black", lty = 2) +
  ylab("Value") + xlab("Year")
  # geom_line(data = filter(d, iter %in% c(1:10)),
  #   aes(y = value, group = iter),
  #   alpha = 0.4, colour = "blue")
  # scale_colour_gradientn(colours = cols,
  #     values = c(0, 0.8, 1.2, 3))
  # viridis::scale_colour_viridis()
g
```

```{r, fig.asp=1.2}
voi_out <- DLMtool::VOI(pcod_mse)
```
